### 2015-11-01 2015/Temporal Distinctiveness & Mixture Distributions/Manuscript Files/main.tex
changed folder name

\documentclass[a4paper, jou, natbib]{apa6}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}

%\usepackage{lineno}

\title{Temporal Distinctiveness in Task Switching: Assessing the Mixture-Distribution Assumption}
\shorttitle{Mixture Distribution Assumption}
\author{James A. Grange}
\affiliation{School of Psychology, Keele University, UK}

\note{{\bf Word Count:} x,xxx (Main body, not including abstract or references.)}
% \note{{\bf Under Review---Please, no direct quotes.}}

% command to insert editing comments or track changes
\newcommand{\jg}[1]{\textcolor{blue}{$^{\textrm{}}${#1}}}

%command for R symbol
   \newcommand{\R}{R}

\authornote{Please address correspondence to James A. Grange, School of Psychology, Dorothy Hodgkin Building, Keele University, Keele, UK, ST5 5BG. Email: grange.jim@gmail.com. All raw data, analysis code, and model code are available to download at www.GitHub.com/JimGrange/MixtureDistribution}

\leftheader{Grange}

\abstract{.}

\keywords{Task switching; decay; interference; computational model}

\begin{document}
\maketitle

%\bibliography{References.bib}

\end{document}

### 2015-11-01 2015/Temporal Distinctiveness & Mixture Distributions/Data & Model Code/Model Fit/modelFit.R
removed model RT trim (not necessary)

@@ -93,33 +93,18 @@ n = 50000
 fastSim <- simLBA_Mixture(n = n, b = c(bFast, bSlow), a = A, 
                           drift = c(driftFast, driftSlow), s = s, ter = ter, 
                           p = 1)
-colnames(fastSim)[3] <- "participant"
-fastSim <- sdTrim(fastSim, minRT = 150, sd = 4, perCondition = FALSE, 
-                  perParticipant = TRUE, omitErrors = FALSE, 
-                  returnType = "raw")
-colnames(fastSim)[3] <- "subject"
 fastSim <- prepData(fastSim)
 
 # slow condition
 slowSim <- simLBA_Mixture(n = n, b = c(bFast, bSlow), a = A, 
                           drift = c(driftFast, driftSlow), s = s, ter = ter, 
                           p = 0)
-colnames(slowSim)[3] <- "participant"
-slowSim <- sdTrim(slowSim, minRT = 150, sd = 4, perCondition = FALSE, 
-                  perParticipant = TRUE, omitErrors = FALSE, 
-                  returnType = "raw")
-colnames(slowSim)[3] <- "subject"
 slowSim <- prepData(slowSim)
 
 # mixture distribution
 intSim <- simLBA_Mixture(n = n, b = c(bFast, bSlow), a = A, 
                          drift = c(driftFast, driftSlow), s = s, ter = ter, 
                          p = p)
-colnames(intSim)[3] <- "participant"
-intSim <- sdTrim(intSim, minRT = 150, sd = 4, perCondition = FALSE, 
-                  perParticipant = TRUE, omitErrors = FALSE, 
-                 returnType = "raw")
-colnames(intSim)[3] <- "subject"
 intSim <- prepData(intSim)
 
 ## do some plots

### 2015-11-02 2015/Temporal Distinctiveness & Mixture Distributions/Data & Model Code/Model Fit/modelFit.R
added mixture simulation

@@ -1,6 +1,6 @@
 #------------------------------------------------------------------------------
 rm(list = ls())
-setwd("~/Git/paperData/2015/Mixture Distribution/Model Fit")
+setwd("~/Git/paperData/2015/Temporal Distinctiveness & Mixture Distributions/Data & Model Code/Model Fit")
 
 # load required libraries & functions
 library(dplyr)

### 2015-11-02 2015/Temporal Distinctiveness & Mixture Distributions/Data & Model Code/Testing Mixture Distributions/fp Data/mixtureDistributions.r

@@ -1,0 +1,45 @@
+rm(list = ls())
+setwd("~/Git/paperData/2015/Mixture Distribution/Testing Mixture Distributions")
+
+source("functions.R")
+library(dplyr)
+
+# get the data (& do trimming)
+data <- read.csv("data.csv")
+data$rt <- round(data$rt / 1000, 3)
+data = sdTrim(data, minRT = 0.150, sd = 2.5, perCondition = FALSE, 
+              perParticipant = TRUE,  returnType = "raw")
+
+#------------------------------------------------------------------------------
+
+
+#------------------------------------------------------------------------------
+### do the mixture plots 
+
+# define ratios to include in the analysis
+ratios <- c(0.05, 1, 20)
+ratioData <- subset(data, data$ratio %in% ratios)
+
+# subset of data to pass to fp package. Then, change names to match 
+# fp package function requirements
+ratioData <- select(ratioData, rt, ratio, participant)
+colnames(ratioData) <- c("rt", "cond", "pp")
+# get the fp1 object
+res <- fpGet(ratioData[, c("rt", "cond")], 1000, bw = 0.75)  
+
+# call plot
+par(las = 1, mfrow = c(1, 3), mar = c(4.2, 4.2, 1, 1))  
+plot(res, xlab = "Resonse Time (S)", col = 1) 
+
+# do Bayesian analysis
+res <- tapply(1:nrow(ratioData), ratioData$pp, function(X) {
+  fpGet(ratioData[X, ], 1000, bw = 0.75)
+})  # compute the list
+fpAnova(res, stat = "both")
+
+# do box-plot
+crosses = fpDensDiff(res)  # first, get the crossing points
+boxplot(t(crosses), frame.plot = F, xlab = "Crossing point", 
+        ylab = "Condition pair", names = c("3-2", "2-1", "3-1"), 
+        horizontal = T)
+#------------------------------------------------------------------------------

### 2015-11-02 2015/Temporal Distinctiveness & Mixture Distributions/Data & Model Code/Testing Mixture Distributions/functions.R

@@ -1,798 +1,0 @@
-#------------------------------------------------------------------------------
-### fixed-point code adapted from the "fp" package
-# http://www.leendertvanmaanen.com/resources/fp/example.html
-
-fp1 <- setClass("fp1", representation(dens="array", diff="data.frame", 
-                                      dat="data.frame"))
-
-plot.fp1 <- function(x, ..., ylab=c("Density","Density difference"), 
-                     xlim=NULL) {
-  options(warn=-1)
-  if (is.null(xlim)) xlim <- range(x@dens[[1]]$x)
-  plot(1,type="n",
-       ylim=c(0,max(unlist(lapply(x@dens, function(X) {max(X$y)})))),
-       xlim=xlim,
-       bty="n", ylab=ylab[1], ...)
-  for (i in 1:length(x@dens)) {
-    lines(x@dens[[i]], col=i)
-  }
-  legend("top", c("1: 0.05", "2: 1.00", "3: 20.00"), lty = c(1, 1, 1), 
-         col = c(1, 2, 3), bty = "n")
-  
-  matplot(x@dens[[1]]$x,x@diff, type='l', pch=16,
-          lwd=3, bty="n", ylab=ylab[2], xlim=xlim, ...); abline(h=0, lty=1)
-  legend("top", c("3-1", "2-1", "3-2"), bty = "n", 
-         lty = c(1, 2, 3), 
-         lwd = c(2, 2, 2))
-}
-setMethod("plot","fp1", function(x, ...) plot.fp1(x, ...))
-
-fpPlot <- function(...) {
-  plot.fp1(...) # just a wrapper
-}
-
-fpGet <- function(dat, n=512, bw='nrd0') {
-  # dat: nx2 dataframe or matrix with in col 1: RT; col 2: condition
-  if (is.matrix(dat)) dat <- as.data.frame(dat)
-  
-  rng <- range(dat[[1]])
-  dens <- tapply(dat[[1]], dat[[2]], density, from=rng[1], to=rng[2], n=n, 
-                 bw=bw)
-  diff <- NULL
-  for (i in 2:length(dens)) {
-    for (j in 1:(i-1)) {
-      
-      # difference (density-based method)
-      tmp <- data.frame(dens[[i]]$y - dens[[j]]$y)
-      names(tmp) <- paste(i,j,sep='-')
-      if (is.null(diff)) diff <- tmp else diff <- cbind(diff, tmp)
-    }
[…]

### 2015-11-02 2015/Temporal Distinctiveness & Mixture Distributions/Data & Model Code/Testing Mixture Distributions/mixtureDistributions.r

@@ -1,45 +1,0 @@
-rm(list = ls())
-setwd("~/Git/paperData/2015/Mixture Distribution/Testing Mixture Distributions")
-
-source("functions.R")
-library(dplyr)
-
-# get the data (& do trimming)
-data <- read.csv("data.csv")
-data$rt <- round(data$rt / 1000, 3)
-data = sdTrim(data, minRT = 0.150, sd = 2.5, perCondition = FALSE, 
-              perParticipant = TRUE,  returnType = "raw")
-
-#------------------------------------------------------------------------------
-
-
-#------------------------------------------------------------------------------
-### do the mixture plots 
-
-# define ratios to include in the analysis
-ratios <- c(0.05, 1, 20)
-ratioData <- subset(data, data$ratio %in% ratios)
-
-# subset of data to pass to fp package. Then, change names to match 
-# fp package function requirements
-ratioData <- select(ratioData, rt, ratio, participant)
-colnames(ratioData) <- c("rt", "cond", "pp")
-# get the fp1 object
-res <- fpGet(ratioData[, c("rt", "cond")], 1000, bw = 0.75)  
-
-# call plot
-par(las = 1, mfrow = c(1, 3), mar = c(4.2, 4.2, 1, 1))  
-plot(res, xlab = "Resonse Time (S)", col = 1) 
-
-# do Bayesian analysis
-res <- tapply(1:nrow(ratioData), ratioData$pp, function(X) {
-  fpGet(ratioData[X, ], 1000, bw = 0.75)
-})  # compute the list
-fpAnova(res, stat = "both")
-
-# do box-plot
-crosses = fpDensDiff(res)  # first, get the crossing points
-boxplot(t(crosses), frame.plot = F, xlab = "Crossing point", 
-        ylab = "Condition pair", names = c("3-2", "2-1", "3-1"), 
-        horizontal = T)
-#------------------------------------------------------------------------------

### 2015-11-02 2015/Temporal Distinctiveness & Mixture Distributions/Manuscript Files/main.tex
completed model sections

@@
+%%%--------------------------------------------------------------------------------------------
 \documentclass[a4paper, jou, natbib]{apa6}
-
 \usepackage[english]{babel}
@@
 \usepackage[colorinlistoftodos]{todonotes} 
+\usepackage{etoolbox}
+
+\newtoggle{jou}
+\toggletrue{jou}
+%\togglefalse{jou}
 
@@
 Email: grange.jim@gmail.com.
-All raw data, analysis code, and model code are available to download at www.GitHub.com/JimGrange/MixtureDistribution}
+All raw data, analysis code, and model code are available to download at http://bit.ly/1l22EUV.}
 
@@
 \maketitle
+%%%--------------------------------------------------------------------------------------------
 
-%\bibliography{References.bib}
+%%%--------------------------------------------------------------------------------------------
+\section{Behavioural Data}
+Describe the gist of the method, and provide a plot of the pertinent data
+%%%--------------------------------------------------------------------------------------------
+
+%%%--------------------------------------------------------------------------------------------
+\section{Assessing the Presence of Mixture-Distributions}
+\cite{VanMaanen2014} introduced a method---the ``fixed-point'' property test---for statistically testing the presence of a mixture-distribution, given two ``base'' distributions.
+If distribution $z$ is a mixture of two base distributions $x$ and $y$, then the fixed-point property states that the probability density for distribution $z$, $f_{z}$, is a weighted sum of the probability densities of the other two distributions $f_{x}$ and $f_{y}$.
+Put simply, this implies that there exists a particular response time $t$ for which the probability of providing such as response is identical for all three distributions; that is $f_{x}(t)$ = $f_{z}(t)$ = $f_{y}(t)$.
+
+For example, consider the left panel of Figure \ref{fig:fpExample}.
+Here, three response time distributions have been simulated: $x$ is a fast RT distribution, and $y$ is a slow RT distribution.
+Distribution $z$ was simulated as being a mixture of distributions $x$ and $y$ with mixture probability $p$ set to $p$ = 0.7.
+
+\iftoggle{jou}{
+\begin{figure}
+\begin{center}
+\includegraphics[width = 0.5\textwidth]{Images/fpExample.pdf}
+\caption{Example of the fixed-point property in three distributions.
+Distribution $z$ is a mixture of distributions $x$ and $y$ with mixture probability $p$ set to $p$ = 0.7.
+The left panel shows the probability densities for each distribution.
+The right panel shows the density difference between different density functions.
+The distributions share a common crossing point at about 0.850 seconds.}
+\label{fig:fpExample}
+\end{center}
+\end{figure}
+}{
+\begin{figure}
+\begin{center}
+\includegraphics[width = \textwidth]{Images/fpExample.pdf}
+\caption{Example of the fixed-point property in three distributions.
+Distribution $z$ is a mixture of distributions $x$ and $y$ with mixture probability $p$ set to $p$ = 0.7.
+The left panel shows the probability densities for each distribution.
+The right panel shows the density difference between different density functions.
+The distributions share a common crossing point at about 0.850 seconds.}
+\label{fig:fpExample}
+\end{center}
+\end{figure}
+}
+
+As can be seen, the density functions of all three distributions share a common ``crossing point'', the RT at which all density functions are equal (i.e., where $f_{x}(t)$ = $f_{z}(t)$ = $f_{y}(t)$).
+The crossing point is made clearer by taking successive subtractions of pairs of density functions (see the right panel of Figure \ref{fig:fpExample}).
+Zero in this plot represents a density difference of zero (i.e., where the two density functions are equal).
+For example, the solid line represents the density difference of $f_{z}$ - $f_{x}$.
+If the distributions share a common crossing point, the density differences for all pairs of distribution differences will cross zero at a similar response time.
+This is the case in the current plot, where the three distributions share a common crossing point of about 0.850 seconds.
+
+%%----------
+\subsection{Application to the Data}
+The data was assessed for the presence of a mixture distribution.
+Correct RTs were first trimmed to retain RTs slower than 150 milliseconds, and RTs faster than 2.5 standard deviations above each subjects' mean RT.
+The data was then assessed for the presence of a fixed-point by passing it to the \texttt{fp} function provided in the form of \texttt{R} code from \citet{VanMaanen2014}.
+Visual representation of the fixed-point assessment is shown in Figure \ref{fig:mixtureDistributionData}.
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width = \textwidth]{Images/mixtureDistributionData.pdf}
+\caption{Example of the fixed-point property in three distributions.
+Distribution $z$ is a mixture of distributions $x$ and $y$ with mixture probability $p$ set to $p$ = 0.7.
+The left panel shows the probability densities for each distribution.
+The right panel shows the density difference between different density functions.
+The distributions share a common crossing point at about 0.850 seconds.}
+\label{fig:mixtureDistributionData}
+\end{center}
+\end{figure*}
+
+As shown in the left and center panels of Figure \ref{fig:mixtureDistributionData}, the three RT distribution functions share a common crossing point at just over 1 second.
+The right panel of Figure \ref{fig:mixtureDistributionData} shows boxplots of the distribution of crossing points for each pair for all subjects.
+There is considerable overlap in the boxplots suggesting no difference between condition pairs of crossing point (supporting the fixed-point hypothesis).
+Together, this visual inspection provides good evidence that the ratio = 1 RT function is a weighted mixture of the ``slow'' RT distribution (where ratio = 0.05) and the ``fast'' RT distribution (where ratio = 20), as predicted by the temporal distinctiveness model \cite{Grange2015}.
+
+To assess statistical support for the common crossing point, a one-way ANOVA was conducted on the three levels of crossing-point pairs shown in the right panel of Figure \ref{fig:mixtureDistributionData}.
+The dependent variable in this analysis---shown in the x-axis of that Figure---is the crossing point in seconds for the density difference.
+This analysis was not statistically significant [\emph{F}(2, 48) = 1.25, \emph{p} = .295].
+However, the presence of a common crossing point requires the acceptance of a null hypothesis (i.e., of no difference in crossing points), which cannot be achieved via standard statistical analysis.
+Therefore, a default Bayesian ANOVA \cite{Rouder2012} was conducted on the same data, which produces a Bayes Factor; the Bayes Factor---denoted $BF_{01}$---assesses the evidence in favour of a model assuming a common crossing point (i.e., a ``null'' model) compared to a model assuming multiple crossing points (i.e., an ``alternative'' model).
+The Bayes Factor for this data was $BF_{01}$ = 3.354, suggesting the data are 3.4 times more likely under the model assuming a common crossing point.
+Together, these statistical analyses converge on the conclusion that the RT distributions share a common crossing point, and as such can be considered support for the mixture-distribution hypothesis.
+
+%%%--------------------------------------------------------------------------------------------
+\section{A Mixture-Distribution Model of Temporal Distinctiveness Effects}
+
+The previous section provided statistical support for the presence of a mixture-distribution for intermediate RCI ratios (i.e., intermediate levels of temporal distinctiveness).
+This is in agreement both with the verbal theory regarding TD effects \cite{Horoufchin2011a} and its formal implementation \cite{Grange2015}, which explains performance across TD ratios.
+In this section I develop a mathematical process model to predict RT distributions of TD data.
+The fitting of whole RT distributions presents an important advance over the model of \citet{Grange2015}, as it allows a direct test---rather than a relatively indirect test from fitting mean RTs---of that model's core assumption: that intermediate TD performance is a weighted mixture of ``retrieved'' and ``not-retrieved'' processing modes, which lead to fast and slow RTs, respectively.
+
+In this section, I first provide a schematic overview of the assumptions of the model. The mathematical details of the model are in Appendix B.
+
+%%----------
+\subsection{Overview of the Model}
+
+\subsubsection{Episodic Retrieval}
+The main processing stages in the model are shown in Figure \ref{fig:retrievalOverview}.
+The model assumes that, when presented with a task cue on a task repetition trial, the cognitive system attempts to retrieve the most recent episodic trace of this task (which was from trial n--1).
+The success of this retrieval attempt is influenced by the temporal distinctiveness of the episodic trace (at n--1) from a distracting episodic trace from the task two trials ago (at n--2).
+
+\iftoggle{jou}{
+\begin{figure}
+\begin{center}
+\includegraphics[width = 0.5 \textwidth]{Images/retrievalOverview.pdf}
+\caption{Overview of the retrieval processes in the model.}
+\label{fig:retrievalOverview}
+\end{center}
+\end{figure}
+}{
+\begin{figure}
+\begin{center}
+\includegraphics[width = \textwidth]{Images/retrievalOverview.pdf}
+\caption{Overview of the retrieval processes in the model.}
+\label{fig:retrievalOverview}
+\end{center}
+\end{figure}
+}
+
+Retrieval probability---$p$(retrieval)---influences the speed of retrieval.
+If retrieval succeeds, the response is facilitated due to retrieval of elements of the previous episodic trace that prime performance on the current trial; if retrieval fails, the response is not facilitated, and thus responding is slower as it has to be performed via a slower, algorithmic, route \citep[see][for discussion]{Grange2015}.
+
+\subsection{RT Distributions}
+To predict response time distributions, the mathematics of the Linear Ballistic Accumulator (ref) was used.
+The LBA is a successful model of choice response time, allowing the modelling of correct and error RT distributions.
+The model assumes that, when presented with a task stimulus, evidence accumulates towards a retrieval threshold.
+Evidence for each response---typically simplified to the ``correct'' and ``error'' response---accumulates in a linear fashion until one of the accumulators reaches the response threshold.
+At this point, it is assumed that this response has been selected by the model.
+
+The LBA model has several parameters.
+The mean rate of evidence accumulation is referred to as the \emph{drift rate}, $v$; it is larger for the correct response than for the error response.
+The drift rate for each accumulator can vary on each trial, but is assumed to have a fixed mean rate.
+The drift rate on each trial is a random draw from a normal distribution with mean $v$ and standard deviation $s$.
+The starting point of the accumulation process can vary uniformly between 0 and $A$.
+The height of the response threshold is governed by the parameter $b$.
+The time taken to perceptually encode stimuli and make a manual response is captured by a single non-decision time parameter $ter$.
+
+Figure \ref{fig:lbaAccumulation} shows how the LBA is applied in the current context.
+(Note that only the correct accumulators are shown to avoid clutter.) The model only ever uses one of two accumulation processes: If retrieval is successful, the model samples the current RT from a ``successful'', ``fast'' accumulation process with a higher drift rate, $v_{Fast}$; if retrieval fails, the current RT is sampled from an ``unsuccessful'', ``slow'' accumulation process with a lower drift rate, $v_{Slow}$.
+
+\iftoggle{jou}{
+\begin{figure}
+\begin{center}
+\includegraphics[width = 0.5 \textwidth]{Images/lbaAccumulation.pdf}
+\caption{Overview of the Linear Ballistic Accumulation Process for successful and unsuccessful retrieval.}
+\label{fig:lbaAccumulation}
+\end{center}
+\end{figure}
+}{
+\begin{figure}
+\begin{center}
+\includegraphics[width = 0.5 \textwidth]{Images/lbaAccumulation.pdf}
+\caption{Overview of the Linear Ballistic Accumulation Process for successful and unsuccessful retrieval.}
+\label{fig:lbaAccumulation}
+\end{center}
+\end{figure}
+}
+
+Thus, in this model, when TD is high, $p$(retrieval) is high, and as such more trials will be sampled from the fast accumulation process.
+When TD is low, so too will  $p$(retrieval), and as such more trials will be sampled from the slow accumulation process.
+Intermediate TDs will have an intermediate $p$(retrieval), and as such their RT distributions will be a weighed mixture of the two base distributions (fast and slow), with the exact proportion governed by $p$(retrieval).
+
+%%----------
+\subsection{Fitting the Model}
+
+\citet{Grange2015} used the full mathematics of SIMPLE to obtain $p$(retrieved).
+To reduce the number of free parameters, in the current model $p$(retrieved) was treated as a ``semi-fixed'' parameter.
+To acieve this, the TD ratio was calculated for each RCI-sequence condition in Figure (dataPlot).
+Specifically, the RCI ratio was 20 for n--2 to n--1 RCIs of 50ms--1000ms; the ratio was 1 for RCIs of 1000ms--1000ms and 50ms--50ms; and the ratio was 0.05 for RCIs of 50ms--1,000ms.
+
+$p$(retrieved) was ``semi-fixed'' in the sense that it was fixed at $p$(retrieved) = 1 for ratios of 20 (i.e., perfect retrieval) and fixed at $p$(retrieved) = 0 for ratios of 0.05 (i.e., failed retrieval); $p$(retrieved) was free to vary for ratios of 1.
+Thus, $p$(retrieved) controls the relative contribution of the two RT distributions for intermediate RCI ratios.
+
+Separate drift rates were estimated for the ``fast'' and ``slow'' distributions---$v_{Fast}$ and $v_{Slow}$, respectively.
+(Note that drift rates for error response evidence accumulation is given as 1--$v$.) Also, each distribution had its own response threshold---$b_{Fast}$ and $b_{Slow}$.\footnote{Initial fits with just $v$ varying between the fast and slow distributions did not fit the data as well as when $b$ was also allowed to vary between conditions.} All other parameters (i.e., $A$, $s$, and $ter$ took on identical values for all three ratio conditions.
+
+Note therefore that this fit is rather ambitious.
+First, the model has to explain whole RT distributions for correct and error responses across all three conditions of RCI ratio; that is 30 data points with just 8 parameters.
+Also, the data for ratio = 1 is never explicitly modelled; rather, the model is fit to the ratio = 20 with a fast distribution and to ratio = 0.05 data with a slow distribution; the data for ratio = 1 is then estimated by a weighted contribution of the two distributions controlled only by $p$(retrieved)).
+
+The model was fitted to the data via a version of Quantile Maximum Probability Estimation (QMPE; REF), where the model is fit to RT quantiles rather than individual RTs as per maximum likelihood (see Appendix B for details).
+This method was used due to the relatively low number of trials per subject, and the rather low error rate.
+The fits of the model to the behavioural data are shown in Figure \ref{fig:modelFit}.
+
+% Table generated by Excel2LaTeX from sheet 'Sheet1'
+\begin{table}[htbp]
+  \centering
+  \caption{Best fitting model parameters from the fit routine.
+Note that $p$(retrieved) refers to the probability of sampling from the fast distribution only for ratio = 1 data points.
+See text for details.}
+    \begin{tabular}{rr}
+    \toprule
+    Model Parameter & Value \\
+    \midrule
+    $p(retrieved)$     & 0.759 \\
+    $A$     & 718.14 \\
+    $b_{Fast}$ & 114.58 \\
+    $b_{Slow}$ & 179.96 \\
+    $v_{Fast}$ & 1.132 \\
+    $v_{Slow}$ & 0.893 \\
+    $s$     & 0.44 \\
+    $ter$   & 346.42 \\
+    \bottomrule
+    \end{tabular}%
+  \label{tab:bestParameters}%
+\end{table}%
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width = \textwidth]{Images/qmp2RCI_drift_+_b.pdf}
+\caption{Model fit.}
+\label{fig:modelFit}
+\end{center}
+\end{figure*}
+
+This Figure presents so-called ``defective'' cumulative distribution functions (CDFs).
+The data are sorted from fastest to slowest, and then quantile cut-off points are calculated for each subject according to a pre-specified set of quantiles $\vec{q}$ (here $\vec{q}$ = .1, .3, .5, .7, .9).
+The Figure plots the average RT for each quantile across subjects against the quantile value.
+The plot is a defective CDF in the sense that it also displays information about errors.
+Specifically, RT is plotted against $\vec{q}$ * mean accuracy rather than just $\vec{q}$.
+Error RT---shown in the Figure as open circles)---is error RT plotted against $\vec{q}$ * (1 - mean accuracy).
+
+The model fit to correct RT distributions is rather good.
+The model captures all of the main trends in the data: RT becomes facilitated as $p$(retrieved) increases (from left-to-right $p$(retrieved) = 0, $p$(retrieved) = 0.759, and $p$(retrieved) = 1).
+This improvement in RT is largely at the slower end of the RT distribution.
+Also, the defective CDFs become steeper as $p$(retrieved) is increased, reflecting generally better accuracy.
+Importantly, the central plot shows a good fit of the model to the data, providing support that intermediate TDs are a mixture of two base distributions.
+
+The fit to the error RT distributions is not as good as for the correct RT distributions.
+However, accuracy was generally very high in this experiment (indeed, participants were excluded for not achieving greater than 90\% accuracy).
+So, there were often few error RTs per quantile bin during the model fit, making accurate estimation difficult.
+However, dispite the poor quantitative fit, the qualitative pattern seen in the human data is generally reproduced: error RT becomes generally faster and less variable as ratio increases.
+%%%--------------------------------------------------------------------------------------------
+
+%%%--------------------------------------------------------------------------------------------
+\section{General Discussion}
+
+%%%--------------------------------------------------------------------------------------------
+
+%%%--------------------------------------------------------------------------------------------
+\appendix
+\section{Overview of Grange \& Cross (2015) Model}
+The \citet{Grange2015} model used the mathematics of the SIMPLE \cite{Brown2007} model to account for TD effects on task repetition trials.
+Distinctiveness is proportional to the \emph{similarity} between a target trace and its neighbours in episodic memory.
+In this model, similarity is only influenced by the temporal domain.
+Similarity of instances at n--1 (item $i$) and n--2 (item $j$) is given by
+
+\begin{equation}
+\eta_{ij} = \left(\frac{T_{i}}{T_{j}}\right)^{c}, 
+\label{eq:simpleSimilarity}
+\end{equation}
+
+\noindent where $T_{x}$ refers to the temporal age of an item. Temporal age is calculated from the current time.
+
+Based on the target traces $i$'s similarity, to its neighbours, its discriminability $D_{i}$ can be determined. This refers to how isolated the target trace $i$ is in episodic memory, and is given by
+
+\begin{equation}
+D_{i} = \frac{1}{\sum\limits_{j = 1}^n \eta_{ij}}.
+\label{eq:simpleDiscriminationA}
+\end{equation}
+
+As we are only considering the similarity between two items ($i$ and $j$), and as an item's similarity to iself is 1, Equation \ref{eq:simpleDiscriminationA} becomes
+
+\begin{equation}
+D_{i} = \frac{1}{\sum\limits_{j = 1}^n \eta_{ij} + 1}.
+\label{eq:simpleDiscriminationB}
+\end{equation}
+
+Given an item's discriminability, we can calculate its retrieval probability $p(R_{i})$ at time of retrieval $t$ by
+
+\begin{equation}
+p(R_{i}|D_{i}) = \frac{1}{1 + e^{-s(D_{i} - t)}}, 
+\label{eq:simpleProb}
+\end{equation}
+
+\noindent where $s$ and $t$ are free parameters which descibe the sloe of the transforming function and the threshold of retrieval, respectively.
+
+Given these equations, we can calculate the retrieval probability for each level of temporal distinctiveness in the behavioural experiment.
+It is assumed that if the trace is retrieved (with probability $p$) then response time will be a random draw from a fast RT distribution with mean $\mu_{fast}$; if retrieval fails (with probability $1 - p$), the response time will be a random draw from a slow RT distribution with mean $\mu_{slow}$.
+Thus, mean RT for each level of TD is given by the RT-mixture equation
+
+\begin{equation}
+RT = p\mu_{Fast} + (1 - p)\mu_{slow}.
+\label{eq:tdMixtureNew}
+\end{equation}
+%%%--------------------------------------------------------------------------------------------
+\appendix
+\section{Mixture-Distribution Model Details}
+
+\subsubsection{LBA for Unitary Process}
+In the LBA for a unitary process (i.e., not a mixture model), evidence for response $i$ has a CDF (at time \emph{t}) of
+
+\begin{equation}
+\begin{aligned}
+F_{i}(t) = & 1 + \frac{b - A - tv_{i}}{A} \Phi\left(\frac{b - A - tv_{i}}{ts}\right) - 
+\frac{b - tv_{i}}{A} \Phi\left(\frac{b - tv_{i}}{ts}\right) + \\ 
+&\qquad \frac{ts}{A} \phi \left(\frac{b - A - tv_{i}}{ts}\right) - \frac{ts}{A} \phi \left(\frac{b - tv_{i}}{ts}\right),
+\end{aligned}
+\label{eq:lbaCDF}
+\end{equation}
+
+\noindent (where $\Phi$ refers to the normal distribution's CDF) and a PDF of
+
+\begin{equation}
+\begin{aligned}
+f_{i}(t) = \frac{1}{A} & \Biggl[-v_{i}\Phi \Biggl(\frac{b - A - tv_{i}}{ts}\Biggr) + s\phi\Biggl(\frac{b - A - tv_{i}}{ts}\Biggr) \\
+&\qquad + v_{i}\Phi \Biggl(\frac{b - tv_{i}}{ts}\Biggr) - s\phi\Biggl(\frac{b - tv_{i}}{ts}\Biggr)\Biggr] 
+\end{aligned}
+\label{eq:lbaPDF}
+\end{equation}
+
+\noindent where $\phi$ refers to the normal distribution's density. Considering two accumulators $i$ and $j$ (e.g., correct \& error response, respectively), the PDF for $i$ at time $t$ is given by
+
+\begin{equation}
+\mbox{PDF}_{i}(t) = f_{i}(t) \prod_{j \neq i} \left(1 - F_{j}(t)\right).
+\label{eq:defectivePDF}
+\end{equation}
+
+\subsubsection{Modelling Mixture Distributions}
+If we denote the fast accumulation process as $\gamma$ and the slow accumulation process as $\lambda$, recall that mean RT can be predicted by
+
+\begin{equation}
+RT = p\mu_{\gamma} + (1 - p)\mu_{\lambda}.
+\end{equation}
+
+Extending this mixture model to a likelihood function, we can now obtain the PDF for response $i$ (rather than response $j$) at time $t$ by
+
+\begin{equation}
+\begin{aligned}
+\mbox{PDF}_{i} = &\left[p \cdot f_{\gamma i}(1 - F_{\gamma j})\right] + \\ 
+&\qquad \left[(1 - p) \cdot f_{\lambda i}\right] (1 - F_{\lambda j})
+\end{aligned}
+\label{eq:tdLikelihood}
+\end{equation}
+
+\bibliography{References.bib}
 

### 2015-11-02 2015/Temporal Distinctiveness & Mixture Distributions/Data & Model Code/Model Fit/modelFit.R

@@ -169,12 +169,12 @@ plot(slowHumanCorrectRT, slowHumanCorrectCDF, type = "p",
      xlab = "Response Time (ms)", ylab = "Defective CDF")
 points(slowHumanErrorRT, slowHumanErrorCDF, type = "p")
 lines(slowModelCorrectRT, slowModelCorrectCDF, type = "b", lty = 1, lwd = 1, 
-      pch = 19, cex = 0.2)
+      pch = 17, cex = 0.7)
 lines(slowModelErrorRT, slowModelErrorCDF, type = "b", lty = 2, lwd = 1,
-      pch = 19, cex = 0.2)
+      pch = 17, cex = 0.7)
 legend("topleft", c("Data (Correct)", "Data (Error)",
                     "Model (Correct)", "Model (Error)"), cex = 1, 
-       pch = c(19, 1, NA, NA), lty = c(NA, NA, 1, 2),  bty = "n")
+       pch = c(19, 1, 17, 17), lty = c(NA, NA, 1, 2),  bty = "n")
 
 # plot intermediate
 plot(intHumanCorrectRT, intHumanCorrectCDF, type = "p", 
@@ -182,9 +182,9 @@ plot(intHumanCorrectRT, intHumanCorrectCDF, type = "p",
      xlab = "Response Time (ms)", ylab = "Defective CDF")
 points(intHumanErrorRT, intHumanErrorCDF, type = "p")
 lines(intModelCorrectRT, intModelCorrectCDF, type = "b", lty = 1, lwd = 1, 
-      pch = 19, cex = 0.2)
+      pch = 17, cex = 0.7)
 lines(intModelErrorRT, intModelErrorCDF, type = "b", lty = 2, lwd = 1,
-      pch = 19, cex = 0.2)
+      pch = 17, cex = 0.7)
 
 # plot fast
 plot(fastHumanCorrectRT, fastHumanCorrectCDF, type = "p", 
@@ -192,9 +192,9 @@ plot(fastHumanCorrectRT, fastHumanCorrectCDF, type = "p",
      xlab = "Response Time (ms)", ylab = "Defective CDF")
 points(fastHumanErrorRT, fastHumanErrorCDF, type = "p")
 lines(fastModelCorrectRT, fastModelCorrectCDF, type = "b", lty = 1, lwd = 1, 
-      pch = 19, cex = 0.2)
+      pch = 17, cex = 0.7)
 lines(fastModelErrorRT, fastModelErrorCDF, type = "b", lty = 2, lwd = 1, 
[…]

### 2015-11-02 2015/Temporal Distinctiveness & Mixture Distributions/Data & Model Code/Testing Mixture Distributions/fp Data/mixtureDistributions.r

@@ -1,5 +1,5 @@
 rm(list = ls())
-setwd("~/Git/paperData/2015/Mixture Distribution/Testing Mixture Distributions")
+setwd("~/Git/paperData/2015/Temporal Distinctiveness & Mixture Distributions/Data & Model Code/Testing Mixture Distributions/fp Data")
 
 source("functions.R")
 library(dplyr)

### 2015-11-02 2015/Temporal Distinctiveness & Mixture Distributions/Grange (under review) re-analysis/functions.R
added Grange (in prep) data

@@ -1,0 +1,593 @@
+### functions for analysis
+
+#------------------------------------------------------------------------------
+# change data to long format
+doLong <- function(data){
+  
+  locationData <- subset(data, data$condition == "Perceptual")
+  parityData <- subset(data, data$condition == "Memory")
+  
+  # do location data first
+  locData <- NULL
+  
+  for(i in 1:nrow(locationData)){
+    
+    # matrix for subject data
+    # rows = 8 conditions
+    # columns = subject, sequence, rci, rciChange, task, rt
+    subjectData <- matrix(0, nrow = 8, ncol = 6)
+    subjectData <- data.frame(subjectData)
+    colnames(subjectData) <- c("subject", "sequence", "rci", "rcichange", 
+                               "task", "rt")
+    
+    # populate the data frame
+    subjectData[1, ] <- c(locationData$subject[i], "repeat", "50", "same", 
+                          "perceptual", locationData$Rep50Same[i])
+    
+    subjectData[2, ] <- c(locationData$subject[i], "repeat", "50", "different",
+                          "perceptual", locationData$Rep50Different[i])
+    
+    subjectData[3, ] <- c(locationData$subject[i], "repeat", "1000", "same",
+                          "perceptual", locationData$Rep1000Same[i])
+    
+    subjectData[4, ] <- c(locationData$subject[i], "repeat", "1000", "different", 
+                          "perceptual", locationData$Rep1000Different[i])
+    
+    subjectData[5, ] <- c(locationData$subject[i], "switch", "50", "same", 
+                          "perceptual", locationData$Sw50Same[i])
+    
+    subjectData[6, ] <- c(locationData$subject[i], "switch", "50", "different",
+                          "perceptual", locationData$Sw50Different[i])
+    
+    subjectData[7, ] <- c(locationData$subject[i], "switch", "1000", "same",
+                          "perceptual", locationData$Sw1000Same[i])
+    
+    subjectData[8, ] <- c(locationData$subject[i], "switch", "1000", "different", 
+                          "perceptual", locationData$Sw1000Different[i])
+    
+    #change certain columns to numeric
[…]

### 2015-11-03 2015/Temporal Distinctiveness & Mixture Distributions/Manuscript Files/main.tex
updated manuscript file

@@
 
+\begin{figure} 
+\begin{center}
+\includegraphics[width = 0.5 \textwidth]{Images/tdAccount.pdf}
+\caption{Schematic overview of the temporal distinctiveness account of response--cue interval effects in task switching. See text for details.}
+\label{fig:tdAccount}
+\end{center}
+\end{figure}
+
 %%%--------------------------------------------------------------------------------------------
 \section{Behavioural Data}
-Describe the gist of the method, and provide a plot of the pertinent data
+Describe the gist of the method, and provide a plot of the pertinent data.
+
+Consider a portion of data reported by Grange (in revision), which can be seen in Figure \ref{fig:grangeData} (see Appendix A for pertinent aspects of the method and statistical analysis).
+Largely replicating earlier work \citep{Horoufchin2011, Horoufchin2011a}, the reduction in switch cost at extended RCIs was significantly larger when the RCI was different from the previous trial (right panel of Figure \ref{fig:grangeData}) than when it was the same (left panel of Figure \ref{fig:grangeData}), as reflected by the significant three-way interaction (see Appendix A for the ANOVA summary table).
+Thus, this data is in accordance with the temporal distinctiveness account, and cannot be easily explained by a decay account.
+
+\iftoggle{jou}{
+\begin{figure}
+\begin{center}
+\includegraphics[width = 0.5\textwidth]{Images/grangeData.pdf}
+\caption{Data from Grange (in preparation) showing mean response time in milliseconds (ms) for task repetition and switch trials as a function of the current response--cue interval (x-axis) and whether the RCI is the same or different from the previous trial.
+Error bars denote  +/- 1 standard error around the mean.}
+\label{fig:grangeData}
+\end{center}
+\end{figure}
+}{
+\begin{figure}
+\begin{center}
+\includegraphics[width = \textwidth]{Images/grangeData.pdf}
+\caption{Data from Grange (in preparation) showing mean response time in milliseconds (ms) for task repetition and switch trials as a function of the current response--cue interval (x-axis) and whether the RCI is the same or different from the previous trial.
+Error bars denote  +/- 1 standard error around the mean.}
+\label{fig:grangeData}
+\end{center}
+\end{figure}
+}
+
+% Table generated by Excel2LaTeX from sheet 'Sheet1'
+\begin{table}[htbp]
+  \centering
+  \caption{ANOVA summary table for response time data from Grange (in preparation).}
+    \begin{tabular}{rrrrr}
+    \toprule
+    Source & df    & \emph{F}     & \emph{p}     & $\eta_{g}^{2}$ \\
+    \midrule
+    Sequence (S) & 1 , 24 & 118.94 & $<$.001 & 0.469 \\
+    RCI (R) & 1 , 24 & 12.61 & 0.002 & 0.022 \\
+    RCI-Change (RC) & 1 , 24 & 15.68 & $<$.001 & 0.015 \\
+    S * R & 1 , 24 & 32.03 & $<$.001 & 0.024 \\
+    S * RC & 1 , 24 & 4.95  & 0.036 & 0.002 \\
+    R * RC & 1 , 24 & 12.26 & 0.002 & 0.021 \\
+    S * R * RC & 1 , 24 & 18.3  & $<$.001 & 0.008 \\
+    \bottomrule
+    \end{tabular}%
+  \label{tab:grangeData}%
+\end{table}%
+
 %%%--------------------------------------------------------------------------------------------
@@
 \subsubsection{Episodic Retrieval}
-The main processing stages in the model are shown in Figure \ref{fig:retrievalOverview}.
+The main processing stages in the model are shown in Figure \ref{fig:modelOverview}.
 The model assumes that, when presented with a task cue on a task repetition trial, the cognitive system attempts to retrieve the most recent episodic trace of this task (which was from trial n--1).
@@
 \begin{center}
-\includegraphics[width = 0.5 \textwidth]{Images/retrievalOverview.pdf}
+\includegraphics[width = 0.5 \textwidth]{Images/modelOverview.pdf}
 \caption{Overview of the retrieval processes in the model.}
-\label{fig:retrievalOverview}
+\label{fig:modelOverview}
 \end{center}
@@
 \begin{center}
-\includegraphics[width = \textwidth]{Images/retrievalOverview.pdf}
+\includegraphics[width = \textwidth]{Images/modelOverview.pdf}
 \caption{Overview of the retrieval processes in the model.}
-\label{fig:retrievalOverview}
+\label{fig:modelOverview}
 \end{center}
@@
 
-Figure \ref{fig:lbaAccumulation} shows how the LBA is applied in the current context.
+The Upper portion of Figure \ref{fig:modelOverview} shows how the LBA is applied in the current context.
 (Note that only the correct accumulators are shown to avoid clutter.) The model only ever uses one of two accumulation processes: If retrieval is successful, the model samples the current RT from a ``successful'', ``fast'' accumulation process with a higher drift rate, $v_{Fast}$; if retrieval fails, the current RT is sampled from an ``unsuccessful'', ``slow'' accumulation process with a lower drift rate, $v_{Slow}$.
-
-\iftoggle{jou}{
-\begin{figure}
-\begin{center}
-\includegraphics[width = 0.5 \textwidth]{Images/lbaAccumulation.pdf}
-\caption{Overview of the Linear Ballistic Accumulation Process for successful and unsuccessful retrieval.}
-\label{fig:lbaAccumulation}
-\end{center}
-\end{figure}
-}{
-\begin{figure}
-\begin{center}
-\includegraphics[width = 0.5 \textwidth]{Images/lbaAccumulation.pdf}
-\caption{Overview of the Linear Ballistic Accumulation Process for successful and unsuccessful retrieval.}
-\label{fig:lbaAccumulation}
-\end{center}
-\end{figure}
-}
 
@@
 %%%--------------------------------------------------------------------------------------------
+
+%%%--------------------------------------------------------------------------------------------
+\appendix
+\section{Method and Results of Grange's (in preparation) Behavioural Experiment}
+
+% Table generated by Excel2LaTeX from sheet 'Sheet1'
+\begin{table}[htbp]
+  \centering
+  \caption{ANOVA summary table for response time data from Grange (in preparation).}
+    \begin{tabular}{rrrrr}
+    \toprule
+    Source & df    & \emph{F}     & \emph{p}     & $\eta_{g}^{2}$ \\
+    \midrule
+    Sequence (S) & 1 , 24 & 118.94 & $<$.001 & 0.469 \\
+    RCI (R) & 1 , 24 & 12.61 & 0.002 & 0.022 \\
+    RCI-Change (RC) & 1 , 24 & 15.68 & $<$.001 & 0.015 \\
+    S * R & 1 , 24 & 32.03 & $<$.001 & 0.024 \\
+    S * RC & 1 , 24 & 4.95  & 0.036 & 0.002 \\
+    R * RC & 1 , 24 & 12.26 & 0.002 & 0.021 \\
+    S * R * RC & 1 , 24 & 18.3  & $<$.001 & 0.008 \\
+    \bottomrule
+    \end{tabular}%
+  \label{tab:grangeData}%
+\end{table}%
 

### 2015-11-04 2015/Temporal Distinctiveness & Mixture Distributions/Manuscript Files/main.tex
finished draft of manuscript

@@
 
-\abstract{.}
+\abstract{In task switching, increasing the response--cue interval has been shown to reduce the switch cost.
+This has been attributed to a time-based decay process influencing the activation of memory representations of tasks (task-sets).
+Recently, an alternative account based on interference rather than decay has been successfully applied to this data \citep{Horoufchin2011a}.
+In this account, variation of the RCI is thought to influence the \emph{temporal distinctiveness} (TD) of episodic traces in memory, thus affecting their retrieval probability.
+This can affect performance as retrieval probability influences response time: If retrieval succeeds, responding is fast due to positive priming; if retrieval fails, responding is slow, due to having to perform the task via a slow algorithmic process.
+This account---and a recent formal model \citep{Grange2015}---makes the strong prediction that all RTs are a mixture of one of two processes: a fast process when retrieval succeeds, and a slow process when retrieval fails.
+The present paper assesses the evidence for this \emph{mixture-distribution} assumption in TD data.
+In a first section, statistical evidence for mixture-distributions is found using the fixed-point property test.
+In a second section, a mathematical process model with mixture-distributions at its core is fitted to the response time distribution data.
+Both approaches provide good evidence in support of the mixture-distribution assumption, and thus support temporal distinctiveness accounts of the data.}
 
@@
 
+The task switching paradigm is a popular method for studying cognitive control \citep{Grange2014a, Kiesel2010, Vandierendonck2010}.
+Within this paradigm, participants are required to perform simple cognitive operations on multi-valent stimuli; for example, participants might be presented with numerical stimuli, and be asked to judge either whether the stimulus is odd/even (task A), or whether the stimulus is lower/higher than 5 (task B).
+Participants know which task to perform as they are presented with a cue informing them which task is relevant for the current trial (e.g., the word ``magnitude'' might cue the lower/higher task).
+It is a consistent finding that switching tasks (e.g., A--B) induces a performance cost in the form of increased response time (RT) and error rates compared to repeating the same task (e.g., A--A); this \emph{switch cost} has become the focus of intense research in an attempt to understand its underlying causes.
+
+More recently, research has started to focus on the nature of the memory representations used to perform these tasks.
+As the stimulus is usually not informative as to which task needs to be performed, a so-called ``task-set'' needs to be formed in working memory, which can be considered a collection of programmable task parameters (such as attentional bias etc.) critical to task performance \citep{Logan2001}; this task-set must be changed when the task changes.
+Therefore, a central goal for efficient cognitive control is to ensure that the relevant task-set is the most active among all competitors \citep[e.g.,][]{Altmann2008}.
+Therefore, an understanding of the dynamics of activation of task-sets is central to a complete understanding of the challenge facing cognitive control.
+
+Evidence from the task switching paradigm has provided several lines of evidence suggesting that activation levels of task-sets decay passively as a function of time.
+For example, \cite{Meiran2000a} varied the temporal separation between successive tasks via the response--cue interval (RCI), the time between the response to one task and the onset of the cue for the next task.
+These authors reported reduced switch costs at longer RCIs; this finding is in perfect accord with a decay account for two reasons: first, on task repetition trials, the previous task's activation will have had more time to decay at longer RCIs, meaning its ability to prime performance on the current trial will have reduced (leading to slower RTs); secondly, on task switch trials, the activation levels of the previous (now irrelevant) task-set will have decayed, inducing less proactive interference on the current trial (thus resulting in faster RTs).
+The net result is a reduced switch cost.
+
+However, this decay account was recently challenged by \cite{Horoufchin2011a} who manipulated RCI on a trial-to-trial basis between a short- (e.g., 50milliseconds, ms) and a long-RCI (1,000ms); they found that the reduction of switch cost was not a function of \emph{absolute} time of the RCI (e.g., between the previous trial n--1 and the current cue at n), but rather was a function of the ratio of the current RCI to that from the previous trial (between trials n--2 and n--1).
+Specifically, the switch cost was only reduced at longer RCIs when the previous RCI was short; when the previous RCI was also long, switch costs were not reduced.
+These effects were primarily localised to task repetition RT; task switch RT was not influenced by RCI or the RCI-ratio.
+
+\cite{Horoufchin2011a} claimed these findings supported an \emph{interference} account of RCI effects, and were not compatible with a decay account.
+Relating to a temporal ratio model of serial memory \citep[SIMPLE][]{Brown2007}, the authors stated that when presented with a cue on the current trial, the cognitive system engages in a retrieval attempt of the previous episodic memory trace of this task; such retrieval attempts have been shown by \cite{Brown2007} to be influenced by the \emph{temporal distinctiveness} (TD) of this episodic trace.
+TD refers to the degree to which the targeted episodic trace is distinguishable in memory from competing memory traces presented within a similar time-window to that of the target trace.
+Traces that are clustered closely in episodic memory will not be distinguishable, and thus have low TD and will have low probability to be retrieved.
+The sequential varying of the RCI was suggested to affect the TD of the targeted episodic trace in memory.
+TD is operationalised in relation to the RCI ratio, which is the ratio of the RCI(n--2:n--1) / RCI(n--1:current trial).
+See Figure \ref{fig:tdAccount} for various examples of how RCI ratio influences the TD of target episodic traces.
+
 \begin{figure} 
@@
 \includegraphics[width = 0.5 \textwidth]{Images/tdAccount.pdf}
-\caption{Schematic overview of the temporal distinctiveness account of response--cue interval effects in task switching. See text for details.}
+\caption{Various manipulations of temporal distinctiveness as used by \cite{Horoufchin2011, Horoufchin2011a}.
+Task instances are represented by circles, and time runs from left to right.
+The current trial's cue is represented by the far-right circle; the episodic trace of the previous task is the middle circle, and the episodic trace of the task from two trials ago is the far-left circle.
+The RCI between each trace is shown for each row.
+The ratio is calculated as RCI(n--2:n--1) / RCI(n--1:current trial).
+See text for more details.}
 \label{fig:tdAccount}
@@
 
-%%%--------------------------------------------------------------------------------------------
-\section{Behavioural Data}
-Describe the gist of the method, and provide a plot of the pertinent data.
+When RCI-ratio is high, so too is TD, which means there is a high probability the episodic trace can be retrieved; successful retrieval primes performance, leading to a fast RT.
+When the RCI-ratio is low, so too is TD, which lowers the probability of successful retrieval.
+When retrieval fails, the task must be performed via a slower, algorithmic route, leading to a slower RT \citep[see][for a similar proposal]{Logan2001}.
+Intermediate RCI-ratios lead to intermediate levels of TD; therefore, a proportion of these trials will have successful retrieval, and some trials will have failed retrieval.
 
-Consider a portion of data reported by Grange (in revision), which can be seen in Figure \ref{fig:grangeData} (see Appendix A for pertinent aspects of the method and statistical analysis).
-Largely replicating earlier work \citep{Horoufchin2011, Horoufchin2011a}, the reduction in switch cost at extended RCIs was significantly larger when the RCI was different from the previous trial (right panel of Figure \ref{fig:grangeData}) than when it was the same (left panel of Figure \ref{fig:grangeData}), as reflected by the significant three-way interaction (see Appendix A for the ANOVA summary table).
-Thus, this data is in accordance with the temporal distinctiveness account, and cannot be easily explained by a decay account.
+Figure \ref{fig:grangeData} represents a portion of data reported by \cite{Grangeinrevision}; a brief overview of the pertinent method details and analysis are presented in Appendix A) that replicates the main findings from \cite{Horoufchin2011a}; focussing on repetition RTs, increasing RCI from 50ms to 1,000ms has negligible effect on RTs when the RCI was the same as the previous trial (e.g., these data points relate to D and C in Figure \ref{fig:tdAccount}); this is because both of these conditions have an identical RCI-ratio of 1, and hence have the same TD.
+RCI has a considerable effect on repetition RT when the RCI has changed from the previous trial: RT is very fast when the RCI is 50ms, as this condition has a very high RCI-ratio, hence high TD (Figure \ref{fig:tdAccount} A); RT is very slow when the RCI is 1,000ms, as this condition has a very low RCI-ratio, hence low TD (Figure \ref{fig:tdAccount} B).
 
@@
 \includegraphics[width = 0.5\textwidth]{Images/grangeData.pdf}
-\caption{Data from Grange (in preparation) showing mean response time in milliseconds (ms) for task repetition and switch trials as a function of the current response--cue interval (x-axis) and whether the RCI is the same or different from the previous trial.
+\caption{Data from \cite{Grangeinrevision} showing mean response time in milliseconds (ms) for task repetition and switch trials as a function of the current response--cue interval (x-axis) and whether the RCI is the same or different from the previous trial.
 Error bars denote  +/- 1 standard error around the mean.}
@@
 \includegraphics[width = \textwidth]{Images/grangeData.pdf}
-\caption{Data from Grange (in preparation) showing mean response time in milliseconds (ms) for task repetition and switch trials as a function of the current response--cue interval (x-axis) and whether the RCI is the same or different from the previous trial.
+\caption{Data from \cite{Grangeinrevision} showing mean response time in milliseconds (ms) for task repetition and switch trials as a function of the current response--cue interval (x-axis) and whether the RCI is the same or different from the previous trial.
 Error bars denote  +/- 1 standard error around the mean.}
@@
 
-% Table generated by Excel2LaTeX from sheet 'Sheet1'
-\begin{table}[htbp]
-  \centering
-  \caption{ANOVA summary table for response time data from Grange (in preparation).}
-    \begin{tabular}{rrrrr}
-    \toprule
-    Source & df    & \emph{F}     & \emph{p}     & $\eta_{g}^{2}$ \\
-    \midrule
-    Sequence (S) & 1 , 24 & 118.94 & $<$.001 & 0.469 \\
-    RCI (R) & 1 , 24 & 12.61 & 0.002 & 0.022 \\
-    RCI-Change (RC) & 1 , 24 & 15.68 & $<$.001 & 0.015 \\
-    S * R & 1 , 24 & 32.03 & $<$.001 & 0.024 \\
-    S * RC & 1 , 24 & 4.95  & 0.036 & 0.002 \\
-    R * RC & 1 , 24 & 12.26 & 0.002 & 0.021 \\
-    S * R * RC & 1 , 24 & 18.3  & $<$.001 & 0.008 \\
-    \bottomrule
-    \end{tabular}%
-  \label{tab:grangeData}%
-\end{table}%
+Note that a decay account cannot explain this data, as it would predict identical slowing of repetition RTs at longer RCIs \emph{regardless} of the RCI on the previous trial (whether it was the same or different to that of the previous trial).
+Thus, this data presents a strong challenge to the decay account of task-sets.
 
+%%%--------------------------------------------------------------------------------------------
+\section{The Current Study}
+
+Given the important of the dynamics of task-sets for the development of theoretical accounts of task switching \citep[e.g.,][]{Altmann2008, Schneider2005}, the temporal distinctiveness account provides an important challenge to our understanding of cognitive control in task switching.
+Given this importance, \cite{Grange2015} developed a basic mathematical model of TD effects using SIMPLE \citep{Brown2007} to calculate the TD for a range of RCI-ratios, and in turn to predict mean RT for a range of RCI-ratios.
+
+In this model---using the mathematics of SIMPLE---the RCI-ratio can be translated in to a measure of the \emph{Distinctiveness} of an episodic trace.
+Distinctiveness is proportional to the probability of retrieving this episodic trace, denoted $p$(retrieval).
+As per the verbal theory of \cite{Horoufchin2011a} it is assumed that if retrieval succeeds, the response for that trial will be sampled from a fast RT process, with mean $\mu_{Fast}$; if retrieval fails, the response for that trial will be sampled from a slow RT process, with mean $\mu_{Slow}$.
+Therefore, trials with high RCI-ratio (e.g., 20) will have high TD, and therefore high $p$(retrieved), meaning many trials will be sampled from the fast RT process; trials with low RCI-ratio (e.g., 0.05) will have low TD, and hence low $p$(retrieved), meaning many trials will be sampled from the slow process.
+
+In the model, mean RT for a given trial is predicted by
+
+\begin{equation}
+RT = p(retrieved) \times \mu_{Fast} + [1 - p(retrieved)] \times \mu_{Slow}.
+\label{eq:simpleMixture}
+\end{equation}
+
+Importantly, this model assumes that all RTs are being sampled from only one of two processes: a fast and a slow process.
+Therefore, trials with intermediate RCI-ratios (e.g., 1) will have intermediate TDs, and therefore intermediate p(retrieved); this means that intermediate RCI-ratio RTs will be a mixture of RTs from the fast process and RTs from the slow process, with the exact proportion of mixture related to $p$(retrieved).
+
+The purpose of the present study is to assess in more detail the validity of this key prediction of the temporal distinctiveness account: that intermediate RCI-ratio RTs are a mixture of samples from a fast process and a slow process.
+I call this assumption the \emph{mixture-distribution} assumption.
+
+I approach this assessment in two ways.
+In the first, I use a statistical test---the fixed-point property test---to assess the presence/absence of evidence for intermediate RCI-ratios being a mixture of a fast and a slow distribution.
+Then, in a next step I extend the model of \cite{Grange2015} to predict whole RT-distributions, which allows a direct test of the mixture-distribution assumption.
+The article ends with discussion of implications of these findings for the TD account of RCI effects in task switching.
 %%%--------------------------------------------------------------------------------------------
@@
 \subsection{Application to the Data}
-The data was assessed for the presence of a mixture distribution.
+The task repetition data from Figure \ref{fig:grangeData} was assessed for the presence of a fixed-point property.
+In this test, the RCI-ratio of 20 can be considered the ``fast'' condition, and the RCI-ratio of 0.05 can be considered the ``slow'' distribution.
+The critical question is whether intermediate RCI-ratios of 1 are a mixture of the fast and the slow distribution.
+
+Data were trimmed before testing.
 Correct RTs were first trimmed to retain RTs slower than 150 milliseconds, and RTs faster than 2.5 standard deviations above each subjects' mean RT.
@@
 \includegraphics[width = \textwidth]{Images/mixtureDistributionData.pdf}
-\caption{Example of the fixed-point property in three distributions.
-Distribution $z$ is a mixture of distributions $x$ and $y$ with mixture probability $p$ set to $p$ = 0.7.
-The left panel shows the probability densities for each distribution.
-The right panel shows the density difference between different density functions.
-The distributions share a common crossing point at about 0.850 seconds.}
+\caption{Test of the fixed-point property in three distributions from \cite{Grangeinrevision}.
+The left panel shows the individual density functions for each condition of RCI-ratio (1 = 0.05, 2 = 1, 3 = 20).
+The middle panel shows ``crossing points'': the subtraction of pairs of density functions (indicated in legend).
+The right panel shows box-plots for the distribution of crossing points for individual participants in the study.}
 \label{fig:mixtureDistributionData}
@@
 As shown in the left and center panels of Figure \ref{fig:mixtureDistributionData}, the three RT distribution functions share a common crossing point at just over 1 second.
-The right panel of Figure \ref{fig:mixtureDistributionData} shows boxplots of the distribution of crossing points for each pair for all subjects.
-There is considerable overlap in the boxplots suggesting no difference between condition pairs of crossing point (supporting the fixed-point hypothesis).
-Together, this visual inspection provides good evidence that the ratio = 1 RT function is a weighted mixture of the ``slow'' RT distribution (where ratio = 0.05) and the ``fast'' RT distribution (where ratio = 20), as predicted by the temporal distinctiveness model \cite{Grange2015}.
+The right panel of Figure \ref{fig:mixtureDistributionData} shows box-plots of the distribution of crossing points for each pair for all subjects.
+There is considerable overlap in the box-plots suggesting no difference between condition pairs of crossing point (supporting the fixed-point property).
+Together, this visual inspection provides good evidence that the RCI-ratio = 1 RT function is a weighted mixture of the ``slow'' RT distribution (where RCI-ratio = 0.05) and the ``fast'' RT distribution (where RCI-ratio = 20), as predicted by the temporal distinctiveness model \cite{Grange2015}.
 
@@
 The dependent variable in this analysis---shown in the x-axis of that Figure---is the crossing point in seconds for the density difference.
-This analysis was not statistically significant [\emph{F}(2, 48) = 1.25, \emph{p} = .295].
-However, the presence of a common crossing point requires the acceptance of a null hypothesis (i.e., of no difference in crossing points), which cannot be achieved via standard statistical analysis.
+This analysis was not statistically significant [\emph{F}(2, 48) = 1.25, \emph{p} = .295], which provides no reason to reject the null hypothesis of a common crossing point.
+However, to confirm the statistical \emph{presence} of a common crossing point requires the acceptance of a null hypothesis which cannot be achieved via standard null hypothesis significance testing.
 Therefore, a default Bayesian ANOVA \cite{Rouder2012} was conducted on the same data, which produces a Bayes Factor; the Bayes Factor---denoted $BF_{01}$---assesses the evidence in favour of a model assuming a common crossing point (i.e., a ``null'' model) compared to a model assuming multiple crossing points (i.e., an ``alternative'' model).
 The Bayes Factor for this data was $BF_{01}$ = 3.354, suggesting the data are 3.4 times more likely under the model assuming a common crossing point.
-Together, these statistical analyses converge on the conclusion that the RT distributions share a common crossing point, and as such can be considered support for the mixture-distribution hypothesis.
+Together, these statistical analyses converge on the conclusion that the RT distributions share a common crossing point, and as such can be considered support for the mixture-distribution assumption.
 
@@
 The previous section provided statistical support for the presence of a mixture-distribution for intermediate RCI ratios (i.e., intermediate levels of temporal distinctiveness).
-This is in agreement both with the verbal theory regarding TD effects \cite{Horoufchin2011a} and its formal implementation \cite{Grange2015}, which explains performance across TD ratios.
-In this section I develop a mathematical process model to predict RT distributions of TD data.
+This is in agreement both with the verbal theory regarding TD effects \cite{Horoufchin2011a} and its formal implementation \cite{Grange2015}, which explains performance across RCI-ratios.
+In this section I develop a mathematical process model to predict RT distributions of RCI-ratio data.
 The fitting of whole RT distributions presents an important advance over the model of \citet{Grange2015}, as it allows a direct test---rather than a relatively indirect test from fitting mean RTs---of that model's core assumption: that intermediate TD performance is a weighted mixture of ``retrieved'' and ``not-retrieved'' processing modes, which lead to fast and slow RTs, respectively.
 
-In this section, I first provide a schematic overview of the assumptions of the model. The mathematical details of the model are in Appendix B.
+In this section, I provide a schematic overview of the assumptions of the model. The mathematical details of the model are in Appendix B.
 
@@
 \subsection{Overview of the Model}
+The model describes two stages to performance: an episodic retrieval attempt of the target trace, and an evidence accumulation process that generates a response; the rate of evidence accumulation towards a response depends on whether the trace was retrieved or not, with accumulation rates being faster for successfully retrieved traces.
+The main processing stages in the model are shown in Figure \ref{fig:modelOverview}.
 
 \subsubsection{Episodic Retrieval}
-The main processing stages in the model are shown in Figure \ref{fig:modelOverview}.
  The model assumes that, when presented with a task cue on a task repetition trial, the cognitive system attempts to retrieve the most recent episodic trace of this task (which was from trial n--1).
@@
 
-Retrieval probability---$p$(retrieval)---influences the speed of retrieval.
+The retrieval probability---$p$(retrieval)---influences the speed of responding.
 If retrieval succeeds, the response is facilitated due to retrieval of elements of the previous episodic trace that prime performance on the current trial; if retrieval fails, the response is not facilitated, and thus responding is slower as it has to be performed via a slower, algorithmic, route \citep[see][for discussion]{Grange2015}.
 
-\subsection{RT Distributions}
-To predict response time distributions, the mathematics of the Linear Ballistic Accumulator (ref) was used.
+\subsubsection{RT Distributions}
+To predict response time distributions, the mathematics of the Linear Ballistic Accumulator \citep{Brown2008} was used.
 The LBA is a successful model of choice response time, allowing the modelling of correct and error RT distributions.
@@
 The LBA model has several parameters.
-The mean rate of evidence accumulation is referred to as the \emph{drift rate}, $v$; it is larger for the correct response than for the error response.
-The drift rate for each accumulator can vary on each trial, but is assumed to have a fixed mean rate.
+The mean rate of evidence accumulation is referred to as the \emph{drift rate}, $v$; it is higher for the correct response than for the error response.
+The drift rate for each accumulator can vary across trials, but is assumed to have a fixed mean rate.
 The drift rate on each trial is a random draw from a normal distribution with mean $v$ and standard deviation $s$.
@@
 The Upper portion of Figure \ref{fig:modelOverview} shows how the LBA is applied in the current context.
-(Note that only the correct accumulators are shown to avoid clutter.) The model only ever uses one of two accumulation processes: If retrieval is successful, the model samples the current RT from a ``successful'', ``fast'' accumulation process with a higher drift rate, $v_{Fast}$; if retrieval fails, the current RT is sampled from an ``unsuccessful'', ``slow'' accumulation process with a lower drift rate, $v_{Slow}$.
+(Note that only the correct accumulators are shown to avoid clutter.) The model only ever uses one of two accumulation processes: If retrieval is successful (with probability $p$[retrieval]), the model samples the current RT from a ``successful'', ``fast'' accumulation process with a higher drift rate, $v_{Fast}$; if retrieval fails (with probability 1 -- $p$[retrieval]), the current RT is sampled from an ``unsuccessful'', ``slow'' accumulation process with a lower drift rate, $v_{Slow}$.
 
@@
 
-\citet{Grange2015} used the full mathematics of SIMPLE to obtain $p$(retrieved).
+\cite{Grange2015} used the full mathematics of SIMPLE to obtain $p$(retrieved).
 To reduce the number of free parameters, in the current model $p$(retrieved) was treated as a ``semi-fixed'' parameter.
-To acieve this, the TD ratio was calculated for each RCI-sequence condition in Figure (dataPlot).
-Specifically, the RCI ratio was 20 for n--2 to n--1 RCIs of 50ms--1000ms; the ratio was 1 for RCIs of 1000ms--1000ms and 50ms--50ms; and the ratio was 0.05 for RCIs of 50ms--1,000ms.
+To achieve this, the RCI-ratio was calculated for each RCI-sequence condition in Figure \ref{fig:grangeData}.
+Specifically, the RCI-ratio was 20 for n--2 to n--1 RCIs of 50ms--1000ms; the ratio was 1 for RCIs of 1000ms--1000ms and 50ms--50ms; and the ratio was 0.05 for RCIs of 50ms--1,000ms.
 
@@
 Note therefore that this fit is rather ambitious.
-First, the model has to explain whole RT distributions for correct and error responses across all three conditions of RCI ratio; that is 30 data points with just 8 parameters.
-Also, the data for ratio = 1 is never explicitly modelled; rather, the model is fit to the ratio = 20 with a fast distribution and to ratio = 0.05 data with a slow distribution; the data for ratio = 1 is then estimated by a weighted contribution of the two distributions controlled only by $p$(retrieved)).
+First, the model has to explain whole RT distributions for correct and error responses across all three conditions of RCI ratio.
+Also, the data for RCI-ratio = 1 is never explicitly modelled; rather, the model is fit to the RCI-ratio = 20 with a fast distribution and to RCI-ratio = 0.05 data with a slow distribution; the data for RCI-ratio = 1 is then estimated by a weighted contribution of the two distributions controlled only by $p$(retrieved)).
 
@@
 \includegraphics[width = \textwidth]{Images/qmp2RCI_drift_+_b.pdf}
-\caption{Model fit.}
+\caption{Defective cumulative distribution functions for the behavioural data and the model fit for all RCI-ratios (0.05, 1, \& 20) for correct and error RT distributions.}
 \label{fig:modelFit}
@@
 This Figure presents so-called ``defective'' cumulative distribution functions (CDFs).
-The data are sorted from fastest to slowest, and then quantile cut-off points are calculated for each subject according to a pre-specified set of quantiles $\vec{q}$ (here $\vec{q}$ = .1, .3, .5, .7, .9).
+The data are sorted from fastest to slowest, and then quantile cut-off points are calculated for each subject according to a pre-specified set of quantiles $\vec{Q}$ (here $\vec{Q}$ = .1, .3, .5, .7, .9).
 The Figure plots the average RT for each quantile across subjects against the quantile value.
 The plot is a defective CDF in the sense that it also displays information about errors.
-Specifically, RT is plotted against $\vec{q}$ * mean accuracy rather than just $\vec{q}$.
-Error RT---shown in the Figure as open circles)---is error RT plotted against $\vec{q}$ * (1 - mean accuracy).
+Specifically, RT is plotted against $\vec{q}$ $\times$ mean accuracy rather than just $\vec{q}$.
+Error RT---shown in the Figure as open circles)---is error RT plotted against $\vec{q}$ $\times$ (1 - mean accuracy).
 
@@
 The fit to the error RT distributions is not as good as for the correct RT distributions.
-However, accuracy was generally very high in this experiment (indeed, participants were excluded for not achieving greater than 90\% accuracy).
+However, accuracy was generally very high in this experiment (indeed, participants were excluded for not achieving greater than 80\% accuracy).
 So, there were often few error RTs per quantile bin during the model fit, making accurate estimation difficult.
-However, dispite the poor quantitative fit, the qualitative pattern seen in the human data is generally reproduced: error RT becomes generally faster and less variable as ratio increases.
+However, despite the poor quantitative fit, the qualitative pattern seen in the behavioural data is generally reproduced: error RT becomes generally faster and less variable as ratio increases.
+
+In sum, this mixture-model provides a good account of the behavioural data.
 %%%--------------------------------------------------------------------------------------------
@@
 
+In this paper, I was interested in assessing a key prediction from the temporal distinctiveness account of RCI effects in task switching: namely, that all responses are governed by one of only two processes: a ``fast'' process when an episodic trace is successfully retrieved, and a ``slow'' process when episodic retrieval fails.
+This account makes a specific prediction that intermediate RCI-ratios should be a mixture-distribution of a fast RT distribution and a slow RT distribution.
+
+This prediction was largely supported.
+In the first section, I provide evidence that the data support the fixed-point property of mixture distributions.
+In the second section I developed a mixture-distribution model that extends the model of \cite{Grange2015} to explain whole RT-distributions.
+As the model is forced to only sample from one of two processes, finding agreement between behavioural data and model predictions provides support for the mixture-distribution assumption.
+Generally, this condition was met, with overall good fit of the model to correct RT distributions; the fit to the error distributions was not so clear, although the qualitative pattern was reproduced.
+The modelling in this paper presents a ``proof of concept'' of the mixture-distribution assumption rather than being designed to be a complete explanation of temporal distinctiveness effects in task switching, so the fit can be considered successful in this regard.
+
+\subsection{Model Parameters}
+The fit of the model to the data allowed estimation of a number of important parameters, which might shed some light on explaining performance in RCI-ratio experiments.
+Importantly, the drift rate was estimated to be higher in the RCI-ratio 20 condition (i.e., $v_{Fast}$) than in the RCI-ratio 0.05 condition ($v_{Slow}$.
+This suggests that successful retrieval of the target episodic trace leads to faster RTs due to a speed-up in evidence accumulation for a response.
+In addition, the response boundary parameter $b$ was reduced when retrieval failed (i.e., $v_{Slow}$.
+This raises the interesting possibility that when the cognitive system fails to retrieve the targeted episodic trace, it enters a more cautious mode of responding by raising $b$; this might be in some way to compensate for the reduced efficiency of evidence accumulation when retrieval fails ($v_{Slow}$).
+
+\subsection{Switch Trials}
+Here it is important to note that a complete model of TD effects in task switching will need to account for performance on switch trials.
+Typically, RCI-ratio does not appear to affect switch RT \citep{Horoufchin2011, Horoufchin2011a} which is why the present focus has been on repetition RTs only.
+The model presented here can easily be extended to account for switch RT performance by adding new LBA parameters for switch trials (e.g., $v_{Switch}$, $A_{Switch}$, $b_{Switch}$, and possibly $s_{Switch}$ and  $ter_{Switch}$.
+As RCI-ratio does not typically affect switch trials, it can be assumed that retrieval always fails on switch trials, so $p(retrieved)$ can be set to zero for all RCI-ratio conditions.
+
+\section{Conclusion}
+In sum, this paper has provided support for the TD account of RCI effects in task switching.
+This presents an important challenge to models of cognitive control during task switching which assume control systems work to prevent relevant task-sets decaying.
+Instead, loss of retrieval of task-sets appears to be well-explained by interference effects rather than time-based decay.
+
 %%%--------------------------------------------------------------------------------------------
@@
 \appendix
-\section{Method and Results of Grange's (in preparation) Behavioural Experiment}
+\section{Method and Results \citep{Grangeinrevision}}
+The data presented in Figure \ref{fig:grangeData} presents a portion of the overall data presented by \cite{Grangeinrevision}.
+Speficially, this data comes from the ``categorisation'' condition.
+In this condition, 25 participants were presented with a 2x2 square grid.
+Two arrow cues either pointed up and down (presented above and below the grid, respectively) or left and right (presented to the left and to the right of the grid, respectively).
+100ms later, a stimulus appeared in one of the grid cells.
+The stimulus could be an A or a 4, presented in either red or blue font.
+If the arrows pointed up and down, the participants had to judge whether the stimulus was an A or a 4; if the arrows pointed left and right, the participants had to judge whether the stimulus was red or blue.
+Participants responded using the ``1'' and the ``9'' keys on the numerical part of the keyboard; 1 corresponded to ``letter'' and ``red'' responses, and 9 corresponded to ``number'' and ``blue'' responses.
+Once a response was registered, the grid was cleared for an RCI of either 50ms or 1,000ms (chosen randomly).
+The next task was chosen randomly.
+In total, participants were presented with 6 blocks of 64 trials, preceded by 16 practice trials.
+
+The ANOVA summary table for this data are shown in Table \ref{tab:grangeData}.
 
@@
   \centering
-  \caption{ANOVA summary table for response time data from Grange (in preparation).}
+  \caption{ANOVA summary table for response time data from \cite{Grangeinrevision}.}
     \begin{tabular}{rrrrr}
@@
 \section{Overview of Grange \& Cross (2015) Model}
-The \citet{Grange2015} model used the mathematics of the SIMPLE \cite{Brown2007} model to account for TD effects on task repetition trials.
+The \cite{Grange2015} model used the full mathematics of the SIMPLE \cite{Brown2007} model to account for TD effects on task repetition trials.
 Distinctiveness is proportional to the \emph{similarity} between a target trace and its neighbours in episodic memory.
 In this model, similarity is only influenced by the temporal domain.
-Similarity of instances at n--1 (item $i$) and n--2 (item $j$) is given by
+Similarity of episodic instances at n--1 (item $i$) and n--2 (item $j$) is given by
 
@@
 
-\noindent where $T_{x}$ refers to the temporal age of an item. Temporal age is calculated from the current time.
-
-Based on the target traces $i$'s similarity, to its neighbours, its discriminability $D_{i}$ can be determined. This refers to how isolated the target trace $i$ is in episodic memory, and is given by
+\noindent where $T_{x}$ refers to the temporal age of an item.
+Temporal age is calculated from the current time.
+Based on the target traces $i$'s similarity, to its neighbours, its discriminability $D_{i}$ can be determined.
+This refers to how isolated the target trace $i$ is in episodic memory, and is given by
 
@@
 
-\noindent where $s$ and $t$ are free parameters which descibe the sloe of the transforming function and the threshold of retrieval, respectively.
-
+\noindent where $s$ and $t$ are free parameters which describe the slope of the transforming function and the threshold of retrieval, respectively.
 Given these equations, we can calculate the retrieval probability for each level of temporal distinctiveness in the behavioural experiment.
-It is assumed that if the trace is retrieved (with probability $p$) then response time will be a random draw from a fast RT distribution with mean $\mu_{fast}$; if retrieval fails (with probability $1 - p$), the response time will be a random draw from a slow RT distribution with mean $\mu_{slow}$.
+It is assumed that if the trace is retrieved (with probability $p$[retrieved]) then response time will be a random draw from a fast RT distribution with mean $\mu_{fast}$; if retrieval fails (with probability $1 - p$[retrieved]), the response time will be a random draw from a slow RT distribution with mean $\mu_{slow}$.
 Thus, mean RT for each level of TD is given by the RT-mixture equation
@@
 \begin{equation}
-RT = p\mu_{Fast} + (1 - p)\mu_{slow}.
+RT = p(retrieved) \times \mu_{Fast} + [1 - p(retrieved)] \times \mu_{slow}.
 \label{eq:tdMixtureNew}
@@
 
-\subsubsection{LBA for Unitary Process}
-In the LBA for a unitary process (i.e., not a mixture model), evidence for response $i$ has a CDF (at time \emph{t}) of
+This section describes the details of the mixture-distribution model.
+The model extends the mathematics of the linear ballistic accumulator \cite{Brown2008} for a unitary process (i.e., not a mixture model), which allows calculation of the defective probability density function of one response accumulator reaching retrieval threshold before the accumulator for the second response does.
+I first describe the mathematics of the LBA for a unitary process before describing how this can be extended to a mixture model.
+
+\subsection{LBA for Unitary Process}
+For a unitary process, to calculate the defective PDF of response option $i$ reaching threshold first (before $j$), one first needs the cumulative distribution function (CDF) for $i$ at time $t$, $F_{i}(t)$, given the model parameters $v$, $A$, $s$, and $t$ = $t - ter$), is given by
 
@@
 
-\noindent (where $\Phi$ refers to the normal distribution's CDF) and a PDF of
+\noindent (where $\Phi$ refers to the normal distribution's CDF). Then one needs the probability density function (PDF) of $i$ at time $t$, $f_{i}(t)$ given by
 
@@
 
-\noindent where $\phi$ refers to the normal distribution's density. Considering two accumulators $i$ and $j$ (e.g., correct \& error response, respectively), the PDF for $i$ at time $t$ is given by
+\noindent where $\phi$ refers to the normal distribution's density.
+Considering two accumulators $i$ and $j$ (e.g., correct \& error response, respectively), the defective PDF for $i$ at time $t$ is given by
 
@@
 
-\subsubsection{Modelling Mixture Distributions}
-If we denote the fast accumulation process as $\gamma$ and the slow accumulation process as $\lambda$, recall that mean RT can be predicted by
+\subsection{Modelling Mixture-Distributions}
+Extending this to a mixture-distribution model is as follows. If we denote the fast accumulation process as $Fast$ and the slow accumulation process as $Slow$, recall that mean RT can be predicted by
 
 \begin{equation}
-RT = p\mu_{\gamma} + (1 - p)\mu_{\lambda}.
+RT = p\mu_{Fast} + (1 - p)\mu_{Slow}.
 \end{equation}
 
-Extending this mixture model to a likelihood function, we can now obtain the PDF for response $i$ (rather than response $j$) at time $t$ by
+Extending this mixture-distribution model to a likelihood function from the LBA, we can now obtain the PDF for response $i$ (rather than response $j$) at time $t$ by
 
@@
 \begin{aligned}
-\mbox{PDF}_{i} = &\left[p \cdot f_{\gamma i}(1 - F_{\gamma j})\right] + \\ 
-&\qquad \left[(1 - p) \cdot f_{\lambda i}\right] (1 - F_{\lambda j})
+\mbox{PDF}_{i} = & \left[p \cdot f_{Fast[i]}(1 - F_{Fast[j]})\right] + \\ 
+&\qquad \left[(1 - p) \cdot f_{Slow[i]}\right] (1 - F_{Slow[j]})
 \end{aligned}
@@
 
+\subsection{Model Fit Details}
+The model was fit to the data via a variant of the QMPE method \citep{Heathcote2002}.
+Specifically, the average quantile cut-off values were found for correct and error responses for each condition and accuracy response.
+The quantiles used were 0.1, 0.3, 0.5, 0.7, and 0.9.
+So, RTs for each each quantile value were stored in the vector $\vec{Q}$ with length $q$ such that $\vec{Q}$ = $RT_{0.1}$ \ldots $RT_{0.9}$.
+The number of RTs in each bin (i.e., in the range 0--$\vec{Q}$--1) were stored in the vector $\vec{N}$ with length $n$.
+Then, the defective cumulative distribution function $F$ at time $t$ = $t-ter$, $F(t)$\footnote{Obtained via numerical integration of Equation \ref{eq:tdLikelihood} at time $t$.}, given model parameters $\vec{\theta}$ was calculated, and multiplied by the number of trials within that bin to obtain the likeilihood $L$
+
+\begin{equation}
+\begin{aligned}
+L_{M}\left(\vec{\theta} | \vec{Q}, \vec{N}\right) & \propto ln\left[F\left(Q_{1}:\vec{\theta}\right) - F\left(0:\vec{\theta}\right)\right]N_{1} \\ 
+& \qquad \times ln\left[F\left(Q_{i}:\vec{\theta}\right) - F\left(Q_{i - 1}:\vec{\theta}\right)\right]N_{i} \\
+& \qquad \times \ldots \\
+& \qquad \times ln\left[F\left(\infty:\vec{\theta}\right) - F\left(Q_{q}:\vec{\theta}\right)\right]N_{n}, \\
+\end{aligned}
+\label{eq:qmp}
+\end{equation}
+
+\noindent where $ln$ is the natural logarithm.
+
+This was performed for each RCI-ratio condition for correct and error responses, and the likelihoods for each were summed.
+The fit routine aimed to find the best-fitting parameters that minimised the negative summed likelihood; the Nelder-Mead method using R's \texttt{optim} was used to fit the model.
+Starting values for the parameter search utilised the starting heuristics recommended by  \cite{Donkin2011}.
+
+%%%--------------------------------------------------------------------------------------------
+
+%%%--------------------------------------------------------------------------------------------
 \bibliography{References.bib}

### 2015-11-05 2015/Temporal Distinctiveness & Mixture Distributions/Manuscript Files/main.tex
final draft of manuscript

@@
 
-\note{{\bf Word Count:} x,xxx (Main body, not including abstract or references.)}
+\note{{\bf Word Count:} 4,816 (Main body, not including abstract or references.)}
 % \note{{\bf Under Review---Please, no direct quotes.}}
@@
 Email: grange.jim@gmail.com.
+I am grateful to Chris Donkin for discussion regarding the Linear Ballistic Accumulator model.
 All raw data, analysis code, and model code are available to download at http://bit.ly/1l22EUV.}
@@
 As the stimulus is usually not informative as to which task needs to be performed, a so-called ``task-set'' needs to be formed in working memory, which can be considered a collection of programmable task parameters (such as attentional bias etc.) critical to task performance \citep{Logan2001}; this task-set must be changed when the task changes.
-Therefore, a central goal for efficient cognitive control is to ensure that the relevant task-set is the most active among all competitors \citep[e.g.,][]{Altmann2008}.
+A central goal for efficient cognitive control is to ensure that the relevant task-set is the most active among all competitors \citep[e.g.,][]{Altmann2008}.
 Therefore, an understanding of the dynamics of activation of task-sets is central to a complete understanding of the challenge facing cognitive control.
@@
 
-\cite{Horoufchin2011a} claimed these findings supported an \emph{interference} account of RCI effects, and were not compatible with a decay account.
-Relating to a temporal ratio model of serial memory \citep[SIMPLE][]{Brown2007}, the authors stated that when presented with a cue on the current trial, the cognitive system engages in a retrieval attempt of the previous episodic memory trace of this task; such retrieval attempts have been shown by \cite{Brown2007} to be influenced by the \emph{temporal distinctiveness} (TD) of this episodic trace.
+\cite{Horoufchin2011a} proposed these findings supported an \emph{interference} account of RCI effects, and were not compatible with a decay account.
+Relating to a temporal ratio model of serial memory \citep[SIMPLE][]{Brown2007}, the authors suggested that when presented with a cue on the current trial, the cognitive system engages in a retrieval attempt of the previous episodic memory trace of this task; such retrieval attempts have been shown by \cite{Brown2007} to be influenced by the \emph{temporal distinctiveness} (TD) of the episodic trace.
 TD refers to the degree to which the targeted episodic trace is distinguishable in memory from competing memory traces presented within a similar time-window to that of the target trace.
@@
 The sequential varying of the RCI was suggested to affect the TD of the targeted episodic trace in memory.
-TD is operationalised in relation to the RCI ratio, which is the ratio of the RCI(n--2:n--1) / RCI(n--1:current trial).
-See Figure \ref{fig:tdAccount} for various examples of how RCI ratio influences the TD of target episodic traces.
+TD is operationalised in relation to the RCI-ratio, which is the ratio of the RCI(n--2:n--1) / RCI(n--1:current trial).
+See Figure \ref{fig:tdAccount} for how various RCI-ratios are calculated.
 
@@
 
-Figure \ref{fig:grangeData} represents a portion of data reported by \cite{Grangeinrevision}; a brief overview of the pertinent method details and analysis are presented in Appendix A) that replicates the main findings from \cite{Horoufchin2011a}; focussing on repetition RTs, increasing RCI from 50ms to 1,000ms has negligible effect on RTs when the RCI was the same as the previous trial (e.g., these data points relate to D and C in Figure \ref{fig:tdAccount}); this is because both of these conditions have an identical RCI-ratio of 1, and hence have the same TD.
+Figure \ref{fig:grangeData} represents a portion of data reported by \cite{Grangeinrevision}---a brief overview of the pertinent method details and analysis are presented in Appendix A---that replicates the main findings from \cite{Horoufchin2011a}; focussing on repetition RTs, increasing RCI from 50ms to 1,000ms has negligible effect on RTs when the RCI was the same as the previous trial (e.g., these data points relate to D and C in Figure \ref{fig:tdAccount}); this is because both of these conditions have an identical RCI-ratio of 1, and hence have the same TD.
 RCI has a considerable effect on repetition RT when the RCI has changed from the previous trial: RT is very fast when the RCI is 50ms, as this condition has a very high RCI-ratio, hence high TD (Figure \ref{fig:tdAccount} A); RT is very slow when the RCI is 1,000ms, as this condition has a very low RCI-ratio, hence low TD (Figure \ref{fig:tdAccount} B).
@@
 Therefore, trials with high RCI-ratio (e.g., 20) will have high TD, and therefore high $p$(retrieved), meaning many trials will be sampled from the fast RT process; trials with low RCI-ratio (e.g., 0.05) will have low TD, and hence low $p$(retrieved), meaning many trials will be sampled from the slow process.
+See Appendix B for an overview of this model.
 
@@
 
-Importantly, this model assumes that all RTs are being sampled from only one of two processes: a fast and a slow process.
-Therefore, trials with intermediate RCI-ratios (e.g., 1) will have intermediate TDs, and therefore intermediate p(retrieved); this means that intermediate RCI-ratio RTs will be a mixture of RTs from the fast process and RTs from the slow process, with the exact proportion of mixture related to $p$(retrieved).
+Importantly, this model therefore assumes that all RTs are being sampled from one of only two processes: a fast and a slow process.
+Therefore, trials with intermediate RCI-ratios (e.g., 1) will have intermediate TDs, and therefore intermediate $p$(retrieved); this means that intermediate RCI-ratio RTs will be a mixture of RTs from the fast process and RTs from the slow process, with the exact proportion of mixture related to $p$(retrieved).
 
@@
 Then, in a next step I extend the model of \cite{Grange2015} to predict whole RT-distributions, which allows a direct test of the mixture-distribution assumption.
-The article ends with discussion of implications of these findings for the TD account of RCI effects in task switching.
 %%%--------------------------------------------------------------------------------------------
@@
 The task repetition data from Figure \ref{fig:grangeData} was assessed for the presence of a fixed-point property.
-In this test, the RCI-ratio of 20 can be considered the ``fast'' condition, and the RCI-ratio of 0.05 can be considered the ``slow'' distribution.
+In this test, the RCI-ratio of 20 can be considered the ``fast'' distribution, and the RCI-ratio of 0.05 can be considered the ``slow'' distribution.
 The critical question is whether intermediate RCI-ratios of 1 are a mixture of the fast and the slow distribution.
@@
 Data were trimmed before testing.
-Correct RTs were first trimmed to retain RTs slower than 150 milliseconds, and RTs faster than 2.5 standard deviations above each subjects' mean RT.
+Correct RTs were trimmed to retain RTs slower than 150 milliseconds, and RTs faster than 2.5 standard deviations above each subjects' mean RT.
 The data was then assessed for the presence of a fixed-point by passing it to the \texttt{fp} function provided in the form of \texttt{R} code from \citet{VanMaanen2014}.
@@
 There is considerable overlap in the box-plots suggesting no difference between condition pairs of crossing point (supporting the fixed-point property).
-Together, this visual inspection provides good evidence that the RCI-ratio = 1 RT function is a weighted mixture of the ``slow'' RT distribution (where RCI-ratio = 0.05) and the ``fast'' RT distribution (where RCI-ratio = 20), as predicted by the temporal distinctiveness model \cite{Grange2015}.
+Together, this visual inspection provides good evidence that the RCI-ratio = 1 RT function is a weighted mixture of the ``slow'' RT distribution (where RCI-ratio = 0.05) and the ``fast'' RT distribution (where RCI-ratio = 20), as predicted by the temporal distinctiveness model \citep{Grange2015}.
 
@@
 However, to confirm the statistical \emph{presence} of a common crossing point requires the acceptance of a null hypothesis which cannot be achieved via standard null hypothesis significance testing.
-Therefore, a default Bayesian ANOVA \cite{Rouder2012} was conducted on the same data, which produces a Bayes Factor; the Bayes Factor---denoted $BF_{01}$---assesses the evidence in favour of a model assuming a common crossing point (i.e., a ``null'' model) compared to a model assuming multiple crossing points (i.e., an ``alternative'' model).
+Therefore, a default Bayesian ANOVA \citep{Rouder2012} was conducted on the same data, which produces a Bayes Factor; the Bayes Factor---denoted $BF_{01}$---assesses the evidence in favour of a model assuming a common crossing point (i.e., a ``null'' model) compared to a model assuming multiple crossing points (i.e., an ``alternative'' model).
 The Bayes Factor for this data was $BF_{01}$ = 3.354, suggesting the data are 3.4 times more likely under the model assuming a common crossing point.
@@
 
-In this section, I provide a schematic overview of the assumptions of the model. The mathematical details of the model are in Appendix B.
+In this section, I provide a schematic overview of the assumptions of the model. The mathematical details of the model are in Appendix C.
 
@@
 The LBA model has several parameters.
-The mean rate of evidence accumulation is referred to as the \emph{drift rate}, $v$; it is higher for the correct response than for the error response.
+The mean rate of evidence accumulation is referred to as the \emph{drift rate}, $v$; it is higher for the correct response than for the error response (which is typically set to 1-$v$).
 The drift rate for each accumulator can vary across trials, but is assumed to have a fixed mean rate.
@@
 Specifically, the RCI-ratio was 20 for n--2 to n--1 RCIs of 50ms--1000ms; the ratio was 1 for RCIs of 1000ms--1000ms and 50ms--50ms; and the ratio was 0.05 for RCIs of 50ms--1,000ms.
-
 $p$(retrieved) was ``semi-fixed'' in the sense that it was fixed at $p$(retrieved) = 1 for ratios of 20 (i.e., perfect retrieval) and fixed at $p$(retrieved) = 0 for ratios of 0.05 (i.e., failed retrieval); $p$(retrieved) was free to vary for ratios of 1.
@@
 Separate drift rates were estimated for the ``fast'' and ``slow'' distributions---$v_{Fast}$ and $v_{Slow}$, respectively.
-(Note that drift rates for error response evidence accumulation is given as 1--$v$.) Also, each distribution had its own response threshold---$b_{Fast}$ and $b_{Slow}$.\footnote{Initial fits with just $v$ varying between the fast and slow distributions did not fit the data as well as when $b$ was also allowed to vary between conditions.} All other parameters (i.e., $A$, $s$, and $ter$ took on identical values for all three ratio conditions.
+(Note that drift rates for error response evidence accumulation is given as 1--$v$.) Also, each distribution had its own response threshold---$b_{Fast}$ and $b_{Slow}$.\footnote{Initial fits with just $v$ varying between the fast and slow distributions did not fit the data as well as when $b$ was also allowed to vary between conditions.} All other parameters (i.e., $A$, $s$, and $ter$) took on identical values for all three ratio conditions.
 
@@
 
-The model was fitted to the data via a version of Quantile Maximum Probability Estimation (QMPE; REF), where the model is fit to RT quantiles rather than individual RTs as per maximum likelihood (see Appendix B for details).
+The model was fitted to the data via a version of Quantile Maximum Probability Estimation \citep[QMPE][]{Heathcote2002}, where the model is fit to RT quantiles rather than individual RTs as per maximum likelihood (see Appendix C for details).
 This method was used due to the relatively low number of trials per subject, and the rather low error rate.
 The fits of the model to the behavioural data are shown in Figure \ref{fig:modelFit}.
+The best-fitting parameters are shown in Table \ref{tab:bestParameters}.
 
@@
 This Figure presents so-called ``defective'' cumulative distribution functions (CDFs).
-The data are sorted from fastest to slowest, and then quantile cut-off points are calculated for each subject according to a pre-specified set of quantiles $\vec{Q}$ (here $\vec{Q}$ = .1, .3, .5, .7, .9).
+The data are sorted from fastest to slowest, and then quantile cut-off points are calculated for each subject according to a pre-specified set of quantiles $\vec{Q}$ (here $\vec{Q}$ = 0.1, 0.3, 0.5, 0.7, 0.9).
 The Figure plots the average RT for each quantile across subjects against the quantile value.
 The plot is a defective CDF in the sense that it also displays information about errors.
-Specifically, RT is plotted against $\vec{q}$ $\times$ mean accuracy rather than just $\vec{q}$.
-Error RT---shown in the Figure as open circles)---is error RT plotted against $\vec{q}$ $\times$ (1 - mean accuracy).
+Specifically, RT is plotted against $\vec{Q}$ $\times$ mean accuracy rather than just $\vec{Q}$.
+Error RT---shown in the Figure as open circles)---is error RT plotted against $\vec{Q}$ $\times$ (1 - mean accuracy).
 
@@
 The fit to the error RT distributions is not as good as for the correct RT distributions.
-However, accuracy was generally very high in this experiment (indeed, participants were excluded for not achieving greater than 80\% accuracy).
+However, accuracy was generally very high in this experiment (indeed, participants were excluded for not achieving greater than 80\% accuracy, and average accuracy was much higher).
 So, there were often few error RTs per quantile bin during the model fit, making accurate estimation difficult.
@@
 The fit of the model to the data allowed estimation of a number of important parameters, which might shed some light on explaining performance in RCI-ratio experiments.
-Importantly, the drift rate was estimated to be higher in the RCI-ratio 20 condition (i.e., $v_{Fast}$) than in the RCI-ratio 0.05 condition ($v_{Slow}$.
+Importantly, the drift rate was estimated to be higher in the RCI-ratio 20 condition (i.e., $v_{Fast}$) than in the RCI-ratio 0.05 condition ($v_{Slow}$).
 This suggests that successful retrieval of the target episodic trace leads to faster RTs due to a speed-up in evidence accumulation for a response.
-In addition, the response boundary parameter $b$ was reduced when retrieval failed (i.e., $v_{Slow}$.
-This raises the interesting possibility that when the cognitive system fails to retrieve the targeted episodic trace, it enters a more cautious mode of responding by raising $b$; this might be in some way to compensate for the reduced efficiency of evidence accumulation when retrieval fails ($v_{Slow}$).
+In addition, the response boundary parameter $b$ was reduced when retrieval failed (i.e., $v_{Slow}$).
+This raises the interesting possibility that when the cognitive system fails to retrieve the targeted episodic trace, it enters a more cautious mode of responding by raising response threshold $b$; this might be in some way to compensate for the reduced efficiency of evidence accumulation when retrieval fails ($v_{Slow}$).
 
@@
 Typically, RCI-ratio does not appear to affect switch RT \citep{Horoufchin2011, Horoufchin2011a} which is why the present focus has been on repetition RTs only.
-The model presented here can easily be extended to account for switch RT performance by adding new LBA parameters for switch trials (e.g., $v_{Switch}$, $A_{Switch}$, $b_{Switch}$, and possibly $s_{Switch}$ and  $ter_{Switch}$.
+The model presented here can easily be extended to account for switch RT performance by adding new LBA parameters for switch trials (e.g., $v_{Switch}$, $A_{Switch}$, $b_{Switch}$, and possibly $s_{Switch}$ and  $ter_{Switch}$).
 As RCI-ratio does not typically affect switch trials, it can be assumed that retrieval always fails on switch trials, so $p(retrieved)$ can be set to zero for all RCI-ratio conditions.
@@
 \section{Conclusion}
-In sum, this paper has provided support for the TD account of RCI effects in task switching.
+The present paper sought to assess the evidence in favour of a key prediction of the TD hypothesis of RCI effects in task switching, namely that RTs are a mixture of only one of two processes.
+In sum, this paper has provided good support for the TD prediction, which provides more support for these theoretical accounts \citep{Grange2015, Horoufchin2011, Horoufchin2011a}.
 This presents an important challenge to models of cognitive control during task switching which assume control systems work to prevent relevant task-sets decaying.
@@
 Two arrow cues either pointed up and down (presented above and below the grid, respectively) or left and right (presented to the left and to the right of the grid, respectively).
-100ms later, a stimulus appeared in one of the grid cells.
+100ms later, a stimulus appeared in one of the grid's cells.
 The stimulus could be an A or a 4, presented in either red or blue font.
@@
 \section{Overview of Grange \& Cross (2015) Model}
-The \cite{Grange2015} model used the full mathematics of the SIMPLE \cite{Brown2007} model to account for TD effects on task repetition trials.
+The \cite{Grange2015} model used the full mathematics of the SIMPLE \citep{Brown2007} model to account for TD effects on task repetition trials.
 Distinctiveness is proportional to the \emph{similarity} between a target trace and its neighbours in episodic memory.
@@
 This section describes the details of the mixture-distribution model.
-The model extends the mathematics of the linear ballistic accumulator \cite{Brown2008} for a unitary process (i.e., not a mixture model), which allows calculation of the defective probability density function of one response accumulator reaching retrieval threshold before the accumulator for the second response does.
+The model extends the mathematics of the linear ballistic accumulator \citep{Brown2008} for a unitary process (i.e., not a mixture model), which allows calculation of the defective probability density function of one response accumulator reaching retrieval threshold before the accumulator for the second response does.
 I first describe the mathematics of the LBA for a unitary process before describing how this can be extended to a mixture model.
@@
 The number of RTs in each bin (i.e., in the range 0--$\vec{Q}$--1) were stored in the vector $\vec{N}$ with length $n$.
-Then, the defective cumulative distribution function $F$ at time $t$ = $t-ter$, $F(t)$\footnote{Obtained via numerical integration of Equation \ref{eq:tdLikelihood} at time $t$.}, given model parameters $\vec{\theta}$ was calculated, and multiplied by the number of trials within that bin to obtain the likeilihood $L$
+Then, the defective cumulative distribution function $F$ at time $t$ = $t-ter$, $F(t)$\footnote{Obtained via numerical integration of Equation \ref{eq:tdLikelihood} at time $t$.}, given model parameters $\vec{\theta}$ was calculated, and multiplied by the number of trials within that bin to obtain the QMPE estimate
 
@@
 \begin{aligned}
-L_{M}\left(\vec{\theta} | \vec{Q}, \vec{N}\right) & \propto ln\left[F\left(Q_{1}:\vec{\theta}\right) - F\left(0:\vec{\theta}\right)\right]N_{1} \\ 
+QMPE\left(\vec{\theta} | \vec{Q}, \vec{N}\right) & \propto ln\left[F\left(Q_{1}:\vec{\theta}\right) - F\left(0:\vec{\theta}\right)\right]N_{1} \\ 
 & \qquad \times ln\left[F\left(Q_{i}:\vec{\theta}\right) - F\left(Q_{i - 1}:\vec{\theta}\right)\right]N_{i} \\
@@
 This was performed for each RCI-ratio condition for correct and error responses, and the likelihoods for each were summed.
-The fit routine aimed to find the best-fitting parameters that minimised the negative summed likelihood; the Nelder-Mead method using R's \texttt{optim} was used to fit the model.
+The fit routine aimed to find the best-fitting parameters that minimised the negative summed likelihood; the Nelder-Mead method using R's \texttt{optim} function was used to fit the model.
 Starting values for the parameter search utilised the starting heuristics recommended by  \cite{Donkin2011}.

### 2015-11-05 2015/Temporal Distinctiveness & Mixture Distributions/Manuscript Files/main.tex
final (ready for submission)

@@
 When the RCI-ratio is low, so too is TD, which lowers the probability of successful retrieval.
-When retrieval fails, the task must be performed via a slower, algorithmic route, leading to a slower RT \citep[see][for a similar proposal]{Logan2001}.
+When retrieval fails, the task must be performed via a slower, algorithmic route, leading to a slower RT \citep[see][for a similar proposal]{Logan2002}.
 Intermediate RCI-ratios lead to intermediate levels of TD; therefore, a proportion of these trials will have successful retrieval, and some trials will have failed retrieval.
@@
 
-In the model, mean RT for a given trial is predicted by
+In the model, mean RT for a given RCI-ratio is predicted by
 
@@
 The previous section provided statistical support for the presence of a mixture-distribution for intermediate RCI ratios (i.e., intermediate levels of temporal distinctiveness).
-This is in agreement both with the verbal theory regarding TD effects \cite{Horoufchin2011a} and its formal implementation \cite{Grange2015}, which explains performance across RCI-ratios.
+This is in agreement both with the verbal theory regarding TD effects \citep{Horoufchin2011a} and its formal implementation \citep{Grange2015}, which explains performance across RCI-ratios.
 In this section I develop a mathematical process model to predict RT distributions of RCI-ratio data.

### 2015-11-22 2015/Episodic Retrieval & Inhibition/Manuscript Files/main.tex
init for BI & Episodic Retrieval paper

%%%--------------------------------------------------------------------------------------------
\documentclass[a4paper, jou, natbib]{apa6}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes} 
\usepackage{etoolbox}

% \newtoggle{jou}
% \toggletrue{jou}
% \togglefalse{jou}

% \usepackage{lineno}

\title{The Effect of Episodic Retrieval on Inhibition in Task Switching}
\shorttitle{Episodic Retrieval \& Inhibition}
\author{James A. Grange, Agnieszka Kowalczyk, and Rory O'Loughlin}
\affiliation{School of Psychology, Keele University, UK}

\note{{\bf Word Count:} x,xxx (Main body, not including abstract or references.)}
% \note{{\bf Under Review---Please, no direct quotes.}}

% command to insert editing comments or track changes
\newcommand{\jg}[1]{\textcolor{blue}{$^{\textrm{}}${#1}}}

%command for R symbol
\newcommand{\R}{R}

\authornote{Please address correspondence to James A. Grange, School of Psychology, Dorothy Hodgkin Building, Keele University, Keele, UK, ST5 5BG. Email: grange.jim@gmail.com. All raw data and analysis code are available to download at http://bit.ly/1l22EUV.}

\leftheader{Grange}

\abstract{.}

\keywords{Task switching; inhibition, episodic retrieval, cognitive control}

\begin{document}
\maketitle

%----------------------
\section{Introduction}

%----------------------
\section{Method}

\subsection{Participants}
All participants were recruited via the participant panel run by the School of Psychology at Keele University. All participants were first year undergraduates participating in exchange for partial course credit. Our final sample comprised 76 participants. Three additional participants were removed before analysis due to failure to maintain accuracy levels above 90\%.

Our sample size was determined via optional stopping. We used Sequential Bayes Factors \citep{Schoenbrodtinpress} to determine our stopping rule for participant recruitment. We were interested in establishing the presence or absence of an interaction between task sequence (ABA vs. CBA) and response repetition (repetition vs. switch). For the purposes of our stopping rule, this can be expressed as a default within-subjects Bayesian t-test \citep{Rouder2009} comparing n--2 repetition costs for response repetitions and response switches. The Bayes Factor (denoted $BF_{10}$) quantifies the relative evidence provided by the data in favour of an alternative hypothesis (i.e., n--2 repetition costs are different) over a null hypothesis (i.e., n--2 repetition costs are equivalent). We conducted a Bayesian t-test on the data collected until the criteria for our a priori stopping rule were met. Specifically, our stopping rule required at least 20 participants; we continued data collection until $BF_{10}$ > 6 (constituting support for the alternative hypothesis) or $BF_{10}$ < 1/6 (constituting support for the null). \cite{Schoenbrodtinpress} demonstrated that a stopping rule of $BF_{10}$ > 6 (or $BF_{10}$ < 1/6) provided the best balance between type 1 and type 2 error, and was their recommended value for studies utilising Sequential Bayes Factors.

\subsection{Stimuli \& Apparatus}

\subsection{Procedure}

\subsection{Design}

%----------------------
\section{Results}

\subsection{Data trimming}
Participants who failed to maintain session-wise accuracy above 90\% were immediately discarded from analysis. For response time analysis, the first two trials from each block were removed, as were error trials and the two trials following an error. Response times were trimmed by removing all RTs faster than 150ms, as well as any RTs slower than 2.5 standard deviations above the mean for each participant for each cell of the experimental design.

\subsection{Standard Analysis}
Mean RTs and error rates can be seen in Table \ref{tab:behaviouralData}.

\begin{table*}[htbp]
\centering
\caption{Response times (RT) in milliseconds (ms) and accuracy (in percent) for ABA and CBA task sequences for response repetitions and response switches.}
\label{my-label}
\begin{tabular}{lccccc}
\hline
                    & \multicolumn{5}{c}{Task Sequence}                       \\ \cline{2-6} 
                    & \multicolumn{2}{c}{ABA}   &  & \multicolumn{2}{c}{CBA}  \\ \cline{2-3} \cline{5-6} 
                    & RT (ms)   & Accuracy (\%) &  & RT (ms)  & Accuracy (\%) \\ \hline
Response Repetition & 1000 (28) & 96.20 (0.39)  &  & 952 (28) & 96.36 (0.39) \\
Response Switch     & 1050 (29) & 95.02 (0.35)  &  & 964 (28) & 95.81 (0.34) \\ \hline
\end{tabular}
\label{tab:behaviouralData}
\end{table*}

Response times were analysed via a two factor repeated measures analysis of variance (ANOVA) with the factors as described in \emph{Design}. There was a significant main effect of \emph{Sequence}, with slower RTs to ABA sequences (1,025ms) than to CBA sequences (958ms), $F$(1, 75) = 94.14, $p$<.001, $\eta_g^2$ = .018.  There was also a significant main effect of \emph{Response Sequence}, with faster RTs to response repetitions (976ms) than to response switches (1,007ms), $F$(1, 75) = 18.21, $p$<.001, $\eta_g^2$ = .004.  Critically, there was a significant interaction of both factors, $F$(1, 75) = 9.60, $p$<.01, $\eta_g^2$ = .001. The n--2 repetition cost was 48ms for response repetitions [t(75) = 4.2, $p$<.001] and 86ms for response switches [t(75) = 13.0, $p$<.001].

\subsection{Sequential Bayes Factors}
The progression of the Sequential Bayes Factor is shown in Figure \ref{fig:bayesFactor}. We stopped data collection after 76 participants, as at this point the criteria for our stopping rule had been reached.

\begin{figure}
\begin{center}
\includegraphics[width = 0.5\textwidth]{Images/bayesFactor.pdf}
\caption{Progression of the Sequential Bayes Factor [expressed as log($BF_{10}$)] as sample size increased. The criteria for a priori stopping rules are shown as dotted horizontal lines.}
\label{fig:bayesFactor}
\end{center}
\end{figure}

The final Bayes Factor for the difference of n--2 repetition costs for response repetitions and response switches was $BF_{10}$ = 9.974, which suggests that the alternative hypothesis is about 10 times more likely given than the data, which provides strong support that n--2 repetition costs are influenced by response repetitions.

%----------------------
\section{Discussion}

\subsection{Robustness of Recruitment Order on the Sequential Bayes Factor}
The progression of the Bayes Factor as sample size increased (Figure \ref{fig:bayesFactor}) appeared to provide slight evidence in favour of the null between sample sizes of 30 and 40, although the criterion for stopping was not reached. One might wonder, therefore, whether had a few more participants been recruited to the experiment showing a null interaction would we have stopped data collection and found evidence in favour of the null?

We wanted to assess how robust our stopping rule was to this apparent early evidence in favour of the null. Specifically, we were interested in whether our stopping rule in favour of the null would have been met had the participants been recruited in a different order. To assess this, we generated 50 random recruitment orders from our data set, and plotted the Sequential Bayes Factors for each recruitment order. If our findings are robust against recruitment order, the stopping rule in favour of the null should be rarely (if ever) met.  The results of this simulation are shown in Figure \ref{fig:recruitmentOrder}; each line represents the Sequential Bayes Factor for a random recruitment order. As can be seen, the stopping criterion in favour of the null is never met, suggesting our results are indeed robust to recruitment order.

\begin{figure}
\begin{center}
\includegraphics[width = 0.5 \textwidth]{Images/recruitmentOrder.pdf}
\caption{Simulated progression of the Sequential Bayes Factors for a random set of 50 different recruitment orders for the current data set. See text for details.}
\label{fig:recruitmentOrder}
\end{center}
\end{figure}

%%%--------------------------------------------------------------------------------------------

%%%--------------------------------------------------------------------------------------------
\bibliography{References.bib}

\end{document}

### 2015-11-22 2015/Episodic Retrieval & Inhibition/Data & Analysis Code/analysis.R

@@ -1,0 +1,243 @@
+### Analysis script for Mayr replication
+
+#------------------------------------------------------------------------------
+### General set-up
+
+# clear workspace
+rm(list = ls())
+
+# set working directory
+setwd("~/Git/paperData/2015/Episodic Retrieval & Inhibition/Data & Analysis Code")
+
+# load necessary functions file & load necessary packages
+source("functions.R")
+library(dplyr)
+library(ggplot2)
+library(ez)
+library(BayesFactor)
+library(BEST)
+
+# load the data file
+fullData <- read.csv("allData.csv", header = TRUE)
+#------------------------------------------------------------------------------
+
+
+
+#------------------------------------------------------------------------------
+### Error Data Trimming 
+
+# Remove null trials (1st and 2nd trial of each block)
+
+# which trials were null?
+nullTrials <- c(1, 2, 121, 122, 241, 242, 361, 362)
+
+# remove these trials
+data <- fullData[! fullData$trial %in% nullTrials, ]
+
+
+# add column to code for removing two trials following an error, initialised 
+# to zero
+data <- mutate(data, accTrim = 0)
+
+# populate this column
+for(i in 3:nrow(data)){
+  data$accTrim[i] <- data$accuracy[i - 2] * data$accuracy[i - 1]
+}
+#------------------------------------------------------------------------------
+
+
+#------------------------------------------------------------------------------
+### Error Analysis
+
+# First, we need to see the OVERALL accuracy per participant, as we will want
+# to remove people who do not meet a certain criteria
+accuracy <- data %>%
+  group_by(subject) %>%
+  summarise(meanAccuracy = (sum(accuracy) / length(accuracy) * 100))
+
+# which subjects fall below our criterion of 90% accuracy?
+errorRemove <- accuracy[accuracy$meanAccuracy <= 90, ]$subject
+
+# remove these subjects from the data file
+data <- data[! data$subject %in% errorRemove, ]
+
+# remove the 2 trials following an error
+data <- subset(data, data$accTrim == 1)
+
+# now produce a data frame with accuracy analysis per condition
+accuracy <- data %>%
+  group_by(subject, stimRep, sequence) %>%
[…]

### 2015-11-22 2015/Episodic Retrieval & Inhibition/Data & Analysis Code/functions.R

@@ -1,0 +1,196 @@
+### Functions script
+
+#------------------------------------------------------------------------------
+### Trim RTs using SD criterion
+getRTs <- function(data, minRT, sd){
+  
+  
+  # get rid of fast RTs
+  data <- subset(data, data$rt > minRT)
+  
+  # get vector of unique subject numbers
+  subjects <- unique(data$subject)
+  
+  # initialise matrix to store data in 
+  rtData <- matrix(0, nrow = length(subjects), ncol = 5)
+  colnames(rtData) <- c("subject", 
+                        "abaRep", "abaSw", 
+                        "cbaRep", "cbaSw")
+  
+  # to keep track of how many subjects have been processed
+  i = 1
+  
+  # loop over each subject
+  for(sub in subjects){
+    
+    # add subject number to data matrix
+    rtData[i, 1] <- sub
+    
+    # get this subject's data
+    subData <- subset(data, data$subject == sub)
+    
+    # get their ABA data first
+    abaData <- subset(subData, subData$sequence == "ABA")
+    
+      # get their stimRepetition == yes data
+      repData <- subset(abaData, abaData$stimRep == "yes")
+    
+      # get the trimmed mean RT
+      rts <- as.numeric(repData$rt)
+      rtData[i, 2] <- trimRTs(rts, sd)
+    
+      # get their stimRepetition == no data
+      swData <- subset(abaData, abaData$stimRep == "no")
+      
+      # get the trimmed mean RT
+      rts <- as.numeric(swData$rt)
+      rtData[i, 3] <- trimRTs(rts, sd)
+    
+    
+    # now get their CBA data 
+    cbaData <- subset(subData, subData$sequence == "CBA")
+    
+      # get their stimRepetition == yes data
+      repData <- subset(cbaData, cbaData$stimRep == "yes")
+      
+      # get the trimmed mean RT
+      rts <- as.numeric(repData$rt)
+      rtData[i, 4] <- trimRTs(rts, sd)
+      
+      # get their stimRepetition == no data
+      swData <- subset(cbaData, cbaData$stimRep == "no")
+      
+      # get the trimmed mean RT
+      rts <- as.numeric(swData$rt)
+      rtData[i, 5] <- trimRTs(rts, sd)
+    
+    # update looping count
+    i <- i + 1
+        
+  } # end of subject loop
+  
+  # change to data frame
+  rtData <- as.data.frame(rtData)
+  
+  return(rtData)
+}
+
[…]

### 2015-11-22 2015/Episodic Retrieval & Inhibition/Manuscript Files/main.tex
added analysis

@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[width = 0.5 \textwidth]{Images/mayrExperiment.pdf}
+\caption{Schematic overview of Mayr's (2002) experimental procedure. See text for details.}
+\label{fig:mayrExperiment}
+\end{center}
+\end{figure}
+
+\section{Changes from Mayr's (2002) Experiment}
+List the main changes we made in this experiment compared to that of \cite{Mayr2002}.
+
 %----------------------
@@
 
-\subsection{Stimuli \& Apparatus}
+\subsection{Apparatus \& Stimuli}
+Stimuli were presented on an xin.
+monitor connected to a PC running E-Prime v.
+2.0 software.
+The stimulus display consisted of an 8cm by 8cm square frame.
+A black circle (diameter = 1cm) served as the trial stimulus.
+Possible cues were the words ``horizontal'', ``vertical'', or ``diagonal'', and were presented in black font (enter font details here) directly above the stimulus frame.
+Responses were collected via a 1-ms precise USB keyboard.
 
 \subsection{Procedure}
+On each trial a cue was presented above the frame for xxms.
+After this time, the circle stimulus appeared in one of the four corners of the frame.
+The cue remained on the screen during stimulus presentation.
+The task required participants to mentally make a spatial transformation of the stimulus' location according to the rule dictated by the task cue, and to make a spatially-congruent response to this translated location.
+For example, if the stimulus was in the top-right corner, the participant would need to make a top-left response if the task was ``horizontal'', a bottom-right response if the task was ``vertical'', and a bottom-left response if the task was ``diagonal''.
+Responses were made on the numerical part of the keyboard, using the ``4'', ``5'', ``1'', and ``2'' keys for top-left, top-right, bottom-left, and bottom-right responses respectively.
+Participants were asked to respond as quickly and as accurately as possible.
+Once a response was registered, the frame was cleared for a response--cue interval of xxms, after which time a new cue appeared for the next trial.
+The cue for the next trial was chosen randomly with the constraint that task repetitions could not occur (cf., Mayr, 2002); the stimulus location was chosen randomly with no constraints on each trial.
+If participants made an error, the word ``Error!'' appeared in red for xxms above the stimulus frame (in the cue's position).
+
+Participants were presented with xx trials as practice (which could be repeated upon request). The main experiment presented x blocks of x trials.
 
 \subsection{Design}
+The experiment manipulated two factors in a fully-related design: \emph{Task Sequence} (n--2 task repetition [ABA] vs.
+n--2 task switch [CBA]) and \emph{Response Repetition} (n--2 response repetition vs.
+n-- response switch).
+The dependent variables were response time (RT) in milliseconds (ms) and percent accuracy (\%).
 

### 2015-11-24 2015/Episodic Retrieval & Inhibition/Manuscript Files/main.tex
updated ms file slightly

@@
 %%%--------------------------------------------------------------------------------------------
-\documentclass[a4paper, jou, natbib]{apa6}
+\documentclass[a4paper, doc, natbib]{apa6}
 \usepackage[english]{babel}
@@
 \begin{center}
-\includegraphics[width = 0.5 \textwidth]{Images/mayrExperiment.pdf}
+\includegraphics[width = \textwidth]{Images/mayrExperiment.pdf}
 \caption{Schematic overview of Mayr's (2002) experimental procedure. See text for details.}
@@
 There was a significant main effect of \emph{Sequence}, with slower RTs to ABA sequences (1,025ms) than to CBA sequences (958ms), $F$(1, 75) = 94.14, $p$<.001, $\eta_g^2$ = .018.
+The Bayes factor for this main effect was $BF_{10}$ = 1e+12, which provides substantial support for the presence of n--2 repetition costs.
 There was also a significant main effect of \emph{Response Sequence}, with faster RTs to response repetitions (976ms) than to response switches (1,007ms), $F$(1, 75) = 18.21, $p$<.001, $\eta_g^2$ = .004.
+The Bayes factor for this main effect was $BF_{10}$ = 338.77, which again provides substantial support for the alternative hypothesis.
 Critically, there was a significant interaction of both factors, $F$(1, 75) = 9.60, $p$<.01, $\eta_g^2$ = .001.
 The n--2 repetition cost was 48ms for response repetitions [t(75) = 4.2, $p$<.001] and 86ms for response switches [t(75) = 13.0, $p$<.001].
+We discuss the Bayes factor for this interaction below.
 
@@
 \begin{center}
-\includegraphics[width = 0.5\textwidth]{Images/bayesFactor.pdf}
+\includegraphics[width = \textwidth]{Images/bayesFactor.pdf}
 \caption{Progression of the Sequential Bayes Factor [expressed as log($BF_{10}$)] as sample size increased. The criteria for a priori stopping rules are shown as dotted horizontal lines.}
@@
 \begin{center}
-\includegraphics[width = 0.5 \textwidth]{Images/recruitmentOrder.pdf}
+\includegraphics[width = \textwidth]{Images/recruitmentOrder.pdf}
 \caption{Simulated progression of the Sequential Bayes Factors for a random set of 50 different recruitment orders for the current data set. See text for details.}

### 2015-11-25 2015/Episodic Retrieval & Inhibition/Manuscript Files/main.tex
updated manuscript file

@@
 
-\note{{\bf Word Count:} x,xxx (Main body, not including abstract or references.)}
+\note{{\bf Word Count:} 2,890 (Main body, not including abstract or references.)}
 % \note{{\bf Under Review---Please, no direct quotes.}}
@@
 
-\abstract{.}
+\abstract{Inhibition in task switching is inferred from n--2 task repetition costs: the observation that ABA task switching sequences are responded to slower than CBA sequences.
+This is thought to reflect the persisting inhibition of task A, which slows re-activation attempts.
+\cite{Mayr2002} reported an experiment testing a critical non-inhibitory account of this effect, namely episodic retrieval: If the trial parameters for task A match across an ABA sequence, responses should be facilitated due to priming from episodic retrieval; a cost would occur if trial parameters mismatch.
+In a rule-switching paradigm, Mayr reported no significant difference in n--2 repetition cost when the trial parameters repeated or switched across an ABA sequence, in contrast to the episodic retrieval account.
+Here we provide a replication of the critical aspects of Mayr's design.
+Using Bayesian analysis to quantify evidence for or against a null hypothesis, we find evidence for reduced n--2 repetition costs when trial parameters repeat compared to when they switch.
+In contrast to Mayr's conclusion, we suggest that episodic retrieval can influence the measure of inhibition in task switching, although it cannot explain it entirely.}
 
@@
 
+Stimuli in the human environment typically afford more than one action.
+Sat at a computer, for example, there are many tasks that could be performed, such as writing a manuscript, checking the weather, or playing a game of online chess.
+In order to act in a goal-directed manner, humans must be able to \emph{select} the relevant task (writing a paper) in the face of competing tasks (playing chess), and maintain this task in an active state so that it can dominate behaviour.
+However, such \emph{stable} representations must also be \emph{flexible}, so that they can be removed when the goals change (such as when the phone rings).
+This tension between the need for stability and flexibility of task representations has been called the \emph{stability--flexibility dilemma} \citep{Goschke2000}.
+
+How the cognitive system addresses the stability--flexibility dilemma has been studied using the task switching paradigm \citep{Grange2014a,Kiesel2010,Vandierendonck2010}, wherein participants have to make speeded responses to simple cognitive tasks.
+For example, participants might be presented with number stimuli, and be asked to switch between judging whether the stimulus is odd/even or lower/higher than five.
+One cognitive process thought to be essential for task switching performance is the active inhibition of competing tasks.
+Evidence for inhibition comes from the so-called backward inhibition paradigm \citep{Koch2010, Mayr2000}, where participants are required to switch between three tasks (A, B, and C).
+It is a consistent finding that ABA task switching sequences are performed slower and with less accuracy than CBA sequences.
+This \emph{n--2 repetition cost} is thought to reflect the persisting inhibition of task A in an ABA sequence, which hinders its re-activation in the last trial of the triplet.
+
+The n--2 repetition costs is important as it appears to be robust against non-inhibitory explanations which have successfully accounted for other ``inhibitory'' phenomena \citep{Mayr2007}.
+One potential explanation---episodic retrieval \citep{Neill1997}---was explored by \cite{Mayr2002}.
+This theory suggests (adapted to a task switching context) that when a task has been performed an episodic trace of trial parameters (such as the cue, stimulus characteristics, and the response made) is stored in memory.
+When this task is cued again, retrieval of the most recent episodic trace occurs.
+If the parameters of the presented trial differ from that of the retrieved episode (e.g., a different response is required), a mismatch cost occurs relative to if the retrieved episode matches parameters of the current trial (which will prime performance).
+Thus, according to this account, n--2 repetition costs reflect a mismatch cost, as trial parameters typically differ between both instances of task A in an ABA sequence.
+
+\cite{Mayr2002} assessed this alternative explanation by developing a paradigm where the match between trial parameters across an ABA sequence could be manipulated (see Figure \ref{fig:mayrExperiment}).
+Participants were required to apply a spatial transformation of a target's location according to one of three stimulus--response rules (vertical, horizontal, or diagonal transformations).
+For example, if the target is in the bottom-left of the display and the current rule is ``vertical'', the correct response would be an upper-left response (as this reflects a vertical transformation of a bottom-left target).
+The parameters that might be stored in an episodic trace include (at least) the cue used, the target's location, and the response made.
+In this paradigm, trial parameters can either match or mismatch across ABA and CBA sequences.
+For example, if the target is in the same location for task A across an ABA sequence, the same response will be required (i.e., an n--2 response repetition).
+In this case, the episodic retrieval account would predict facilitated performance relative to an n--2 response switch as in the former case the current trial parameters match perfectly the retrieved episodic trace.
+Thus, the episodic account would predict reduced (or zero) n--2 task repetition costs for n--2 response repetitions compared to n--2 response switches (where there is a mismatch between trial parameters and the retrieved episodic trace).
+
 \begin{figure}
@@
 \includegraphics[width = \textwidth]{Images/mayrExperiment.pdf}
-\caption{Schematic overview of Mayr's (2002) experimental procedure. See text for details.}
+\caption{Schematic overview of Mayr's (2002) experimental procedure.
+The arrows are not displayed to participants, but reflect the spatial transformation required according to the given rule.
+See text for details.}
 \label{fig:mayrExperiment}
@@
 
-\section{Changes from Mayr's (2002) Experiment}
-List the main changes we made in this experiment compared to that of \cite{Mayr2002}.
+\cite{Mayr2002} found no statistically significant interaction between n--2 task repetitions and n--2 response repetition [$F$(1, 38) = 1.3, $p$ = .26]; that is, there was no significant difference between n--2 task repetition costs for n--2 response repetitions and n--2 response switches.
+Mayr suggested this provided evidence against the episodic retrieval account of n--2 task repetition costs, and instead favours the inhibitory account.
+
+\section{The Current Study}
+The purpose of the current study was to re-examine the evidence for the effect of episodic retrieval on n--2 task repetition costs.
+The conclusion of \cite{Mayr2002} rests on the acceptance of a null hypothesis (i.e., no difference of n--2 task repetition costs), which cannot be achieved via standard null hypothesis significance testing \citep[NHST;][]{Gallistel2009, Wagenmakers2007}; however, evidence in favour of a null hypothesis (given some data) can be obtained using Bayes Factors \citep[e.g.,][]{Rouder2009}.
+The Bayes Factor (denoted $BF_{10}$) quantifies the relative evidence provided by the data in favour of an alternative hypothesis (i.e., n--2 task repetition costs are different for response repetitions and response switches) over a null hypothesis (i.e., n--2 repetition costs are equivalent).
+
+The Bayes factor for the critical statistical test from Mayr's (2002) study ($BF_{10}$ = 0.315) suggests that the null hypothesis is about 3 times more likely than the alternative, given the data, which provides anecdotal--moderate support for the null.
+As this Bayesian analysis does not provide decisive evidence for the null, and given the importance of assessing to what extent (if any) episodic retrieval can influence n--2 task repetition costs in task switching, we were interested in performing a replication of Mayr's study to gather more evidence.
+
+The current study replicated critical aspects of Mayr's (2002) design relevant to n--2 task repetitions.
+As Mayr's study was also interested in exploring to what extent the paradigm generated typical task switching effects (such as switch costs, effects of preparation, and effects of the delay between tasks), we made some changes to the original design of Mayr.
+Specifically, immediate task repetitions were not allowed; it has been shown that including immediate task repetitions reduces the n--2 task repetition cost \citep{Philipp2006}, so we removed this possibility.
+We also did not manipulate preparation via the cue--stimulus interval, as Mayr reported no effect of this variable on n--2 task repetition costs.
+Mayr did find that n--2 repetition costs were larger with shorter response--cue intervals (RCI; the time between the response to one trial and the onset of the cue for the next trial), a typical finding for n--2 task repetition costs \citep{Gade2005, Grange2009, Mayr2000}.
+Therefore, in order to obtain large n--2 task repetition costs we only used a short RCI.
 
@@
 switch).
-For the purposes of our stopping rule, this can be expressed as a default within-subjects Bayesian t-test \citep{Rouder2009} comparing n--2 repetition costs for response repetitions and response switches.
-The Bayes Factor (denoted $BF_{10}$) quantifies the relative evidence provided by the data in favour of an alternative hypothesis (i.e., n--2 repetition costs are different) over a null hypothesis (i.e., n--2 repetition costs are equivalent).
-We conducted a Bayesian t-test on the data collected until the criteria for our a priori stopping rule were met.
+For the purposes of our stopping rule, this can be expressed as a default within-subjects Bayesian \emph{t}-test \citep{Rouder2009} comparing n--2 repetition costs for response repetitions and response switches.
+We conducted a Bayesian \emph{t}-test on the data collected until the criterion for our a priori stopping rule was met.
 Specifically, our stopping rule required at least 20 participants; we continued data collection until $BF_{10}$ > 6 (constituting support for the alternative hypothesis) or $BF_{10}$ < 1/6 (constituting support for the null).
@@
 \subsection{Apparatus \& Stimuli}
-Stimuli were presented on an xin.
+Stimuli were presented on a 17in.
 monitor connected to a PC running E-Prime v.
@@
 \subsection{Procedure}
-On each trial a cue was presented above the frame for xxms.
+On each trial a cue was presented above the frame for 150ms.
 After this time, the circle stimulus appeared in one of the four corners of the frame.
@@
 Participants were asked to respond as quickly and as accurately as possible.
-Once a response was registered, the frame was cleared for a response--cue interval of xxms, after which time a new cue appeared for the next trial.
+Once a response was registered, the frame was cleared for a response--cue interval of 150ms, after which time a new cue appeared for the next trial.
 The cue for the next trial was chosen randomly with the constraint that task repetitions could not occur (cf., Mayr, 2002); the stimulus location was chosen randomly with no constraints on each trial.
@@
 
-Participants were presented with xx trials as practice (which could be repeated upon request). The main experiment presented x blocks of x trials.
+Participants were presented with 16 trials as practice (which could be repeated upon request). The main experiment presented 4 blocks of 120 trials.
 
@@
 \section{Results}
-
-\subsection{Data trimming}
 Participants who failed to maintain session-wise accuracy above 90\% were immediately discarded from analysis.
@@
 Response times were trimmed by removing all RTs faster than 150ms, as well as any RTs slower than 2.5 standard deviations above the mean for each participant for each cell of the experimental design.
-
-\subsection{Standard Analysis}
 Mean RTs and error rates can be seen in Table \ref{tab:behaviouralData}.
@@
 
+\subsection{Response Times}
 Response times were analysed via a two factor repeated measures analysis of variance (ANOVA) with the factors as described in \emph{Design}.
@@
 The n--2 repetition cost was 48ms for response repetitions [t(75) = 4.2, $p$<.001] and 86ms for response switches [t(75) = 13.0, $p$<.001].
-We discuss the Bayes factor for this interaction below.
 
-\subsection{Sequential Bayes Factors}
-The progression of the Sequential Bayes Factor is shown in Figure \ref{fig:bayesFactor}.
-We stopped data collection after 76 participants, as at this point the criteria for our stopping rule had been reached.
+The progression of the Sequential Bayes Factor for the interaction is shown in Figure \ref{fig:bayesFactor}.
+We stopped data collection after 76 participants, as at this point the criteria for our stopping rule had been reached\footnote{We could have stopped after 75 participants, but the last two participants were tested in successive sessions, so the Bayes factor was not checked until after the final participant.}.
+The final Bayes Factor for the difference of n--2 repetition costs for response repetitions and response switches was $BF_{10}$ = 9.974, which suggests that the alternative hypothesis is about 10 times more likely given than the data, which provides strong support that n--2 repetition costs are influenced by response repetitions.
 
@@
 
-The final Bayes Factor for the difference of n--2 repetition costs for response repetitions and response switches was $BF_{10}$ = 9.974, which suggests that the alternative hypothesis is about 10 times more likely given than the data, which provides strong support that n--2 repetition costs are influenced by response repetitions.
-
-%----------------------
-\section{Discussion}
-
-\subsection{Robustness of Recruitment Order on the Sequential Bayes Factor}
+\subsubsection{Robustness of Recruitment Order on the Sequential Bayes Factor}
 The progression of the Bayes Factor as sample size increased (Figure \ref{fig:bayesFactor}) appeared to provide slight evidence in favour of the null between sample sizes of 30 and 40, although the criterion for stopping was not reached.
 One might wonder, therefore, whether had a few more participants been recruited to the experiment showing a null interaction would we have stopped data collection and found evidence in favour of the null?
+Put another way, did recruitment order bias our results?
 
@@
 
+\subsection{Accuracy}
+Accuracy analysis showed no significant effect of task sequence [$F$(1, 75) = 3.36, $p$=.07, $\eta_g^2$ = .006]; the Bayes factor for this main effect was $BF_{10}$ = 0.618, which provides only anecdotal support for the null.
+The main effect of response repetition was significant [$F$(1, 75) = 12.17, $p$<.001, $\eta_g^2$ = .019], suggestive of better accuracy for response repetitions (96.28\%) than for response switches (95.41\%).
+The Bayes factor was $BF_{10}$ = 29.66, which provides substantial support for the alternative.
+The interaction was not significant [$F$(1, 75) = 1.32, $p$=.25, $\eta_g^2$ = .003]; the Bayes factor was $BF_{10}$ = 0.238, which provides moderate support for the null hypothesis.
+
+%----------------------
+\section{Discussion}
+
+The present study sought to re-examine the evidence for any potential effect of episodic retrieval on n--2 task repetition costs in task switching by replicating key aspects of Mayr's (2002) study.
+In contrast to that study, we found clear evidence of episodic retrieval influencing n--2 task repetition costs in task switching; specifically, n--2 task repetition costs were smaller when the response repeated over an ABA sequence compared to when the response switched.
+This is in line with an episodic retrieval account which produces facilitation to responding when trial parameters match over an ABA sequence (i.e., for n--2 response repetitions).
+This facilitation to performance can reduce to some extent the n--2 task repetition cost, suggesting episodic retrieval can reduce the negative effects of inhibition when trial parameters match.
+
+This finding has important implications for theories of task switching.
+There is growing evidence that episodic retrieval plays a role in explaining several task switching effects.
+For example, \cite{Altmann2011} provided empirical and theoretical evidence that episodic retrieval can explain the response-repetition effect in task switching, the observation that task repetition RTs are facilitated when the required response repeats from trial n--1 to the current trial, yet response repetitions produce a cost for task switches.
+\cite{Horoufchin2011a} \citep[see also][]{Horoufchin2011} also provided evidence that episodic retrieval can explain some task switching effects.
+It is typically found that the switch cost is reduced at longer RCIs \cite[e.g.,][]{Meiran2000a}; the standard explanation for this finding pertains to the decay of task representations in memory reducing task repetition RTs.
+However, \cite{Horoufchin2011a} provided compelling evidence that this pattern of data can be better explained with reference to episodic retrieval account: trialwise variation of the RCI affects the \emph{temporal distinctiveness} of task traces in episodic memory, thus influencing their retrieval probability \citep{Brown2007,Grange2015}.
+The current work extends this evidence of the role of episodic retrieval influencing task switching effects.
+As such, theoretical accounts of cognitive control during task switching will have to take into account the role of episodic retrieval.
+
+For clarification, note that we have not provided evidence that episodic retrieval can explain the n--2 task repetition cost entirely, but rather it reduces the cost.
+Indeed, the n--2 task repetition cost was still statistically significant even when the trial parameters matched across n--2 task repetitions [i.e., n--2 response repetitions; \emph{t}(75) = 4.20, $p$<.001; $BF_{10}$ = 286.50].
+Therefore, our findings do not provide evidence against the inhibitory explanation of these costs.
+Rather, we have shown that these costs can be reduced with successful episodic retrieval.
+As such, researchers should be cognisant of the potential contribution of episodic retrieval mismatches inflating estimates of n--2 task repetition costs when wishing to use this effect for measuring inhibition.
+
+Our results differ to those reported by \cite{Mayr2002}.
+We suggest that our modifications to Mayr's original design improved the sensitivity of the paradigm to be able to detect potential episodic retrieval effects on n--2 task repetitions.
+The modifications were made to enhance the magnitude of n--2 task repetition costs, so that modulation of this cost with response repetitions could be more easily detected.
+Specifically, removing the possibility of n--2 task repetitions likely enhanced the n--2 task repetition cost as it has been shown that allowing immediate repetitions reduces this cost \citep{Philipp2006}.
+We also used the shortest RCI used by Mayr (150ms), as it is a consistent finding that this increases the n--2 repetition cost \cite{Gade2005, Grange2009, Mayr2000, Mayr2002}.
+Any one of these modifications could explain the difference in results between this study and that of Mayr (2002).
+Future research should aim to examine the potential role for episodic retrieval influencing n--2 task repetition costs by providing further replications to this study \citep{OpenScienceCollaboration2015}.
+
 %%%--------------------------------------------------------------------------------------------

### 2015-11-26 2015/Episodic Retrieval & Inhibition/Manuscript Files/main.tex
finalised manuscript; added Bayesian est.

@@
 %%%--------------------------------------------------------------------------------------------
-\documentclass[a4paper, doc, natbib]{apa6}
+\documentclass[a4paper, man, natbib]{apa6}
 \usepackage[english]{babel}
@@
 \shorttitle{Episodic Retrieval \& Inhibition}
-\author{James A. Grange, Agnieszka Kowalczyk, and Rory O'Loughlin}
+\author{James A. Grange, Agnieszka W. Kowalczyk, and Rory O'Loughlin}
 \affiliation{School of Psychology, Keele University, UK}
 
-\note{{\bf Word Count:} 2,890 (Main body, not including abstract or references.)}
+\note{{\bf Word Count:} 3,124 (Main body, not including abstract or references.)}
 % \note{{\bf Under Review---Please, no direct quotes.}}
@@
 Email: grange.jim@gmail.com.
-All raw data and analysis code are available to download at http://bit.ly/1l22EUV.}
+All raw data and analysis code are available to download at http://bit.ly/1OgH9v0.}
 
-\leftheader{Grange}
+\leftheader{Grange, Kowalczyk, \& O'Loughlin}
 
-\abstract{Inhibition in task switching is inferred from n--2 task repetition costs: the observation that ABA task switching sequences are responded to slower than CBA sequences.
+\abstract{Inhibition in task switching is inferred from n--2 task repetition costs: the observation that AB$A$ task switching sequences are responded to slower than CB$A$ sequences.
 This is thought to reflect the persisting inhibition of task A, which slows re-activation attempts.
@@
 %----------------------
-\section{Introduction}
-
 Stimuli in the human environment typically afford more than one action.
 Sat at a computer, for example, there are many tasks that could be performed, such as writing a manuscript, checking the weather, or playing a game of online chess.
-In order to act in a goal-directed manner, humans must be able to \emph{select} the relevant task (writing a paper) in the face of competing tasks (playing chess), and maintain this task in an active state so that it can dominate behaviour.
-However, such \emph{stable} representations must also be \emph{flexible}, so that they can be removed when the goals change (such as when the phone rings).
+In order to act in a goal-directed manner, humans must be able to \emph{select} the relevant task (writing a paper) in the face of competing tasks (playing chess), and maintain this task in an active state so that it can be performed.
+However, such \emph{stable} task representations must also be \emph{flexible}, so that they can be removed when the goals change (such as when the phone rings).
 This tension between the need for stability and flexibility of task representations has been called the \emph{stability--flexibility dilemma} \citep{Goschke2000}.
@@
 For example, participants might be presented with number stimuli, and be asked to switch between judging whether the stimulus is odd/even or lower/higher than five.
-One cognitive process thought to be essential for task switching performance is the active inhibition of competing tasks.
+One cognitive process thought to be essential for task switching performance is the inhibition of competing tasks.
 Evidence for inhibition comes from the so-called backward inhibition paradigm \citep{Koch2010, Mayr2000}, where participants are required to switch between three tasks (A, B, and C).
-It is a consistent finding that ABA task switching sequences are performed slower and with less accuracy than CBA sequences.
+It is a consistent finding that AB$A$ task switching sequences are performed slower and with less accuracy than CB$A$ sequences.
 This \emph{n--2 repetition cost} is thought to reflect the persisting inhibition of task A in an ABA sequence, which hinders its re-activation in the last trial of the triplet.
 
-The n--2 repetition costs is important as it appears to be robust against non-inhibitory explanations which have successfully accounted for other ``inhibitory'' phenomena \citep{Mayr2007}.
-One potential explanation---episodic retrieval \citep{Neill1997}---was explored by \cite{Mayr2002}.
+The n--2 repetition cost is important as it appears to be robust against non-inhibitory explanations \citep{Mayr2007}.
+One potential explanation of the n--2 repetition cost that does not assume inhibition---the episodic retrieval account \citep{Neill1997}---was explored by \cite{Mayr2002}.
 This theory suggests (adapted to a task switching context) that when a task has been performed an episodic trace of trial parameters (such as the cue, stimulus characteristics, and the response made) is stored in memory.
@@
 
-\cite{Mayr2002} found no statistically significant interaction between n--2 task repetitions and n--2 response repetition [$F$(1, 38) = 1.3, $p$ = .26]; that is, there was no significant difference between n--2 task repetition costs for n--2 response repetitions and n--2 response switches.
+\cite{Mayr2002} found no statistically significant interaction between n--2 task repetition and n--2 response repetition [$F$(1, 38) = 1.3, $p$ = .26]; that is, there was no significant difference between n--2 task repetition costs for n--2 response repetitions and n--2 response switches.
 Mayr suggested this provided evidence against the episodic retrieval account of n--2 task repetition costs, and instead favours the inhibitory account.
@@
 \subsection{Participants}
-All participants were recruited via the participant panel run by the School of Psychology at Keele University.
-All participants were first year undergraduates participating in exchange for partial course credit.
+All participants were undergraduates at the School of Psychology at Keele University.
+Participants took part in exchange for partial course credit or a small cash payment (£6).
 Our final sample comprised 76 participants.
@@
 A black circle (diameter = 1cm) served as the trial stimulus.
-Possible cues were the words ``horizontal'', ``vertical'', or ``diagonal'', and were presented in black font (enter font details here) directly above the stimulus frame.
+Possible cues were the words ``horizontal'', ``vertical'', or ``diagonal'', and were presented in size 22 black Verdanna font directly above the stimulus frame.
 Responses were collected via a 1-ms precise USB keyboard.
@@
 The task required participants to mentally make a spatial transformation of the stimulus' location according to the rule dictated by the task cue, and to make a spatially-congruent response to this translated location.
-For example, if the stimulus was in the top-right corner, the participant would need to make a top-left response if the task was ``horizontal'', a bottom-right response if the task was ``vertical'', and a bottom-left response if the task was ``diagonal''.
+For example, if the stimulus was in the top-right corner of the frame, the participant would need to make a top-left response if the task was ``horizontal'', a bottom-right response if the task was ``vertical'', and a bottom-left response if the task was ``diagonal''.
 Responses were made on the numerical part of the keyboard, using the ``4'', ``5'', ``1'', and ``2'' keys for top-left, top-right, bottom-left, and bottom-right responses respectively.
@@
 The cue for the next trial was chosen randomly with the constraint that task repetitions could not occur (cf., Mayr, 2002); the stimulus location was chosen randomly with no constraints on each trial.
-If participants made an error, the word ``Error!'' appeared in red for xxms above the stimulus frame (in the cue's position).
+If participants made an error, the word ``Error!'' appeared in red for 1000ms above the stimulus frame (in the cue's position).
 
-Participants were presented with 16 trials as practice (which could be repeated upon request). The main experiment presented 4 blocks of 120 trials.
+Participants were presented with 16 trials as practice. The practice block was repeated once if the participant made more than four errors. The main experiment presented 4 blocks of 120 trials.
 
@@
 \section{Results}
-Participants who failed to maintain session-wise accuracy above 90\% were immediately discarded from analysis.
 For response time analysis, the first two trials from each block were removed, as were error trials and the two trials following an error.
@@
 Response times were analysed via a two factor repeated measures analysis of variance (ANOVA) with the factors as described in \emph{Design}.
-There was a significant main effect of \emph{Sequence}, with slower RTs to ABA sequences (1,025ms) than to CBA sequences (958ms), $F$(1, 75) = 94.14, $p$<.001, $\eta_g^2$ = .018.
+There was a significant main effect of \emph{Sequence}, with slower RTs to ABA sequences (1,025ms) than to CBA sequences (958ms), $F$(1, 75) = 94.14, $p$<.001, $\eta_G^2$ = .018.
 The Bayes factor for this main effect was $BF_{10}$ = 1e+12, which provides substantial support for the presence of n--2 repetition costs.
-There was also a significant main effect of \emph{Response Sequence}, with faster RTs to response repetitions (976ms) than to response switches (1,007ms), $F$(1, 75) = 18.21, $p$<.001, $\eta_g^2$ = .004.
+There was also a significant main effect of \emph{Response Sequence}, with faster RTs to response repetitions (976ms) than to response switches (1,007ms), $F$(1, 75) = 18.21, $p$<.001, $\eta_G^2$ = .004.
 The Bayes factor for this main effect was $BF_{10}$ = 338.77, which again provides substantial support for the alternative hypothesis.
-Critically, there was a significant interaction of both factors, $F$(1, 75) = 9.60, $p$<.01, $\eta_g^2$ = .001.
-The n--2 repetition cost was 48ms for response repetitions [t(75) = 4.2, $p$<.001] and 86ms for response switches [t(75) = 13.0, $p$<.001].
+Critically, there was a significant interaction of both factors, $F$(1, 75) = 9.60, $p$<.01, $\eta_G^2$ = .001.
+The n--2 repetition cost was 48ms for response repetitions [$t$(75) = 4.2, $p$<.001; $BF_{10}$ = 271.24] and 86ms for response switches [$t$(75) = 13.0, $p$<.001; $BF_{10}$ = 7.11e+17].
 
@@
 We stopped data collection after 76 participants, as at this point the criteria for our stopping rule had been reached\footnote{We could have stopped after 75 participants, but the last two participants were tested in successive sessions, so the Bayes factor was not checked until after the final participant.}.
-The final Bayes Factor for the difference of n--2 repetition costs for response repetitions and response switches was $BF_{10}$ = 9.974, which suggests that the alternative hypothesis is about 10 times more likely given than the data, which provides strong support that n--2 repetition costs are influenced by response repetitions.
+The final Bayes Factor for the difference of n--2 repetition costs for response repetitions and response switches was $BF_{10}$ = 9.97, which suggests that the alternative hypothesis is about 10 times more likely given than the data, which provides strong support that n--2 repetition costs are influenced by response repetitions.
 
-\begin{figure}
+\begin{figure*}
 \begin{center}
@@
 \end{center}
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{figure}
+\begin{figure*}
 \begin{center}
-\includegraphics[width = \textwidth]{Images/recruitmentOrder.pdf}
+\includegraphics[width =\textwidth]{Images/recruitmentOrder.pdf}
 \caption{Simulated progression of the Sequential Bayes Factors for a random set of 50 different recruitment orders for the current data set. See text for details.}
@@
 \end{center}
-\end{figure}
+\end{figure*}
+
+\subsubsection{Bayesian Parameter Estimation}
+We wished to supplement our Bayes factor analysis with Bayesian parameter estimation of the mean and effect size of the difference in n--2 task repetition cost between response repetitions and response switches.
+As such, we used the (default) methods outlined by \cite{Kruschke2013}.
+The input to the analysis was the n--2 task repetition cost for response repetitions minus the n--2 task repetition cost for response switches.
+The posterior distributions for mean difference and effect size of difference (Cohen's $d$) are shown in Figure \ref{fig:bayesParameter}.
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width =\textwidth]{Images/bayesParameter.pdf}
+\caption{Bayesian posterior distributions for the parameters of mean difference and effect size of difference for n--2 task repetition cost [response repetition] minus n--2 task repetition cost [response switch].
+HDI = Highest Density Interval.
+See text for details.}
+\label{fig:bayesParameter}
+\end{center}
+\end{figure*}
+
+These posterior distributions present histograms of the Bayesian posterior estimate of the true mean and effect size underlying the data we obtained.
+The black horizontal bar represents the 95\% Highest Density Interval (HDI); in contrast to frequentist confidence intervals, we can interpret this interval as the span of parameter values we are 95\% certain the true underlying parameter lies within.
+The mean difference in n--2 task repetition costs for response repetitions and response switches is estimated to be -37ms; the HDI does not cross zero, so we can be confident that there is a difference between response repetitions and switches.
+Note, though, that the effect size of this difference is in the small range.
+For hypothesis testing (i.e., assessing whether episodic retrieval does impact the n--2 repetition cost or not), this is less relevant, but it is important to note if we wish to explore \emph{how much} episodic retrieval might affect n--2 repetition costs.
 
 \subsection{Accuracy}
-Accuracy analysis showed no significant effect of task sequence [$F$(1, 75) = 3.36, $p$=.07, $\eta_g^2$ = .006]; the Bayes factor for this main effect was $BF_{10}$ = 0.618, which provides only anecdotal support for the null.
-The main effect of response repetition was significant [$F$(1, 75) = 12.17, $p$<.001, $\eta_g^2$ = .019], suggestive of better accuracy for response repetitions (96.28\%) than for response switches (95.41\%).
-The Bayes factor was $BF_{10}$ = 29.66, which provides substantial support for the alternative.
-The interaction was not significant [$F$(1, 75) = 1.32, $p$=.25, $\eta_g^2$ = .003]; the Bayes factor was $BF_{10}$ = 0.238, which provides moderate support for the null hypothesis.
+Accuracy analysis showed no significant effect of task sequence [$F$(1, 75) = 3.36, $p$=.07, $\eta_G^2$ = .006]; the Bayes factor for this main effect was $BF_{10}$ = 0.618, which provides only anecdotal support for the null.
+The main effect of response repetition was significant [$F$(1, 75) = 12.17, $p$<.001, $\eta_G^2$ = .019], suggestive of better accuracy for response repetitions (96.28\%) than for response switches (95.41\%).
+The Bayes factor was $BF_{10}$ = 29.66, which provides strong support for the alternative.
+The interaction was not significant [$F$(1, 75) = 1.32, $p$=.25, $\eta_G^2$ = .003]; the Bayes factor was $BF_{10}$ = 0.238, which provides moderate support for the null hypothesis.
 
@@
 
-For clarification, note that we have not provided evidence that episodic retrieval can explain the n--2 task repetition cost entirely, but rather it reduces the cost.
-Indeed, the n--2 task repetition cost was still statistically significant even when the trial parameters matched across n--2 task repetitions [i.e., n--2 response repetitions; \emph{t}(75) = 4.20, $p$<.001; $BF_{10}$ = 286.50].
+For clarification, note that we have not provided evidence that episodic retrieval can explain the n--2 task repetition cost entirely, but rather that it reduces the cost.
+Indeed, the n--2 task repetition cost was still statistically significant even when the trial parameters matched across n--2 task repetitions (i.e., n--2 response repetitions).
 Therefore, our findings do not provide evidence against the inhibitory explanation of these costs.
@@
 The modifications were made to enhance the magnitude of n--2 task repetition costs, so that modulation of this cost with response repetitions could be more easily detected.
-Specifically, removing the possibility of n--2 task repetitions likely enhanced the n--2 task repetition cost as it has been shown that allowing immediate repetitions reduces this cost \citep{Philipp2006}.
+Specifically, removing the possibility of immediate task repetitions likely enhanced the n--2 task repetition cost as it has been shown that allowing immediate repetitions reduces this cost \citep{Philipp2006}.
 We also used the shortest RCI used by Mayr (150ms), as it is a consistent finding that this increases the n--2 repetition cost \cite{Gade2005, Grange2009, Mayr2000, Mayr2002}.

### 2015-11-26 2015/Episodic Retrieval & Inhibition/Data & Analysis Code/analysis.R

@@ -68,15 +68,15 @@ data <- subset(data, data$accTrim == 1)
 accuracy <- data %>%
   group_by(subject, stimRep, sequence) %>%
   summarise(acc = (sum(accuracy) / length(accuracy)))
-
-# now remove all error trials, so we are ready for RT analysis
-data <- subset(data, data$accuracy == 1)
 #------------------------------------------------------------------------------
 
 
 
 #------------------------------------------------------------------------------
 ### response time analysis
+
+# remove all error trials, so we are ready for RT analysis
+data <- subset(data, data$accuracy == 1)
 
 # trim the RTs with fixed standard deviation upper limit
 rtData <- getRTs(data = data, minRT = 150, sd = 2.5)
@@ -169,10 +169,24 @@ aovRT <- ezANOVA(
 #------------------------------------------------------------------------------
 
 
+#------------------------------------------------------------------------------
+### Bayesian t-test with Kruschke's t-test
+bayesK <- BESTmcmc(y1 = biDiff)
+
+# plot the mean and effect size estimates
+pdf("bayesParameter.pdf", width = 8, height = 5)
+par(mfrow = c(1, 2))
+plot(bayesK, which = c("mean"))
+plot(bayesK, which = c("effect"))
+dev.off()
+
+#------------------------------------------------------------------------------
+
+
 
 
 #------------------------------------------------------------------------------
-### do somple plotting
+### plot mean RTs (not in paper)
 pdf("meanRT.pdf", width = 8, height = 8)
 plot <- ggplot(rtSummary, (aes(x = sequence, y = meanRT, group = stimRep, 
                                colour = stimRep)))

### 2015-11-26 2015/Episodic Retrieval & Inhibition/Manuscript Files/main.tex
added prior robustness check

@@
 %%%--------------------------------------------------------------------------------------------
-\documentclass[a4paper, man, natbib]{apa6}
+\documentclass[a4paper, doc, natbib]{apa6}
 \usepackage[english]{babel}
@@
 
-% \newtoggle{jou}
-% \toggletrue{jou}
-% \togglefalse{jou}
-
 % \usepackage{lineno}
@@
 
-\note{{\bf Word Count:} 3,124 (Main body, not including abstract or references.)}
+\note{{\bf Word Count:} 3,280 (Main body, not including abstract or references.)}
 % \note{{\bf Under Review---Please, no direct quotes.}}
@@
 
-How the cognitive system addresses the stability--flexibility dilemma has been studied using the task switching paradigm \citep{Grange2014a,Kiesel2010,Vandierendonck2010}, wherein participants have to make speeded responses to simple cognitive tasks.
+How the cognitive system solves the stability--flexibility dilemma has been studied using the task switching paradigm \citep{Grange2014a,Kiesel2010,Vandierendonck2010}, wherein participants have to make speeded responses to simple cognitive tasks.
 For example, participants might be presented with number stimuli, and be asked to switch between judging whether the stimulus is odd/even or lower/higher than five.
@@
 It is a consistent finding that AB$A$ task switching sequences are performed slower and with less accuracy than CB$A$ sequences.
-This \emph{n--2 repetition cost} is thought to reflect the persisting inhibition of task A in an ABA sequence, which hinders its re-activation in the last trial of the triplet.
+This \emph{n--2 task repetition cost} is thought to reflect the persisting inhibition of task A in an ABA sequence, which hinders its re-activation in the last trial of the triplet.
 
-The n--2 repetition cost is important as it appears to be robust against non-inhibitory explanations \citep{Mayr2007}.
-One potential explanation of the n--2 repetition cost that does not assume inhibition---the episodic retrieval account \citep{Neill1997}---was explored by \cite{Mayr2002}.
+The n--2 task repetition cost is important as it appears to be robust against non-inhibitory explanations \citep{Mayr2007}.
+One potential explanation of the n--2 task repetition cost that does not assume inhibition---the episodic retrieval account \citep{Neill1997}---was explored by \cite{Mayr2002}.
 This theory suggests (adapted to a task switching context) that when a task has been performed an episodic trace of trial parameters (such as the cue, stimulus characteristics, and the response made) is stored in memory.
@@
 If the parameters of the presented trial differ from that of the retrieved episode (e.g., a different response is required), a mismatch cost occurs relative to if the retrieved episode matches parameters of the current trial (which will prime performance).
-Thus, according to this account, n--2 repetition costs reflect a mismatch cost, as trial parameters typically differ between both instances of task A in an ABA sequence.
+Thus, according to this account, n--2 task repetition costs reflect a mismatch cost, as trial parameters typically differ between both instances of task A in an ABA sequence.
 
@@
 For example, if the target is in the bottom-left of the display and the current rule is ``vertical'', the correct response would be an upper-left response (as this reflects a vertical transformation of a bottom-left target).
-The parameters that might be stored in an episodic trace include (at least) the cue used, the target's location, and the response made.
-In this paradigm, trial parameters can either match or mismatch across ABA and CBA sequences.
+The parameters that might be stored in an episodic trace include (at least) the cue presented, the target's location, and the response made.
+In this paradigm, trial parameters can either match or mismatch across ABA and CBA sequences\footnote{Note that with one cue per task, the cue for task A will always be the same across an ABA sequence.}.
 For example, if the target is in the same location for task A across an ABA sequence, the same response will be required (i.e., an n--2 response repetition).
@@
 
-The Bayes factor for the critical statistical test from Mayr's (2002) study ($BF_{10}$ = 0.315) suggests that the null hypothesis is about 3 times more likely than the alternative, given the data, which provides anecdotal--moderate support for the null.
+The Bayes factor for the critical statistical test from Mayr's (2002) study ($BF_{10}$ = 0.315)\footnote{For all Bayes factors reported in this paper we use a non-informative prior on the alternative hypothesis, which is assumed to be distributed as a Cauchy with scaling factor $r$ = 0.707.} suggests that the null hypothesis is about 3 times more likely than the alternative, given the data, which provides anecdotal-to-moderate support for the null.
 As this Bayesian analysis does not provide decisive evidence for the null, and given the importance of assessing to what extent (if any) episodic retrieval can influence n--2 task repetition costs in task switching, we were interested in performing a replication of Mayr's study to gather more evidence.
@@
 The current study replicated critical aspects of Mayr's (2002) design relevant to n--2 task repetitions.
-As Mayr's study was also interested in exploring to what extent the paradigm generated typical task switching effects (such as switch costs, effects of preparation, and effects of the delay between tasks), we made some changes to the original design of Mayr.
+As Mayr's study was also interested in exploring to what extent the rule-switching paradigm generated typical task switching effects (such as switch costs, effects of preparation, and effects of the delay between tasks), we made some changes to the original design of Mayr.
 Specifically, immediate task repetitions were not allowed; it has been shown that including immediate task repetitions reduces the n--2 task repetition cost \citep{Philipp2006}, so we removed this possibility.
@@
 Responses were made on the numerical part of the keyboard, using the ``4'', ``5'', ``1'', and ``2'' keys for top-left, top-right, bottom-left, and bottom-right responses respectively.
-Participants were asked to respond as quickly and as accurately as possible.
+Participants were asked to respond as quickly and as accurately as possible, using the index finger of their right hand.
+In between trials, participants were asked to place their finger in the centre of the four response keys.
 Once a response was registered, the frame was cleared for a response--cue interval of 150ms, after which time a new cue appeared for the next trial.
@@
 \label{fig:bayesFactor}
+\end{center}
+\end{figure*}
+
+\subsubsection{Robustness Check on Bayesian Priors}
+We used a default prior distribution on the effect size for the alternative hypothesis in the Bayes factor analysis, which was assumed to be distributed as a Cauchy distribution with scale parameter $r$ = 0.707.
+To examine how robust our findings were to the choice of prior, we conducted a robustness check by re-calculating the Bayes factor across a wide range of priors by varying scale parameter $r$: As $r$ increases, the prior distribution becomes wider, reflecting a prior for larger effects; $r$s closer to zero make the distribution narrower, reflecting a prior for smaller effects.
+The robustness check is plotted in Figure \ref{fig:robustPrior}.
+This figure shows our conclusions (and our stopping rule) are robust to the prior used: Evidence favours the alternative hypothesis across all prior widths.
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width = \textwidth]{Images/robustPrior.pdf}
+\caption{Robustness check of Bayes factor across a wide range of priors.}
+\label{fig:robustPrior}
 \end{center}
@@
 Any one of these modifications could explain the difference in results between this study and that of Mayr (2002).
-Future research should aim to examine the potential role for episodic retrieval influencing n--2 task repetition costs by providing further replications to this study \citep{OpenScienceCollaboration2015}.
+Future research should aim to examine the potential role for episodic retrieval influencing n--2 task repetition costs by providing further replications and conceptual extensions to this study \citep{OpenScienceCollaboration2015}.
 

### 2015-11-26 2015/Episodic Retrieval & Inhibition/Data & Analysis Code/analysis.R

@@ -117,6 +117,35 @@ text(0, log(1/3) - 0.4, labels = "Evidence for Null",
      cex = 1.5, col = "black", pos = 4)
 dev.off()
 
+#---
+## robustness check based on prior
+
+# what is the t-value for the data?
+tVal <- as.numeric(t.test(biRT$rep, biRT$sw, paired = TRUE)[['statistic']])
+
+# what are the priors to explore?
+priors <- seq(from = 0.01, to = 1.5, length.out = 1000)
+
+# get the Bayes factor for each prior value
+robust <- sapply(priors, function(x) 
+  exp(ttest.tstat(t = tVal, n1 = nrow(biRT), rscale = x)[['bf']]))
+
+# plot it
+pdf("robustPrior.pdf", width = 8, height = 5)
+plot(priors, robust, type = "l", lwd = 2, col = "gray48",
+     ylim = c(0, max(robust)), xaxt = "n", xlab = "Caucy Prior Width (r)", 
+              ylab = "Bayes Factor (10)")
+abline(h = 0, lwd = 1)
+abline(h = 6, col = "black", lty = 2, lwd = 2)
+axis(1, at = seq(0, 1.5, 0.25))
+points(0.707, extractBF(bfDiff, onlybf = TRUE), col = "black", 
+       cex = 1, pch = 21, bg = "black")
+legend(x = 1, y = 13, legend = c("Default Prior", "Stopping Rule"),
+       pch = c(21, NA), lty = c(NA, 2), lwd = c(NA, 2), pt.cex = c(1, NA),
+       col = c("black", "black"), pt.bg = "black", bty = "n")
+dev.off()
+
+
 
 #---------
 ### ANOVA analsyis

### 2015-11-27 2015/Episodic Retrieval & Inhibition/Manuscript Files/main.tex
minor update to manuscript file

@@
 
-\abstract{Inhibition in task switching is inferred from n--2 task repetition costs: the observation that AB$A$ task switching sequences are responded to slower than CB$A$ sequences.
+\abstract{Inhibition in task switching is inferred from n--2 repetition costs: the observation that AB$A$ task switching sequences are responded to slower than CB$A$ sequences.
 This is thought to reflect the persisting inhibition of task A, which slows re-activation attempts.
@@
 In a rule-switching paradigm, Mayr reported no significant difference in n--2 repetition cost when the trial parameters repeated or switched across an ABA sequence, in contrast to the episodic retrieval account.
+This conclusion rests on accepting a null hypothesis, which cannot be achieved with null hypothesis significance testing.
 Here we provide a replication of the critical aspects of Mayr's design.
@@
 One cognitive process thought to be essential for task switching performance is the inhibition of competing tasks.
-Evidence for inhibition comes from the so-called backward inhibition paradigm \citep{Koch2010, Mayr2000}, where participants are required to switch between three tasks (A, B, and C).
+Evidence for inhibition comes from the backward inhibition paradigm \citep{Koch2010, Mayr2000}, where participants are required to switch between three tasks (A, B, and C).
 It is a consistent finding that AB$A$ task switching sequences are performed slower and with less accuracy than CB$A$ sequences.
@@
 The n--2 task repetition cost is important as it appears to be robust against non-inhibitory explanations \citep{Mayr2007}.
-One potential explanation of the n--2 task repetition cost that does not assume inhibition---the episodic retrieval account \citep{Neill1997}---was explored by \cite{Mayr2002}.
-This theory suggests (adapted to a task switching context) that when a task has been performed an episodic trace of trial parameters (such as the cue, stimulus characteristics, and the response made) is stored in memory.
+One potential explanation of the n--2 task repetition cost that does not assume inhibition was explored by \cite{Mayr2002}.
+This \emph{episodic retrieval} account \citep{Neill1997} suggests (adapted to a task switching context) that when a task has been performed an episodic trace of trial parameters (such as the cue, stimulus characteristics, and the response made) is stored in memory.
 When this task is cued again, retrieval of the most recent episodic trace occurs.
@@
 In this case, the episodic retrieval account would predict facilitated performance relative to an n--2 response switch as in the former case the current trial parameters match perfectly the retrieved episodic trace.
-Thus, the episodic account would predict reduced (or zero) n--2 task repetition costs for n--2 response repetitions compared to n--2 response switches (where there is a mismatch between trial parameters and the retrieved episodic trace).
+Thus, the episodic account would predict reduced n--2 task repetition costs for n--2 response repetitions compared to n--2 response switches (where there is a mismatch between trial parameters and the retrieved episodic trace).
 
@@
 The purpose of the current study was to re-examine the evidence for the effect of episodic retrieval on n--2 task repetition costs.
-The conclusion of \cite{Mayr2002} rests on the acceptance of a null hypothesis (i.e., no difference of n--2 task repetition costs), which cannot be achieved via standard null hypothesis significance testing \citep[NHST;][]{Gallistel2009, Wagenmakers2007}; however, evidence in favour of a null hypothesis (given some data) can be obtained using Bayes Factors \citep[e.g.,][]{Rouder2009}.
-The Bayes Factor (denoted $BF_{10}$) quantifies the relative evidence provided by the data in favour of an alternative hypothesis (i.e., n--2 task repetition costs are different for response repetitions and response switches) over a null hypothesis (i.e., n--2 repetition costs are equivalent).
+The conclusion of \cite{Mayr2002} rests on the acceptance of a null hypothesis (i.e., no difference of n--2 task repetition costs), which cannot be achieved via standard null hypothesis significance testing \citep{Gallistel2009, Wagenmakers2007}; however, evidence in favour of a null hypothesis (given some data) can be obtained using Bayes factors \citep[e.g.,][]{Rouder2009}.
+The Bayes factor (denoted $BF_{10}$) quantifies the relative evidence provided by the data in favour of an alternative hypothesis (i.e., n--2 task repetition costs are different for response repetitions and response switches) over a null hypothesis (i.e., n--2 repetition costs are equivalent).
 
-The Bayes factor for the critical statistical test from Mayr's (2002) study ($BF_{10}$ = 0.315)\footnote{For all Bayes factors reported in this paper we use a non-informative prior on the alternative hypothesis, which is assumed to be distributed as a Cauchy with scaling factor $r$ = 0.707.} suggests that the null hypothesis is about 3 times more likely than the alternative, given the data, which provides anecdotal-to-moderate support for the null.
-As this Bayesian analysis does not provide decisive evidence for the null, and given the importance of assessing to what extent (if any) episodic retrieval can influence n--2 task repetition costs in task switching, we were interested in performing a replication of Mayr's study to gather more evidence.
+The Bayes factor for the critical statistical test from Mayr's (2002) study ($BF_{10}$ = 0.315)\footnote{For all Bayes factors reported in this paper we use a non-informative prior on the alternative hypothesis, which is assumed to be distributed as a Cauchy with scaling factor $r$ = 0.707.} suggests that the null hypothesis is about 3 times more likely than the alternative, given the data, which provides anecdotal-to-moderate support for the null \citep[e.g.,][]{Schoenbrodtinpress}.
+As this Bayesian analysis does not provide compelling evidence for the null, and given the importance of assessing to what extent (if any) episodic retrieval can influence n--2 task repetition costs in task switching, we were interested in performing a replication of Mayr's study to gather more evidence.
 
 The current study replicated critical aspects of Mayr's (2002) design relevant to n--2 task repetitions.
-As Mayr's study was also interested in exploring to what extent the rule-switching paradigm generated typical task switching effects (such as switch costs, effects of preparation, and effects of the delay between tasks), we made some changes to the original design of Mayr.
+As Mayr's study was also interested in exploring to what extent the rule-switching paradigm generated typical task switching effects (such as switch costs, effects of preparation, and effects of the delay between tasks), we made some changes to the original design so that it was more tailored toward assessing n--2 task repetition costs.
 Specifically, immediate task repetitions were not allowed; it has been shown that including immediate task repetitions reduces the n--2 task repetition cost \citep{Philipp2006}, so we removed this possibility.
@@
 Mayr did find that n--2 repetition costs were larger with shorter response--cue intervals (RCI; the time between the response to one trial and the onset of the cue for the next trial), a typical finding for n--2 task repetition costs \citep{Gade2005, Grange2009, Mayr2000}.
-Therefore, in order to obtain large n--2 task repetition costs we only used a short RCI.
+Therefore, in order to obtain larger n--2 task repetition costs we only used a short RCI.
 
@@
 The stimulus display consisted of an 8cm by 8cm square frame.
-A black circle (diameter = 1cm) served as the trial stimulus.
+A black circle (diameter = 1 cm.) served as the trial stimulus.
 Possible cues were the words ``horizontal'', ``vertical'', or ``diagonal'', and were presented in size 22 black Verdanna font directly above the stimulus frame.
-Responses were collected via a 1-ms precise USB keyboard.
+Responses were collected via a 1-ms.
+precise USB keyboard.
 
@@
 n-- response switch).
-The dependent variables were response time (RT) in milliseconds (ms) and percent accuracy (\%).
+The dependent variables were response time (RT) in milliseconds (ms.) and percent accuracy (\%).
 
@@
 \begin{center}
-\includegraphics[width =\textwidth]{Images/recruitmentOrder.pdf}
+\includegraphics[width =  \textwidth]{Images/recruitmentOrder.pdf}
 \caption{Simulated progression of the Sequential Bayes Factors for a random set of 50 different recruitment orders for the current data set. See text for details.}
@@
 \begin{center}
-\includegraphics[width =\textwidth]{Images/bayesParameter.pdf}
+\includegraphics[width = \textwidth]{Images/bayesParameter.pdf}
 \caption{Bayesian posterior distributions for the parameters of mean difference and effect size of difference for n--2 task repetition cost [response repetition] minus n--2 task repetition cost [response switch].
@@
 These posterior distributions present histograms of the Bayesian posterior estimate of the true mean and effect size underlying the data we obtained.
-The black horizontal bar represents the 95\% Highest Density Interval (HDI); in contrast to frequentist confidence intervals, we can interpret this interval as the span of parameter values we are 95\% certain the true underlying parameter lies within.
+The black horizontal bar represents the 95\% Highest Density Interval (HDI); in contrast to frequentist confidence intervals, we can interpret this interval as the range of parameter values we are 95\% certain the true underlying parameter lies within.
 The mean difference in n--2 task repetition costs for response repetitions and response switches is estimated to be -37ms; the HDI does not cross zero, so we can be confident that there is a difference between response repetitions and switches.

### 2015-11-27 2015/Episodic Retrieval & Inhibition/Data & Analysis Code/analysis.R

@@ -133,7 +133,7 @@ robust <- sapply(priors, function(x)
 # plot it
 pdf("robustPrior.pdf", width = 8, height = 5)
 plot(priors, robust, type = "l", lwd = 2, col = "gray48",
-     ylim = c(0, max(robust)), xaxt = "n", xlab = "Caucy Prior Width (r)", 
+     ylim = c(0, max(robust)), xaxt = "n", xlab = "Cauchy Prior Width (r)", 
               ylab = "Bayes Factor (10)")
 abline(h = 0, lwd = 1)
 abline(h = 6, col = "black", lty = 2, lwd = 2)

### 2016-01-20 Temporal Distinctiveness & Mixture Distributions/Revision 1/Manuscript Files/main.tex
folder re-structure

--- 2015-11-05 2015/Temporal Distinctiveness & Mixture Distributions/Manuscript Files/main.tex
@@
 %%%--------------------------------------------------------------------------------------------
-\documentclass[a4paper, jou, natbib]{apa6}
+\documentclass[a4paper, man, natbib]{apa6}
 \usepackage[english]{babel}
@@
 
-\newtoggle{jou}
-\toggletrue{jou}
-%\togglefalse{jou}
+% \newtoggle{jou}
+% \toggletrue{jou}
+% \togglefalse{jou}
 
-%\usepackage{lineno}
+\usepackage{lineno}
+\linenumbers
 
-\title{Temporal Distinctiveness in Task Switching: Assessing the Mixture-Distribution Assumption}
+\title{Temporal Distinctiveness in Task Switching: Assessing the Mixture-Distribution Assumption --- Revision 1}
 \shorttitle{Mixture Distribution Assumption}
@@
 I am grateful to Chris Donkin for discussion regarding the Linear Ballistic Accumulator model.
-All raw data, analysis code, and model code are available to download at http://bit.ly/1l22EUV.}
+All raw data, analysis code, and model code are available to download at http://bit.ly/1YumV7i.}
 
@@
 The net result is a reduced switch cost.
+\jg{It should be noted that several studies have found task repetition RTs slow as a function of RCI, the evidence for the predicted speeding of switch RT is less clear.
+In fact, several studies have found no evidence for RCI affecting switch RTs in the predicted direction \citep{Altmann2005, Horoufchin2011a, Meiran2000a}.
+However, slowing of repetition RTs with increasing RCI remains an important finding supporting decay accounts.}
 
-However, this decay account was recently challenged by \cite{Horoufchin2011a} who manipulated RCI on a trial-to-trial basis between a short- (e.g., 50milliseconds, ms) and a long-RCI (1,000ms); they found that the reduction of switch cost was not a function of \emph{absolute} time of the RCI (e.g., between the previous trial n--1 and the current cue at n), but rather was a function of the ratio of the current RCI to that from the previous trial (between trials n--2 and n--1).
+However, this decay account was recently challenged by \cite{Horoufchin2011a} who manipulated RCI on a trial-to-trial basis between a short- (e.g., 50milliseconds, ms) and a long-RCI (1000ms); they found that the reduction of switch cost was not a function of \emph{absolute} time of the RCI (e.g., between the previous trial n--1 and the current cue at n), but rather was a function of the ratio of the current RCI to that from the previous trial (between trials n--2 and n--1).
 Specifically, the switch cost was only reduced at longer RCIs when the previous RCI was short; when the previous RCI was also long, switch costs were not reduced.
@@
 \cite{Horoufchin2011a} proposed these findings supported an \emph{interference} account of RCI effects, and were not compatible with a decay account.
-Relating to a temporal ratio model of serial memory \citep[SIMPLE][]{Brown2007}, the authors suggested that when presented with a cue on the current trial, the cognitive system engages in a retrieval attempt of the previous episodic memory trace of this task; such retrieval attempts have been shown by \cite{Brown2007} to be influenced by the \emph{temporal distinctiveness} (TD) of the episodic trace.
+Relating to a temporal ratio model of serial memory \citep[SIMPLE][]{Brown2007}, the authors suggested that when presented with a cue on the current trial, the cognitive system engages in a retrieval attempt of the previous episodic memory trace of \jg{the task-set associated with this cue}; such retrieval attempts have been shown by \cite{Brown2007} to be influenced by the \emph{temporal distinctiveness} (TD) of the episodic trace.
 TD refers to the degree to which the targeted episodic trace is distinguishable in memory from competing memory traces presented within a similar time-window to that of the target trace.
 Traces that are clustered closely in episodic memory will not be distinguishable, and thus have low TD and will have low probability to be retrieved.
-The sequential varying of the RCI was suggested to affect the TD of the targeted episodic trace in memory.
+The sequential varying of the RCI was suggested to affect the TD of the targeted episodic trace \jg{of the task-set} in memory.
 TD is operationalised in relation to the RCI-ratio, which is the ratio of the RCI(n--2:n--1) / RCI(n--1:current trial).
@@
 \begin{center}
-\includegraphics[width = 0.5 \textwidth]{Images/tdAccount.pdf}
+\includegraphics[width = \textwidth]{Images/tdAccount.pdf}
 \caption{Various manipulations of temporal distinctiveness as used by \cite{Horoufchin2011, Horoufchin2011a}.
@@
 
-When RCI-ratio is high, so too is TD, which means there is a high probability the episodic trace can be retrieved; successful retrieval primes performance, leading to a fast RT.
-When the RCI-ratio is low, so too is TD, which lowers the probability of successful retrieval.
+When RCI-ratio is high, so too is TD, which means there is a high probability the episodic trace can be retrieved; successful retrieval \jg{of the task-set} primes performance, leading to a fast RT.
+When the RCI-ratio is low, so too is TD, which lowers the probability of successful retrieval \jg{of the task-set}.
 When retrieval fails, the task must be performed via a slower, algorithmic route, leading to a slower RT \citep[see][for a similar proposal]{Logan2002}.
@@
 
-Figure \ref{fig:grangeData} represents a portion of data reported by \cite{Grangeinrevision}---a brief overview of the pertinent method details and analysis are presented in Appendix A---that replicates the main findings from \cite{Horoufchin2011a}; focussing on repetition RTs, increasing RCI from 50ms to 1,000ms has negligible effect on RTs when the RCI was the same as the previous trial (e.g., these data points relate to D and C in Figure \ref{fig:tdAccount}); this is because both of these conditions have an identical RCI-ratio of 1, and hence have the same TD.
-RCI has a considerable effect on repetition RT when the RCI has changed from the previous trial: RT is very fast when the RCI is 50ms, as this condition has a very high RCI-ratio, hence high TD (Figure \ref{fig:tdAccount} A); RT is very slow when the RCI is 1,000ms, as this condition has a very low RCI-ratio, hence low TD (Figure \ref{fig:tdAccount} B).
+Figure \ref{fig:grangeData} represents a portion of data reported by \cite{Grangeinrevision}---a brief overview of the pertinent method details and analysis are presented in Appendix A---that replicates the main findings from \cite{Horoufchin2011a}; focussing on repetition RTs, increasing RCI from 50ms to 1000ms has negligible effect on RTs when the RCI was the same as the previous trial (e.g., these data points relate to D and C in Figure \ref{fig:tdAccount}); this is because both of these conditions have an identical RCI-ratio of 1, and hence have the same TD.
+RCI has a considerable effect on repetition RT when the RCI has changed from the previous trial: RT is very fast when the RCI is 50ms, as this condition has a very high RCI-ratio, hence high TD (Figure \ref{fig:tdAccount} A); RT is very slow when the RCI is 1000ms, as this condition has a very low RCI-ratio, hence low TD (Figure \ref{fig:tdAccount} B).
 
-\iftoggle{jou}{
-\begin{figure}
-\begin{center}
-\includegraphics[width = 0.5\textwidth]{Images/grangeData.pdf}
-\caption{Data from \cite{Grangeinrevision} showing mean response time in milliseconds (ms) for task repetition and switch trials as a function of the current response--cue interval (x-axis) and whether the RCI is the same or different from the previous trial.
+% \iftoggle{jou}{
+% \begin{figure}
+% \begin{center}
+% \includegraphics[width = 0.5\textwidth]{Images/grangeData.pdf}
+% \caption{Data from \cite{Grangeinrevision} showing mean response time in milliseconds (ms) for task repetition and switch trials as a function of the current response--cue interval (x-axis) and whether the RCI is the same or different from the previous trial.
 Error bars denote  +/- 1 standard error around the mean.}
-\label{fig:grangeData}
-\end{center}
-\end{figure}
-}{
+% \label{fig:grangeData}
+% \end{center}
+% \end{figure}
+% }{
 \begin{figure}
@@
 \end{figure}
-}
+% }
 
@@
 Then, in a next step I extend the model of \cite{Grange2015} to predict whole RT-distributions, which allows a direct test of the mixture-distribution assumption.
+
+\jg{\subsection{Switch Trials}}
+\jg{Note that the current paper does not attempt to model switch RT performance.
+This is for several reasons.
+One is that there is evidence that RCI does not affect switch RT \citep{Altmann2005, Horoufchin2011a, Meiran2000a}.
+Second, the temporal distinctiveness account of \cite{Horoufchin2011a} mostly considers task repetition performance because the RCI-ratio did not influence switch trials.
+As such, the formal model of \cite{Grange2015} only modelled repetition RTs.
+As the purpose of the present paper is to test further the main assumptions of the account of \cite{Horoufchin2011a} and the formal model of \cite{Grange2015}, the current work continues to focus on repetition RT.
+A complete model would of course have to account for switch trial performance, too, but as these trials appear unaffected by temporal distinctiveness they are less interesting for the aims of the current paper.
+I leave discussion of this issue to the General Discussion.}
+
 %%%--------------------------------------------------------------------------------------------
@@
 \section{Assessing the Presence of Mixture-Distributions}
-\cite{VanMaanen2014} introduced a method---the ``fixed-point'' property test---for statistically testing the presence of a mixture-distribution, given two ``base'' distributions.
+\cite{VanMaanen2014} introduced a method---the ``fixed-point'' property test---for statistically testing the presence of a mixture-distribution.
 If distribution $z$ is a mixture of two base distributions $x$ and $y$, then the fixed-point property states that the probability density for distribution $z$, $f_{z}$, is a weighted sum of the probability densities of the other two distributions $f_{x}$ and $f_{y}$.
-Put simply, this implies that there exists a particular response time $t$ for which the probability of providing such as response is identical for all three distributions; that is $f_{x}(t)$ = $f_{z}(t)$ = $f_{y}(t)$.
+Put simply, this implies that there exists a particular response time $t$ for which the probability of providing such a response is identical for all three distributions; that is $f_{x}(t)$ = $f_{z}(t)$ = $f_{y}(t)$.
 
@@
 
-\iftoggle{jou}{
-\begin{figure}
-\begin{center}
-\includegraphics[width = 0.5\textwidth]{Images/fpExample.pdf}
-\caption{Example of the fixed-point property in three distributions.
+% \iftoggle{jou}{
+% \begin{figure}
+% \begin{center}
+% \includegraphics[width = 0.5\textwidth]{Images/fpExample.pdf}
+% \caption{Example of the fixed-point property in three distributions.
 Distribution $z$ is a mixture of distributions $x$ and $y$ with mixture probability $p$ set to $p$ = 0.7.
@@
 The distributions share a common crossing point at about 0.850 seconds.}
-\label{fig:fpExample}
-\end{center}
-\end{figure}
-}{
+% \label{fig:fpExample}
+% \end{center}
+% \end{figure}
+% }{
 \begin{figure}
@@
 The critical question is whether intermediate RCI-ratios of 1 are a mixture of the fast and the slow distribution.
+\jg{For this test, I collapsed the 50--50 and 1000--1000 data, as both represent an RCI-ratio of 1.
+The mean difference between these two conditions was 54.8ms, but was not statistically significant, $t$(24) = 1.7496, $p$ = 0.09.
+The Bayes factor for this test was $BF_{01}$ = 1.26, which slightly favours the null of no difference (although this is not decisive).}
 
@@
 The data was then assessed for the presence of a fixed-point by passing it to the \texttt{fp} function provided in the form of \texttt{R} code from \citet{VanMaanen2014}.
-Visual representation of the fixed-point assessment is shown in Figure \ref{fig:mixtureDistributionData}.
+\jg{This takes the individual participants' RT data as input.} Visual representation of the fixed-point assessment is shown in Figure \ref{fig:mixtureDistributionData}.
 
-\begin{figure*}
+\begin{figure}
 \begin{center}
@@
 \end{center}
-\end{figure*}
+\end{figure}
 
-As shown in the left and center panels of Figure \ref{fig:mixtureDistributionData}, the three RT distribution functions share a common crossing point at just over 1 second.
-The right panel of Figure \ref{fig:mixtureDistributionData} shows box-plots of the distribution of crossing points for each pair for all subjects.
+As shown in the left and center panels of Figure \ref{fig:mixtureDistributionData}, the three \jg{group-averaged} RT distribution functions share a common crossing point at just over 1 second.
+The right panel of Figure \ref{fig:mixtureDistributionData} shows box-plots of the distribution \jg{across individual participant data} of crossing points for each pair.
 There is considerable overlap in the box-plots suggesting no difference between condition pairs of crossing point (supporting the fixed-point property).
-Together, this visual inspection provides good evidence that the RCI-ratio = 1 RT function is a weighted mixture of the ``slow'' RT distribution (where RCI-ratio = 0.05) and the ``fast'' RT distribution (where RCI-ratio = 20), as predicted by the temporal distinctiveness model \citep{Grange2015}.
+Together, this visual inspection provides good evidence that the RT function for the RCI-ratio of 1 is a weighted mixture of the ``slow'' RT distribution (where RCI-ratio = 0.05) and the ``fast'' RT distribution (where RCI-ratio = 20), as predicted by the temporal distinctiveness model \citep{Grange2015}.
 
@@
 
-\iftoggle{jou}{
-\begin{figure}
-\begin{center}
-\includegraphics[width = 0.5 \textwidth]{Images/modelOverview.pdf}
-\caption{Overview of the retrieval processes in the model.}
-\label{fig:modelOverview}
-\end{center}
-\end{figure}
-}{
+% \iftoggle{jou}{
+% \begin{figure}
+% \begin{center}
+% \includegraphics[width = 0.5 \textwidth]{Images/modelOverview.pdf}
+% \caption{Overview of the retrieval processes in the model.}
+% \label{fig:modelOverview}
+% \end{center}
+% \end{figure}
+% }{
 \begin{figure}
@@
 
-\cite{Grange2015} used the full mathematics of SIMPLE to obtain $p$(retrieved).
+\jg{All modelling was performed on group-averaged data.} \cite{Grange2015} used the full mathematics of SIMPLE to obtain $p$(retrieved).
 To reduce the number of free parameters, in the current model $p$(retrieved) was treated as a ``semi-fixed'' parameter.
 To achieve this, the RCI-ratio was calculated for each RCI-sequence condition in Figure \ref{fig:grangeData}.
-Specifically, the RCI-ratio was 20 for n--2 to n--1 RCIs of 50ms--1000ms; the ratio was 1 for RCIs of 1000ms--1000ms and 50ms--50ms; and the ratio was 0.05 for RCIs of 50ms--1,000ms.
+Specifically, the RCI-ratio was 20 for n--2 to n--1 RCIs of 1000ms---50ms; the ratio was 1 for RCIs of 1000ms--1000ms and 50ms--50ms; and the ratio was 0.05 for RCIs of 50ms--1000ms.
 $p$(retrieved) was ``semi-fixed'' in the sense that it was fixed at $p$(retrieved) = 1 for ratios of 20 (i.e., perfect retrieval) and fixed at $p$(retrieved) = 0 for ratios of 0.05 (i.e., failed retrieval); $p$(retrieved) was free to vary for ratios of 1.
 Thus, $p$(retrieved) controls the relative contribution of the two RT distributions for intermediate RCI ratios.
+\jg{It is of course possible that even in the RCI-ratio of 20 some retrieval failures occur (and vice-versa for RCI-ratios of 0.05).
+However, for the purposes of this modelling work, I use the simplifying assumption described.}
 
@@
 
-The model was fitted to the data via a version of Quantile Maximum Probability Estimation \citep[QMPE][]{Heathcote2002}, where the model is fit to RT quantiles rather than individual RTs as per maximum likelihood (see Appendix C for details).
+The model was fitted to the data via a version of Quantile Maximum Probability Estimation \citep[QMPE][]{Heathcote2002}, where the model is fit to \jg{observed frequencies between RT quantiles} rather than individual RTs as per maximum likelihood (see Appendix C for details).
 This method was used due to the relatively low number of trials per subject, and the rather low error rate.
@@
     \bottomrule
-    \end{tabular}%
-  \label{tab:bestParameters}%
-\end{table}%
+    \end{tabular}
+  \label{tab:bestParameters}
+\end{table}
 
-\begin{figure*}
+\begin{figure}
 \begin{center}
@@
 \end{center}
-\end{figure*}
+\end{figure}
 
@@
 Specifically, RT is plotted against $\vec{Q}$ $\times$ mean accuracy rather than just $\vec{Q}$.
-Error RT---shown in the Figure as open circles)---is error RT plotted against $\vec{Q}$ $\times$ (1 - mean accuracy).
+\jg{Perfect accuracy would thus be plotting RT against $\vec{Q}$.} Error RT---shown in the Figure as open circles)---is error RT plotted against $\vec{Q}$ $\times$ (1 - mean accuracy).
 
-The model fit to correct RT distributions is rather good.
-The model captures all of the main trends in the data: RT becomes facilitated as $p$(retrieved) increases (from left-to-right $p$(retrieved) = 0, $p$(retrieved) = 0.759, and $p$(retrieved) = 1).
+\jg{The overall fit statistic of the model was QMPE = 330.12.
+The model fit to correct RT distributions is rather good; the model's prediction for mean RT gave $R^{2}$ = 0.986.} The model captures all of the main trends in the data: RT becomes facilitated as $p$(retrieved) increases (from left-to-right $p$(retrieved) = 0, $p$(retrieved) = 0.759, and $p$(retrieved) = 1).
 This improvement in RT is largely at the slower end of the RT distribution.
-Also, the defective CDFs become steeper as $p$(retrieved) is increased, reflecting generally better accuracy.
+Also, \jg{the height of the defective CDFs increases as $p$(retrieved) is increased}, reflecting generally better accuracy.
 Importantly, the central plot shows a good fit of the model to the data, providing support that intermediate TDs are a mixture of two base distributions.
 
-The fit to the error RT distributions is not as good as for the correct RT distributions.
-However, accuracy was generally very high in this experiment (indeed, participants were excluded for not achieving greater than 80\% accuracy, and average accuracy was much higher).
+The fit to the error RT distributions is not as good as for the correct RT distributions; \jg{the model's prediction for mean RT gave $R^{2}$ = 0.864.} However, accuracy was generally very high in this experiment (indeed, participants were excluded for not achieving greater than 80\% accuracy, and average accuracy was much higher).
 So, there were often few error RTs per quantile bin during the model fit, making accurate estimation difficult.
@@
 \section{Conclusion}
-The present paper sought to assess the evidence in favour of a key prediction of the TD hypothesis of RCI effects in task switching, namely that RTs are a mixture of only one of two processes.
+The present paper sought to assess the evidence in favour of a key prediction of the TD hypothesis of RCI effects on task repetition trials in task switching, namely that repetition RTs are a mixture of only one of two processes.
 In sum, this paper has provided good support for the TD prediction, which provides more support for these theoretical accounts \citep{Grange2015, Horoufchin2011, Horoufchin2011a}.
@@
 Participants responded using the ``1'' and the ``9'' keys on the numerical part of the keyboard; 1 corresponded to ``letter'' and ``red'' responses, and 9 corresponded to ``number'' and ``blue'' responses.
-Once a response was registered, the grid was cleared for an RCI of either 50ms or 1,000ms (chosen randomly).
+Once a response was registered, the grid was cleared for an RCI of either 50ms or 1000ms (chosen randomly).
 The next task was chosen randomly.
@@
 
-\noindent where $T_{x}$ refers to the temporal age of an item.
+\noindent where $T_{x}$ refers to the temporal age of an item and $c$ scales the similarity.
 Temporal age is calculated from the current time.
-Based on the target traces $i$'s similarity, to its neighbours, its discriminability $D_{i}$ can be determined.
+\jg{So, with RCIs of 50ms---1000ms, $T_{i}$ would equal 1000ms, and $T_{j}$ would equal 1050ms.} Based on the target trace $i$'s similarity to its neighbours, its discriminability $D_{i}$ can be determined.
 This refers to how isolated the target trace $i$ is in episodic memory, and is given by
@@
 
-As we are only considering the similarity between two items ($i$ and $j$), and as an item's similarity to iself is 1, Equation \ref{eq:simpleDiscriminationA} becomes
+As we are only considering the similarity between two items ($i$ and $j$), and as an item's similarity to itself is 1, Equation \ref{eq:simpleDiscriminationA} becomes
 
 \begin{equation}
-D_{i} = \frac{1}{\sum\limits_{j = 1}^n \eta_{ij} + 1}.
+D_{i} = \frac{1}{\eta_{ij} + 1}.
 \label{eq:simpleDiscriminationB}
@@
 \begin{equation}
-p(R_{i}|D_{i}) = \frac{1}{1 + e^{-s(D_{i} - t)}}, 
+p(R_{i}|D_{i}) = \frac{1}{1 + e^{-s(D_{i} - thresh)}}, 
 \label{eq:simpleProb}
@@
 
-\noindent where $s$ and $t$ are free parameters which describe the slope of the transforming function and the threshold of retrieval, respectively.
+\noindent where $s$ and $thresh$ are free parameters which describe the slope of the transforming function and the threshold of retrieval, respectively.
 Given these equations, we can calculate the retrieval probability for each level of temporal distinctiveness in the behavioural experiment.
@@
 \subsection{LBA for Unitary Process}
-For a unitary process, to calculate the defective PDF of response option $i$ reaching threshold first (before $j$), one first needs the cumulative distribution function (CDF) for $i$ at time $t$, $F_{i}(t)$, given the model parameters $v$, $A$, $s$, and $t$ = $t - ter$), is given by
+For a unitary process, to calculate the defective PDF of response option $i$ reaching threshold first (before $j$), one first needs the cumulative distribution function (CDF) for $i$ at time $t$, $F_{i}(t)$, given the model parameters $v$, $A$, $s$, $b$, and $t$ = $t - ter$), is given by
 

### 2016-01-20 Episodic Retrieval & Inhibition/Data & Analysis Code/analysis.R
plot correction

@@ -7,7 +7,7 @@
 rm(list = ls())
 
 # set working directory
-setwd("~/Git/paperData/2015/Episodic Retrieval & Inhibition/Data & Analysis Code")
+setwd("~/Git/paperData/Episodic Retrieval & Inhibition/Data & Analysis Code")
 
 # load necessary functions file & load necessary packages
 source("functions.R")

### 2016-01-20 Episodic Retrieval & Inhibition/Data & Analysis Code/analysis.R
minor plot fix

@@ -139,10 +139,10 @@ abline(h = 0, lwd = 1)
 abline(h = 6, col = "black", lty = 2, lwd = 2)
 axis(1, at = seq(0, 1.5, 0.25))
 points(0.707, extractBF(bfDiff, onlybf = TRUE), col = "black", 
-       cex = 1, pch = 21, bg = "black")
+       cex = 1.2, pch = 21, bg = "skyblue")
 legend(x = 1, y = 13, legend = c("Default Prior", "Stopping Rule"),
        pch = c(21, NA), lty = c(NA, 2), lwd = c(NA, 2), pt.cex = c(1, NA),
-       col = c("black", "black"), pt.bg = "black", bty = "n")
+       col = c("black", "black"), pt.bg = "skyblue", bty = "n")
 dev.off()
 
 

### 2016-09-16 Episodic Retrieval & Inhibition/Manuscript Files/main.tex
folder re-structure
new version of episodic retrieval paper

--- 2015-11-27 2015/Episodic Retrieval & Inhibition/Manuscript Files/main.tex
@@
 
-\note{{\bf Word Count:} 3,280 (Main body, not including abstract or references.)}
+\note{{\bf Word Count:} 7,125 (Main body \& references, not including abstract.)}
+% 577 words in references.
 % \note{{\bf Under Review---Please, no direct quotes.}}
@@
 Email: grange.jim@gmail.com.
-All raw data and analysis code are available to download at http://bit.ly/1OgH9v0.}
+All raw data and analysis code are available to download at http://bit.ly/1P5cd0G.}
 
@@
 \cite{Mayr2002} reported an experiment testing a critical non-inhibitory account of this effect, namely episodic retrieval: If the trial parameters for task A match across an ABA sequence, responses should be facilitated due to priming from episodic retrieval; a cost would occur if trial parameters mismatch.
-In a rule-switching paradigm, Mayr reported no significant difference in n--2 repetition cost when the trial parameters repeated or switched across an ABA sequence, in contrast to the episodic retrieval account.
-This conclusion rests on accepting a null hypothesis, which cannot be achieved with null hypothesis significance testing.
-Here we provide a replication of the critical aspects of Mayr's design.
-Using Bayesian analysis to quantify evidence for or against a null hypothesis, we find evidence for reduced n--2 repetition costs when trial parameters repeat compared to when they switch.
-In contrast to Mayr's conclusion, we suggest that episodic retrieval can influence the measure of inhibition in task switching, although it cannot explain it entirely.}
+In a rule-switching paradigm, Mayr reported no significant difference in n--2 repetition cost when the trial parameters repeated or switched across an ABA sequence, in clear contrast to the episodic retrieval account.
+What remains unclear is whether successful episodic retrieval \emph{modulates} the n--2 repetition cost.
+Across three experiments---including a close replication of Mayr (2002)---we find clear evidence of reduced n--2 task repetition costs when episodic retrieval is controlled.
+We find that the effect of episodic retrieval on the n--2 task repetition cost is increased when the cue--task relationship is made more abstract, suggesting the effect is due to interference in establishing the relevant attentional set.
+We also demonstrate that the episodic retrieval effect is not influenced by retrieval of low-level, perceptual, elements.
+Together, the data suggest the n--2 task repetition cost---typically attributable to an inhibitory mechanism---is largely explained by episodic retrieval effects.}
 
-\keywords{Task switching; inhibition, episodic retrieval, cognitive control}
+\keywords{Task switching; inhibition, n--2 repetition cost, episodic retrieval, cognitive control}
 
@@
 It is a consistent finding that AB$A$ task switching sequences are performed slower and with less accuracy than CB$A$ sequences.
-This \emph{n--2 task repetition cost} is thought to reflect the persisting inhibition of task A in an ABA sequence, which hinders its re-activation in the last trial of the triplet.
+This effect---know as the \emph{n--2 task repetition cost}---is thought to reflect the persisting inhibition of task A in an ABA sequence, which hinders its re-activation in the last trial of the triplet.
 
-The n--2 task repetition cost is important as it appears to be robust against non-inhibitory explanations \citep{Mayr2007}.
+The n--2 task repetition cost is important as it is believed to be a good measure of cognitive inhibition as the n--2 task repetition cost appears to be robust against non-inhibitory explanations \citep{Mayr2007}.
 One potential explanation of the n--2 task repetition cost that does not assume inhibition was explored by \cite{Mayr2002}.
@@
 
-\cite{Mayr2002} assessed this alternative explanation by developing a paradigm where the match between trial parameters across an ABA sequence could be manipulated (see Figure \ref{fig:mayrExperiment}).
+\cite{Mayr2002} assessed this alternative explanation by developing a paradigm where the match between trial parameters (i.e., the cue, the stimulus, and the response) across an ABA sequence could be manipulated (see Figure \ref{fig:mayrExperiment}).
 Participants were required to apply a spatial transformation of a target's location according to one of three stimulus--response rules (vertical, horizontal, or diagonal transformations).
@@
 The parameters that might be stored in an episodic trace include (at least) the cue presented, the target's location, and the response made.
-In this paradigm, trial parameters can either match or mismatch across ABA and CBA sequences\footnote{Note that with one cue per task, the cue for task A will always be the same across an ABA sequence.}.
+This paradigm is able to test the episodic retrieval account of n--2 task repetition costs because trial parameters can either match or mismatch across n--2 task repetitions\footnote{Note that with one cue per task, the cue for task A will always be the same across an ABA sequence.}.
 For example, if the target is in the same location for task A across an ABA sequence, the same response will be required (i.e., an n--2 response repetition).
-In this case, the episodic retrieval account would predict facilitated performance relative to an n--2 response switch as in the former case the current trial parameters match perfectly the retrieved episodic trace.
-Thus, the episodic account would predict reduced n--2 task repetition costs for n--2 response repetitions compared to n--2 response switches (where there is a mismatch between trial parameters and the retrieved episodic trace).
+In this case, the episodic retrieval account would predict facilitated performance (i.e., an n--2 task repetition \emph{benefit}).
+An n--2 response switch, however, would produce an n--2 task repetition cost as there is a mismatch between trial parameters and the retrieved episodic trace (i.e., the response required).
 
@@
 \includegraphics[width = \textwidth]{Images/mayrExperiment.pdf}
-\caption{Schematic overview of Mayr's (2002) experimental procedure.
-The arrows are not displayed to participants, but reflect the spatial transformation required according to the given rule.
-See text for details.}
+\caption{Schematic overview of Mayr's (2002) experimental procedure. The arrows are not displayed to participants, but reflect the spatial transformation required according to the given rule. }
 \label{fig:mayrExperiment}
@@
 \cite{Mayr2002} found no statistically significant interaction between n--2 task repetition and n--2 response repetition [$F$(1, 38) = 1.3, $p$ = .26]; that is, there was no significant difference between n--2 task repetition costs for n--2 response repetitions and n--2 response switches.
-Mayr suggested this provided evidence against the episodic retrieval account of n--2 task repetition costs, and instead favours the inhibitory account.
+This provides clear evidence against the episodic retrieval account of n--2 task repetition costs, and instead supports the inhibitory account.
 
 \section{The Current Study}
-The purpose of the current study was to re-examine the evidence for the effect of episodic retrieval on n--2 task repetition costs.
-The conclusion of \cite{Mayr2002} rests on the acceptance of a null hypothesis (i.e., no difference of n--2 task repetition costs), which cannot be achieved via standard null hypothesis significance testing \citep{Gallistel2009, Wagenmakers2007}; however, evidence in favour of a null hypothesis (given some data) can be obtained using Bayes factors \citep[e.g.,][]{Rouder2009}.
-The Bayes factor (denoted $BF_{10}$) quantifies the relative evidence provided by the data in favour of an alternative hypothesis (i.e., n--2 task repetition costs are different for response repetitions and response switches) over a null hypothesis (i.e., n--2 repetition costs are equivalent).
+Although Mayr's (2002) study provides clear evidence against episodic retrieval being the \emph{sole} explanation of n--2 task repetition costs, it is not clear from this study whether episodic retrieval has any modulatory effect on this measure of inhibition.
+Indeed, as Mayr notes in his conclusion, despite the non-significance of the critical interaction, a numerical trend of smaller n--2 task repetition costs for n--2 response repetitions was present in the data.
+However, the lack of a significant interaction cannot be taken as evidence supporting no modulatory effect, as accepting a null hypothesis cannot be achieved via standard null hypothesis significance testing \citep{Gallistel2009, Wagenmakers2007}; however, evidence in favour of a null hypothesis (given some data) can be obtained using Bayes factors \citep[e.g.,][]{Rouder2009}.
+The Bayes factor (denoted $BF_{10}$) quantifies the relative evidence provided by the data in favour of an alternative hypothesis (i.e., n--2 task repetition costs are different for response repetitions and response switches) over a null hypothesis (i.e., n--2 task repetition costs are equivalent).
 
-The Bayes factor for the critical statistical test from Mayr's (2002) study ($BF_{10}$ = 0.315)\footnote{For all Bayes factors reported in this paper we use a non-informative prior on the alternative hypothesis, which is assumed to be distributed as a Cauchy with scaling factor $r$ = 0.707.} suggests that the null hypothesis is about 3 times more likely than the alternative, given the data, which provides anecdotal-to-moderate support for the null \citep[e.g.,][]{Schoenbrodtinpress}.
-As this Bayesian analysis does not provide compelling evidence for the null, and given the importance of assessing to what extent (if any) episodic retrieval can influence n--2 task repetition costs in task switching, we were interested in performing a replication of Mayr's study to gather more evidence.
+The Bayes factor for the critical statistical test from Mayr's (2002) study ($BF_{10}$ = 0.315)\footnote{For all Bayes factors reported in this paper we use a non-informative prior on the alternative hypothesis, which is assumed to be distributed as a Cauchy with scaling factor $r$ = 0.707.} suggests that the null hypothesis is about three times more likely than the alternative, given the data, which provides anecdotal-to-moderate support for the null \citep[e.g.,][]{Schoenbrodtinpress}.
+As this Bayesian analysis does not provide compelling evidence for the null, and given the importance of assessing to what extent (if any) episodic retrieval can influence n--2 task repetition costs in task switching, we were interested in investigating this question further.
 
-The current study replicated critical aspects of Mayr's (2002) design relevant to n--2 task repetitions.
+The purpose of the current study was to re-examine the evidence for the effect of episodic retrieval on n--2 task repetition costs in a series of Experiments.
+In Experiment 1, we report a close replication of Mayr's (2002) design, and find that the n--2 task repetition cost is modulated by episodic retrieval.
+We follow this main finding up in two experiments.
+In Experiment 2, we manipulate the cue--task transparency---that is, ``\emph{...the degree to which the cue exogenously provides or directly stimulates the relevant [working memory] representations}'' \citep[][p.1004]{Grange2009}.
+Non-transparent cues require more processing in working memory to establish the relevant attentional set in comparison to transparent cues which require little or no processing in working memory to establish the relevant attentional set \citep[e.g.,][]{Grange2009, Grange2010, Grange2015a, Houghton2009, Mayr2000a}.
+If the episodic retrieval effect observed in Experiment 1 is caused by interference in working memory establishing a relevant attentional set, then we should observe larger episodic retrieval effects on the n--2 repetition cost under conditions of non-transparent cues; we find strong evidence for such an effect.
+In a final Experiment, we investigate whether the episodic retrieval effect is sensitive to low-level perceptual details---in particular, task-irrelevant aspects of the stimulus display---and find that it is not.
+Together, these results provide evidence that the n--2 repetition cost in task switching---typically described as a ``pure'' measure of cognitive inhibition---is heavily influenced by episodic retrieval effects.
+
+%----------------------
+\section{Experiment 1}
+
+In Experiment 1, we wished to replicate critical aspects of Mayr's (2002) design relevant to n--2 task repetitions.
 As Mayr's study was also interested in exploring to what extent the rule-switching paradigm generated typical task switching effects (such as switch costs, effects of preparation, and effects of the delay between tasks), we made some changes to the original design so that it was more tailored toward assessing n--2 task repetition costs.
@@
 
-%----------------------
-\section{Method}
+\subsection{Method}
 
-\subsection{Participants}
+\subsubsection{Participants}
 All participants were undergraduates at the School of Psychology at Keele University.
@@
 Our final sample comprised 76 participants.
+The stopping rule utilised a Bayesian sequential analysis, which is detailed in Appendix A.
 Three additional participants were removed before analysis due to failure to maintain accuracy levels above 90\%.
 
-Our sample size was determined via optional stopping.
-We used Sequential Bayes Factors \citep{Schoenbrodtinpress} to determine our stopping rule for participant recruitment.
-We were interested in establishing the presence or absence of an interaction between task sequence (ABA vs.
-CBA) and response repetition (repetition vs.
-switch).
-For the purposes of our stopping rule, this can be expressed as a default within-subjects Bayesian \emph{t}-test \citep{Rouder2009} comparing n--2 repetition costs for response repetitions and response switches.
-We conducted a Bayesian \emph{t}-test on the data collected until the criterion for our a priori stopping rule was met.
-Specifically, our stopping rule required at least 20 participants; we continued data collection until $BF_{10}$ > 6 (constituting support for the alternative hypothesis) or $BF_{10}$ < 1/6 (constituting support for the null).
-\cite{Schoenbrodtinpress} demonstrated that a stopping rule of $BF_{10}$ > 6 (or $BF_{10}$ < 1/6) provided the best balance between type 1 and type 2 error, and was their recommended value for studies utilising Sequential Bayes Factors.
-
-\subsection{Apparatus \& Stimuli}
+\subsubsection{Apparatus \& Stimuli}
 Stimuli were presented on a 17in.
@@
 
-\subsection{Procedure}
+\subsubsection{Procedure}
 On each trial a cue was presented above the frame for 150ms.
@@
 The cue for the next trial was chosen randomly with the constraint that task repetitions could not occur (cf., Mayr, 2002); the stimulus location was chosen randomly with no constraints on each trial.
-If participants made an error, the word ``Error!'' appeared in red for 1000ms above the stimulus frame (in the cue's position).
+If participants made an error, the word ``Error!'' appeared in red (same size \& font as cues) for 1000ms above the stimulus frame (in the cue's position).
 
-Participants were presented with 16 trials as practice. The practice block was repeated once if the participant made more than four errors. The main experiment presented 4 blocks of 120 trials.
+Participants were presented with 16 trials as practice. The practice block was repeated once if the participant made more than four errors. The main experiment presented four blocks of 120 trials.
 
-\subsection{Design}
+\subsubsection{Design}
 The experiment manipulated two factors in a fully-related design: \emph{Task Sequence} (n--2 task repetition [ABA] vs.
 n--2 task switch [CBA]) and \emph{Response Repetition} (n--2 response repetition vs.
-n-- response switch).
+n--2 response switch).
 The dependent variables were response time (RT) in milliseconds (ms.) and percent accuracy (\%).
 
-%----------------------
-\section{Results}
+\subsection{Results}
 For response time analysis, the first two trials from each block were removed, as were error trials and the two trials following an error.
+These trials cannot be classified as ABA or CBA sequences.
 Response times were trimmed by removing all RTs faster than 150ms, as well as any RTs slower than 2.5 standard deviations above the mean for each participant for each cell of the experimental design.
-Mean RTs and error rates can be seen in Table \ref{tab:behaviouralData}.
+Mean RTs and error rates can be seen in Table \ref{tab:Experiment1}.
+
+We present our results using standard null hypothesis significance testing (NHST), as well as Bayesian analysis (Bayes factors).
+All analysis was conducted using \texttt{R} statistics \citep{RCore2015}.
+Bayesian analysis utilised the \texttt{BayesFactor} package \citep{Morey2015} and the \texttt{BEST} package \citep{Kruschke2013}.
 
@@
 \centering
-\caption{Response times (RT) in milliseconds (ms) and accuracy (in percent) for ABA and CBA task sequences for response repetitions and response switches.}
-\label{my-label}
+\caption{Response times (RT) in milliseconds (ms) and accuracy (in percent) for ABA and CBA task sequences for response repetitions and response switches in Experiment 1.}
 \begin{tabular}{lccccc}
@@
                     & RT (ms)   & Accuracy (\%) &  & RT (ms)  & Accuracy (\%) \\ \hline
-Response Repetition & 1000 (28) & 96.20 (0.39)  &  & 952 (28) & 96.36 (0.39) \\
-Response Switch     & 1050 (29) & 95.02 (0.35)  &  & 964 (28) & 95.81 (0.34) \\ \hline
+N--2 Response Repetition & 1000 (28) & 96.20 (0.39)  &  & 952 (28) & 96.36 (0.39) \\
+N--2 Response Switch     & 1050 (29) & 95.02 (0.35)  &  & 964 (28) & 95.81 (0.34) \\ \hline
 \end{tabular}
-\label{tab:behaviouralData}
+\label{tab:Experiment1}
 \end{table*}
 
-\subsection{Response Times}
-Response times were analysed via a two factor repeated measures analysis of variance (ANOVA) with the factors as described in \emph{Design}.
-There was a significant main effect of \emph{Sequence}, with slower RTs to ABA sequences (1,025ms) than to CBA sequences (958ms), $F$(1, 75) = 94.14, $p$<.001, $\eta_G^2$ = .018.
-The Bayes factor for this main effect was $BF_{10}$ = 1e+12, which provides substantial support for the presence of n--2 repetition costs.
-There was also a significant main effect of \emph{Response Sequence}, with faster RTs to response repetitions (976ms) than to response switches (1,007ms), $F$(1, 75) = 18.21, $p$<.001, $\eta_G^2$ = .004.
+\subsubsection{Response Times} 
+Response times were analysed via a two factor repeated measures analysis of variance (ANOVA) with the factors \emph{Task Sequence} and \emph{Response Repetition}.
+There was a significant main effect of Task Sequence, with slower RTs to ABA sequences (1,025ms) than to CBA sequences (958ms), $F$(1, 75) = 94.14, $p$<.001, $\eta_G^2$ = .018.
+The Bayes factor for this main effect was $BF_{10}$ = 1e+12, which provides substantial support for the presence of n--2 task repetition costs.
+There was also a significant main effect of Response Repetition, with faster RTs to n--2 response repetitions (976ms) than to n--2 response switches (1,007ms), $F$(1, 75) = 18.21, $p$<.001, $\eta_G^2$ = .004.
 The Bayes factor for this main effect was $BF_{10}$ = 338.77, which again provides substantial support for the alternative hypothesis.
 Critically, there was a significant interaction of both factors, $F$(1, 75) = 9.60, $p$<.01, $\eta_G^2$ = .001.
-The n--2 repetition cost was 48ms for response repetitions [$t$(75) = 4.2, $p$<.001; $BF_{10}$ = 271.24] and 86ms for response switches [$t$(75) = 13.0, $p$<.001; $BF_{10}$ = 7.11e+17].
+The n--2 task repetition cost was 48ms for n--2 response repetitions [$t$(75) = 4.2, $p$<.001; $BF_{10}$ = 271.24] and 86ms for n--2 response switches [$t$(75) = 13.0, $p$<.001; $BF_{10}$ = 7.11e+17].
 
-The progression of the Sequential Bayes Factor for the interaction is shown in Figure \ref{fig:bayesFactor}.
-We stopped data collection after 76 participants, as at this point the criteria for our stopping rule had been reached\footnote{We could have stopped after 75 participants, but the last two participants were tested in successive sessions, so the Bayes factor was not checked until after the final participant.}.
-The final Bayes Factor for the difference of n--2 repetition costs for response repetitions and response switches was $BF_{10}$ = 9.97, which suggests that the alternative hypothesis is about 10 times more likely given than the data, which provides strong support that n--2 repetition costs are influenced by response repetitions.
+\paragraph{Bayesian Analysis}
+
+The final Bayes Factor for the difference of n--2 task repetition costs for n--2 response repetitions and response switches was $BF_{10}$ = 9.97, which suggests that the alternative hypothesis is about 10 times more likely given the data, which provides strong support that n--2 task repetition costs are influenced by n--2 response repetitions.
+Due to the theoretical importance of this finding, we provide more detailed Bayesian analysis and robustness checks in Appendix B.
+
+\subsubsection{Accuracy}
+Accuracy analysis showed no significant effect of Task Sequence [$F$(1, 75) = 3.36, $p$=.07, $\eta_G^2$ = .006]; the Bayes factor for this main effect was $BF_{10}$ = 0.618, which provides only anecdotal support for the null.
+The main effect of Response Repetition was significant [$F$(1, 75) = 12.17, $p$<.001, $\eta_G^2$ = .019], suggestive of better accuracy for n--2 response repetitions (96.28\%) than for response switches (95.41\%).
+The Bayes factor was $BF_{10}$ = 29.66, which provides strong support for the alternative.
+The interaction was not significant [$F$(1, 75) = 1.32, $p$=.25, $\eta_G^2$ = .003]; the Bayes factor was $BF_{10}$ = 0.238, which provides moderate support for the null hypothesis.
+
+%----------------------
+\subsection{Discussion}
+Experiment 1 sought to re-examine the evidence for a modulatory effect of episodic retrieval on n--2 task repetition costs in task switching by replicating key aspects of Mayr's (2002) study.
+In contrast to that study, we found clear evidence of episodic retrieval influencing n--2 task repetition costs in task switching; specifically, n--2 task repetition costs were smaller when the response repeated over an ABA sequence compared to when the response switched.
+This is in line with episodic retrieval facilitating responding when trial parameters match over an ABA sequence (i.e., for n--2 response repetitions).
+This finding questions the common interpretation of the n--2 task repetition cost as a ``pure'' measure of task inhibition \citep{Koch2010, Mayr2007}.
+
+%----------------------
+\section{Experiment 2}
+We wished to follow the findings from Experiment 1 by testing some of the boundary conditions of the effect.
+In particular, we were interested in whether manipulating the cue--task transparency modulated the observed episodic retrieval effect on the n--2 repetition cost.
+Recall that non-transparent cues require more processing in working memory to establish the relevant attentional set in comparison to transparent cues which require little or no processing in working memory to establish the relevant attentional set \citep[e.g.,][]{Grange2009, Grange2010, Grange2015a, Houghton2009, Mayr2000a}.
+In the case of Experiment 1, the word cues are relatively transparent in that the words clearly cue the relevant rule.
+An example of a non-transparent cue would be arbitrary shapes paired with each task (e.g., a square cue for the ``diagonal'' task).
+
+Investigating the effect of cue--task transparency was of interest as there is good evidence that non-transparent cues increase the magnitude of the n--2 task repetition cost relative to transparent cues \citep[e.g.,][]{Gade2014, Grange2009, Grange2010, Houghton2009}.
+Such increases in the n--2 task repetition cost have been interpreted as reflecting an increased need for inhibition.
+For example \cite{Houghton2009} suggested that non-transparent cues require a process of ``translation'' between the cue and the elements of the task-set required; based on \cite{Mayr2000a}, they suggested this translation involves retrieval of task-set elements from long-term memory and their application in working memory.
+During a task switch, newly-retrieved elements will conflict with the still-active elements in working memory from the previous task; this interference is resolved by inhibition.
+Houghton et al.
+hypothesised that transparent cues do not lead to such interference as the cue provides the desired contents of working memory directly, and as such interference from elements active on the previous trial is minimal.
+In several studies, Houghton and colleagues \citep{Grange2009, Grange2010, Houghton2009} found evidence that the n--2 task repetition cost is larger for non-transparent cues, and often absent for highly-transparent cues \citep[but see][for a discussion on interpreting null n--2 task repetition costs]{Grange2013}.
+
+However, given the findings of our Experiment 1, this pattern of data could also be explained under a model of episodic retrieval being influenced by cue transparency, rather than inhibition per se.
+For example, if the larger n--2 task repetition cost under conditions of episodic mismatch from Experiment 1 was occurring due to conflict between the task-set elements retrieved from episodic memory (from n--2) and the current task parameters in working memory, then reducing the need for working memory in establishing the currently-relevant task-set should reduce this interference.
+That is, with highly-transparent cues, the need for working memory processing to establish the relevant attentional set is reduced as the cue provides the necessary elements to perform the task successfully; therefore, the parameters retrieved from episodic memory will not interfere with anything.
+
+Under this hypothesis, the effect of episodic retrieval on the n--2 task repetition cost should be greater under conditions of non-transparent cues.
+If such a pattern is found, it questions the conclusion that reduced cue-transparency increases the need for inhibition; instead, it would suggest that cue-transparency is influencing episodic interference in working memory.
+
+To test this, we performed a conceptual replication of Experiment 1, but changed the nature of the task cue in two (within-subject) conditions (see Figure \ref{fig:cues_Experiment2}): In the ``shape'' cue condition, the cues were non-transparent, having no pre-experimental association with the task rules, for example a square cue indicating the ``diagonal'' judgment.
+In contrast, the ``arrow'' cues condition, the cue provides a direct sample of the response rules relevant for the current trial.
+For example, the ``vertical'' judgment is cued by two up--down arrows.
+We predicted that the effect of episodic retrieval on the n--2 task repetition cost would be greater for the Shape cues compared to the Arrow cues.
+
+\subsection{Method}
+\subsubsection{Participants}
+The stopping rule for Experiment 2 is detailed in Appendix A.
+All participants were from the same pool as Experiment 1, receiving the same compensation.
+None had taken part in Experiment 1.
+Our final sample consisted of 66 participants.
+
+\subsubsection{Apparatus \& Stimuli}
+The apparatus was identical to Experiment 1.
+The stimulus frame and stimulus object was identical to Experiment 1, but we did not use the word cues.
+Instead, participants were presented with ``arrow'' cues in one half of the experiment, and ``shape'' cues in the other half.
+The cues were presented in the centre of the stimulus frame.
+The cues are shown in Figure \ref{fig:cues_Experiment2}.
+For the shape cues, a hexagon cued the vertical judgement, a triangle cued the horizontal judgement, and a square cued the diagonal judgement.
+The arrow cues visually dictated the response rule: vertical arrows cued the vertical judgement, horizontal arrows cued the horizontal judgement, and diagonal arrows cued the diagonal judgement.
+All cues were 2.5cm in width and height.
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width = \textwidth]{Images/experiment_2_cues.png}
+\caption{Cues from Experiment 2 for each of the three judgements (vertical, horizontal, and diagonal).}
+\label{fig:cues_Experiment2}
+\end{center}
+\end{figure*}
+
+\subsubsection{Procedure}
+The Experiment was in two halves, with different cue-types presented in each half.
+Order of cue presentation in each half was counterbalanced across participants.
+For each half, participants learned the cue--task pairings, and were presented with a practice session consisting of 16 trials, which was repeated once if the participant made than four errors.
+The experimental section of each half consisted of three blocks of 120 trials.
+The trial procedure and response requirements were the same as Experiment 1.
+
+\subsubsection{Design}
+The experiment manipulated three factors in a fully-related design: \emph{Cue-Type} (arrow cues vs.
+shape cues), \emph{Task Sequence} (n--2 task repetition [ABA] vs.
+n--2 task switch [CBA]) and \emph{Response Repetition} (n--2 response repetition vs.
+n--2 response switch).
+The dependent variables were response time (RT) in milliseconds (ms.) and percent accuracy (\%).
+
+\subsection{Results}
+The data trimming was identical to Experiment 1. Mean RTs and errors are presented in Table \ref{tab:Experiment2}.
+
+\subsubsection{Response Times}
+Response times\footnote{All of the response time analysis was re-analysed using log(RT) as the dependent variable, which produced qualitatively similar results.
+This transformation was analysed as there was a large discrepancy in mean response time for arrow cues and shape cues, and as such, interaction effects could have been artificially amplified.} were analysed via a three factor repeated measures ANOVA with the factors \emph{Cue-Type, Task Sequence} and \emph{Response Repetition}.
+There was a significant main effect of Cue-Type, with faster RTs to arrow cues (720ms) than to shape cues (1067ms), $F$(1, 65) = 247.98, $p$<.001, $\eta_G^2$ = .42.
+There was also a main effect of Task Sequence, with slower RTs to ABA sequences (916ms) than to CBA sequences (871ms), $F$(1, 65) = 61.75, $p$<.001, $\eta_G^2$ = .012.
+There was also a main effect of Response Repetition, with faster RTs to response repetitions (878ms) than to response switches (909ms), $F$(1, 65) = 24.53, $p$<.001, $\eta_G^2$ = .006.
+
+\begin{table*}[htbp]
+\centering
+\caption{Response times (RT) in milliseconds (ms) and accuracy (in percent) for ABA and CBA task sequences for response repetitions and response switches for both cue types in Experiment 2.}
+\begin{tabular}{lllllll}
+\hline
+         &                          & \multicolumn{5}{c}{Task Sequence}                        \\ \cline{3-7}
+
+         &                          & \multicolumn{2}{c}{ABA}   &  & \multicolumn{2}{c}{CBA}   \\\cline{3-4}
+\cline{6-7}
+
+Cue Type &                          & RT (ms)   & Accuracy (\%) &  & RT (ms)   & Accuracy (\%) \\ \hline
+Arrows   & N--2 Response Repetition & 722 (22)  & 98.05 (0.29)  &  & 709 (20)  & 96.64 (0.40)  \\
+         & N--2 Response Switch     & 739 (20)  & 96.36 (0.32)  &  & 709 (20)  & 97.49 (0.22)  \\
+         &                          &           &               &  &           &               \\
+Shapes   & N--2 Response Repetition & 1053 (29) & 96.90 (0.40)  &  & 1027 (30) & 95.75 (0.49)  \\
+         & N--2 Response Switch     & 1148 (29) & 94.20 (0.47)  &  & 1039 (30) & 96.66 (0.30) \\
+\hline
+\end{tabular}
+\label{tab:Experiment2}
+\end{table*}
+
+Replicating previous work (Grange \& Houghton, 2009, 2010; Houghton et al., 2009), there was a significant interaction of Cue-Type and Task Sequence [$F$(1, 65) = 15.85, $p$<.001, $\eta_G^2$ = .003], with smaller n--2 task repetition costs for the more ``transparent'' arrow cues (22ms) than for the more ``non-transparent'' shape cues (68ms).
+Cue-Type also interacted with Response Repetition [$F$(1, 65) = 16.07, $p$<.001, $\eta_G^2$ = .003]: The difference of slower RTs for response switches compared to response repetitions was smaller for arrow cues (8ms) than for the shape cues (53ms).
+
+Replicating Experiment 1, we also found a significant interaction of Task Sequence and Response Repetition [$F$(1, 65) = 14.87, $p$<.001, $\eta_G^2$ = .004.]: n--2 repetition costs were smaller for response repetitions (20ms) than for response switches (70ms).
+This replication provides converging evidence that the n--2 task repetition cost is reduced under conditions of an episodic match from n--2.
+
+Pertinent to the current Experiment's aims, we also found a significant interaction between all three factors, $F$(1, 65) = 8.88, $p$<.01, $\eta_G^2$ = .002.
+This suggests that the difference in n--2 task repetition cost for response repetitions and response switches varied between Cue-Type.
+This three-way interaction is depicted in the upper panel of Figure \ref{fig:Experiment2}.
+A simplified depiction of this interaction is depicted in the lower panel of Figure \ref{fig:Experiment2}, where we plot the n--2 task repetition cost as the dependent variable.
+As is clear, the difference between the n--2 task repetition cost for response repetitions and response switches was larger for the non-transparent shape cues.
+That is, episodic retrieval appeared to have a larger modulatory effect for the shape cues, as predicted.
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width = \textwidth]{Images/all_rts_Experiment2.pdf}
+\caption{Data from Experiment 2.
+The upper panel depicts the three-way interaction of Cue-Type (arrows vs.
+shapes), Task Sequence, and Response Repetition for mean response time (in milliseconds, ms).
+The lower panel depicts the same data expressed with N--2 task repetition costs as the dependent variable, for both cue types as a function of response repetition and response switch from n--2 to n.
+Error bars denote +/- 1 standard error around the mean.}
+\label{fig:Experiment2}
+\end{center}
+\end{figure*}
+
+\paragraph{Bayesian Analysis}
+See Appendix A for details of the Bayesian model comparison process.
+We modelled the data in the lower portion of Figure \ref{fig:Experiment2}, with n--2 task repetition cost as the dependent variable.
+The ``full'' model---i.e., two main effects (Cue-Type and Response Repetition) plus their interaction---had a Bayes factor of 1,236,317.
+The next-best model was the model with two main effects---Cue-Type and Response Repetition---with a Bayes factor of 156,707.
+Thus, the $BF_{10}$ for the full interaction model was 1,236,317 / 156,707 = 7.89, suggesting the evidence in support of the interaction of Cue-Type and Response Repetition is about 8 times greater than the next-best model.
+This provides moderate support for this model.
+Thus, the NHST and Bayesian analysis both support the conclusion that the episodic retrieval effect on the n--2 task repetition cost is greater for non-transparent cues, as predicted.
+
+\subsubsection{Accuracy}
+For the accuracy data, there was a significant main effect of Cue-Type, with more accurate responses to arrow cues (97.13\%) compared to shape cues (95.88\%), $F$(1, 65) = 16.57, $p$<.001, $\eta_G^2$ = .042.
+The main effect of Task Sequence was not significant, $F$(1, 65) = 1.38, $p$=.244, $\eta_G^2$ = .002.
+There was a main effect of Response Repetition, with more correct responses to response repetitions (96.84\%) compared to response switches (96.18\%), $F$(1, 65) = 12.81, $p$<.001, $\eta_G^2$ = .012.
+
+The interaction of Cue-Type and Task Sequence was not significant, $F$(1, 65) = 3.79, $p$=.056, $\eta_G^2$ = .004, nor was the interaction of Cue-Type and Response Repetition, $F$(1, 65) = 1.33, $p$=.254, $\eta_G^2$ = .002.
+There was a significant interaction between Task Sequence and Response Repetition, $F$(1, 65) = 51.99, $p$<.001, $\eta_G^2$ = .061, indicative of different n--2 task repetition costs for response repetitions and response switches.
+The n--2 task repetition cost---calculated as $\%Accuracy_{ABA}$ -- $\%Accuracy_{CBA}$---for response switches was --1.79\%, but there was an n--2 task repetition \emph{benefit} of 1.28\% for response repetitions.
+The three way interaction was not significant, $F$(1, 65) = 1.69, $p$=.199, $\eta_G^2$ = .002.
+
+\subsection{Discussion}
+Experiment 2 replicated the finding from Experiment 1 of increased n--2 task repetition costs under conditions of n--2 response switches (i.e., episodic mismatches).
+In addition, this effect was larger when the cue--task relationship was relatively non-transparent (i.e., the Shape cues).
+We suggest that the transparent Arrow cues minimise the role of working memory in establishing the relevant attentional set, and as such, elements retrieved from episodic memory interfere less with ongoing processing.
+This finding localises the episodic retrievel effect on n--2 task repetition costs to interference during establishing the relevant attentional set for current task performance.
+
+The current finding also has implications for previous work suggesting that cue--task transparency influences the degree of inhibition deployed during task switching \citep{Grange2009, Grange2010, Grange2015a, Houghton2009}.
+Cue--task transparency in Experiment 2 only appeared to influence the n--2 task repetition cost under conditions of n--2 response switches; cue--task transparency had little influence on the n--2 task repetition cost under conditions of n--2 response repetitions.
+If we assume the latter condition is a better measure of ``pure'' inhibition---in the sense that the n--2 task repetition cost here is not influenced by episodic retrieval---we can see that cue--task transparency is not having a large effect on inhibition.
+We return to the implications of this finding in the General Discussion.
+
+%----------------------
+\section{Experiment 3}
+In the final Experiment, we wished to understand whether the observed episodic retrieval effect in Experiments 1 and 2 was sensitive to low-level perceptual details of the stimulus display.
+In Experiments 1 and 2, the identity of the stimulus was always task-irrelevant; what was relevant was the location of the stimulus.
+Therefore, we were interested in whether the facilitatory performance we find for n--2 task repetition costs under conditions of n--2 response repetitions was due to low-level perceptual matching of the stimulus identity between the episodic trace retrieved and the current stimulus display, or a matching between more ``high-level'' representations, such as the stimulus location and the response required.
+Finding that the episodic retrieval effect is not sensitive to low-level, task-irrelevant, perceptual properties of the task would suggest that what is being retrieved from episodic memory during task switching are exclusively task-relevant elements of task performance.
+
+To this end, we designed an experiment which varied the novelty of the task-relevant stimulus on each trial.
+The paradigm was very similar to the ``Shape'' condition of Experiment 2, but the stimulus was always a letter.
+In the ``Match'' condition, the stimulus was always the letter ``A''; thus, there is always a perceptual match of the stimulus identity between n--2 and n.
+In the ``Mismatch'' condition, the stimulus was randomly drawn from the set ``A--Z''; thus, in this condition, the probability of a perceptual match of the stimulus identity between n--2 and n is drastically reduced.
+
+If the episodic retrieval effect observed thus far is sensitive to low-level, task-irrelevant, properties of the stimulus display, we should find a larger episodic facilitatory effect in the Match condition, as this is the only condition where such details match across n--2 to n.
+If, however, the effect is due to retrieval of task-relevant, ``high-level'' representations---such as stimulus location and the response executed---we should find similar effects of episodic retrieval in both conditions.
+
+\subsection{Method}
+\subsubsection{Participants}
+The stopping rule for Experiment 3 is detailed in Appendix A.
+All participants were from the same pool as Experiments 1 and 2, receiving the same compensation.
+None had taken part in either of these Experiments.
+Our final sample consisted of 25 participants.
+
+\subsubsection{Apparatus \& Stimuli}
+The apparatus was identical to Experiments 1 and 2.
+The stimulus frame was also identical to Experiment 1, but different stimuli were used.
+Instead of circles, letters served as stimuli, presented in Verdana font approximately 1cm in height and width.
+In one condition---the \emph{Match} condition---the stimulus was always the letter ``A''.
+In the other condition---the \emph{Mismatch} condition---the stimulus was selected from the letters A--Z.
+The cues were the shape cues used from Experiment 2, and were presented in the centre of the stimulus frame.
+A hexagon cued the vertical judgment, a triangle cued the horizontal judgment, and a square cued the diagonal judgment.
+All cues were 2.5cm in width and height.
+
+\subsubsection{Procedure}
+The Experiment was in two halves, with different stimulus conditions presented in each half.
+In the Match condition, the same letter was presented as the stimulus on all trials (the letter ``A'' for all participants).
+In the Mismatch condition, the stimulus was randomly selected (with replacement) from the set A--Z.
+Participants were informed that the identity of the stimulus was always irrelevant, and that they were to always respond based on the current task and the location of the stimulus.
+
+The ordering of stimulus condition was counterbalanced across participants.
+Participants were presented with a practice session in both halves, consisting of 16 trials which was repeated once if the participant made than four errors.
+The experimental section of each half consisted of three blocks of 120 trials.
+The trial procedure and response requirements were the same as Experiment 1.
+
+\subsubsection{Design}
+The experiment manipulated three factors in a fully-related design: \emph{Stimulus Condition} (match vs.
+mismatch), \emph{Task Sequence} (n--2 task repetition [ABA] vs.
+n--2 task switch [CBA]) and \emph{Response Repetition} (n--2 response repetition vs.
+n--2 response switch).
+The dependent variables were response time (RT) in milliseconds (ms.) and percent accuracy (\%).
+
+\subsection{Results}
+The data trimming was identical to Experiments 1 and 2, with the exception that trials in the Mismatch condition in which a stimulus repeated from the previous trial or from the trial at n--2 were removed.
+Mean RTs and errors are presented in Table \ref{tab:Experiment3}.
+
+\begin{table*}[htbp]
+\centering
+\caption{Response times (RT) in milliseconds (ms) and accuracy (in percent) for ABA and CBA task sequences for response repetitions and response switches for both cue types in Experiment 3.}
+\begin{tabular}{lllllll}
+\hline
+         &                          & \multicolumn{5}{c}{Task Sequence}                        \\ \cline{3-7}
+
+         &                          & \multicolumn{2}{c}{ABA}   &  & \multicolumn{2}{c}{CBA}   \\\cline{3-4}
+\cline{6-7}
+
+Stimulus &                          & RT (ms)   & Accuracy (\%) &  & RT (ms)   & Accuracy (\%) \\ \hline
+Match   & N--2 Response Repetition & 1074 (51) & 96.99 (0.88)  &  & 1042 (51)  & 97.55 (0.49)  \\
+         & N--2 Response Switch     & 1124 (51)  & 96.60 (0.42)  &  & 1038 (49)  & 97.86 (0.56)  \\
+         &                          &           &               &  &           &               \\
+Mismatch   & N--2 Response Repetition & 1075 (50) & 95.63 (0.69)  &  & 1047 (56) & 97.62 (0.72)  \\
+         & N--2 Response Switch     & 1131 (49) & 95.47 (0.69)  &  & 1002 (45) & 97.06 (0.38) \\
+\hline
+\end{tabular}
+\label{tab:Experiment3}
+\end{table*}
+
+\subsubsection{Response Times}
+Response times were analysed via a three factor repeated measures ANOVA with the factors \emph{Stimulus Condition}, \emph{Task Sequence}, and \emph{Response Repetition}.
+The main effect of Stimulus Condition was not significant, $F$(1, 24) = 0.01, $p$ = .924, $\eta_G^2$ < .001.
+There was a main effect of Task Sequence, with slower RTs to ABA sequences (1101ms) than to CBA sequences (1032ms), $F$(1, 24) = 35.74, $p$ < .001, $\eta_G^2$ = .019.
+The main effect of Response Repetition was not significant, $F$(1, 24) = 1.20, $p$ = .283, $\eta_G^2$ < .001.
+
+Stimulus Condition did not interact with Task Sequence [$F$(1, 24) = 0.87, $p$ = .362, $\eta_G^2$ < .001] or Response Repetition [$F$(1, 24) = 0.66, $p$ = .426, $\eta_G^2$ < .001].
+Replicating the first two Experiments, Task Sequence interacted with Response Repetition, $F$(1, 24) = 17.04, $p$ < .001, $\eta_G^2$ = .006: n--2 task repetition costs were smaller for response repetitions (29ms) than for response switches (108ms).
+This provides converging evidence that the n--2 repetition cost is reduced under conditions of an episodic match from n--2.
+
+Importantly for the current study, the three-way interaction was not significant, $F$(1, 24) = 1.07, $p$ = .311, $\eta_G^2$ < .001.
+This three-way interaction is depicted in the upper panel of Figure \ref{fig:Experiment3}.
+A simplified depiction of this interaction is depicted in the lower panel of Figure \ref{fig:Experiment3}, where we plot the n--2 task repetition cost as the dependent variable.
+There is no clear variation of the episodic-retrieval effect on n--2 task repetition costs under conditions of stimulus matching or mismatching.
+
+\paragraph{Bayesian Analysis}
+See Appendix A for details of the Bayesian model comparison process.
+We modelled the data in the lower portion of Figure \ref{fig:Experiment3}, with n--2 task repetition cost as the dependent variable.
+The ``full'' model---i.e., two main effects (Stimulus Condition and Response Repetition) plus their interaction---had a Bayes factor of 24.17.
+The best model was the model with Response Repetition as the only main effect, with a Bayes factor of 151.10.
+Thus, the $BF_{10}$ for the full interaction model was 24.17 / 151.10 = 0.16, suggesting the evidence against the interaction of Stimulus Condition and Response Repetition is about 6.25, which constitutes moderate evidence against this model.
+Thus, the NHST and Bayesian analysis both support the conclusion that, whilst the n--2 task repetition cost is modulated by episodic retrieval, the effect is similar for both Stimulus Conditions.
+
+\subsubsection{Accuracy}
+For the accuracy data, there was no significant main effect of Stimulus Condition, $F$(1, 24) = 2.46, $p$ = .130, $\eta_G^2$ = .017.
+There was a significant main effect of Task Sequence, with less accurate response to ABA sequences (96.17\%) than to CBA sequences (97.52\%), $F$(1, 24) = 14.64, $p$ < .001, $\eta_G^2$ = .046.
+The main effect of Response Repetition was not significant, $F$(1, 24) = 0.58, $p$ = .452, $\eta_G^2$ = .001.
+
+None of the interactions were significant: Stimulus Condition by Task Sequence, $F$(1, 24) = 1.33, $p$ = .260, $\eta_G^2$ = .005; Stimulus Condition by Response Repetition, $F$(1, 24) = 0.23, $p$ = .638, $\eta_G^2$ < .001; Task Sequence by Response Repetition, $F$(1, 24) = 0.05, $p$ = .821, $\eta_G^2$ < .001.
+The three-way interaction was also not significant, $F$(1, 24) = 0.62, $p$ = .438, $\eta_G^2$ = .002.
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width = \textwidth]{Images/all_rts_Experiment3.pdf}
+\caption{Data from Experiment 3.
+The upper panel depicts the three-way interaction of Stimulus Condition (match vs.
+mismatch), Task Sequence, and Response Repetition for mean response time (in milliseconds, ms).
+The lower panel depicts the same data expressed with N--2 task repetition costs as the dependent variable, for both Stimulus Conditions as a function of response repetition and response switch from n--2 to n.
+Error bars denote +/- 1 standard error around the mean.}
+\label{fig:Experiment3}
+\end{center}
+\end{figure*}
+
+\subsection{Discussion}
+We were interested in whether the effect of episodic retrieval on the n--2 task repetition cost was due to low-level perceptual details of the stimulus display.
+The results support the conclusion that it is not: The effect of episodic retrieval on the n--2 task repetition cost was similar under conditions of stimulus matching and stimulus mismatching from n--2 to n.
+These results suggest that the episodic retrieval effect observed in all three experiments can be localised to the retrieval of ``high-level'', task-relevant representations, such as the stimulus location and the response executed.
+
+%----------------------
+\section{General Discussion}
+The current study was interested in re-investigating whether---and to what extent---episodic retrieval affects the n--2 task repetition cost, an effect typically ascribed to a ``pure'' measure of task inhibition \citep{Gade2014, Koch2010, Mayr2007}.
+Across three experiments, we find consistent evidence that the n--2 task repetition cost is increased when there is a mismatch between task-relevant elements from episodic memory of the task from n--2 and the task demands on the current trial.
+When the trace from n--2 that is retrieved from episodic memory matches the current task demands, the n--2 task repetition cost is significantly reduced.
+Experiment 2 demonstrated that the effect is larger for less-transparent cue--task relationships, which we suggest provides evidence that localises the episodic retrieval effect to interference during establishing the relevant attentional set in working memory.
+In Experiment 3 we demonstrated that the effect is not influenced by low-level perceptual properties being retrieved from episodic memory.
+Rather, the effect appears to be localised to higher-level representations regarding task-relevant stimulus properties and response execution.
+
+Together, our data suggests that episodic retrieval strongly modulates the n--2 task repetition cost.
+Therefore, we suggest that the n--2 task repetition cost---as typically measured---is at least a contaminated measure, and should be used with caution.
+Not controlling for episodic retrieval will bias the estimates of n--2 task repetition costs.
+
+\subsection{Practical Implications}
+This finding has significant practical implications, as the n--2 task repetition cost has garnered much interest with researchers interested in using the n--2 task repetition cost as a measure of inhibitory control.
+For example, \cite{Whitmer2007} used the n--2 task repetition cost as a measure of inhibition to assess to what extent depressive rumination is associated with deficient inhibitory control, finding a negative correlation between n--2 task repetition costs and rumination tendencies; from this, the authors concluded that rumination is associated with deficits in cognitive inhibition \citep[see also][]{Whitmer2012}.
+The n--2 task repetition cost has also been used to assess the effects of brain lesions on cognitive inhibition \citep{Mayr2006}, the effect of Parkinson's \citep{Fales2006}, healthy ageing \citep{Lawo2012}, obsessive-compulsive disorder \citep{Moritz2004}, bilingualism \citep{Prior2012}, and others.
+Our findings would suggest that the results of such studies need reconsideration, as episodic retrieval was not controlled.
+Therefore, the measures of the n--2 task repetition cost are likely confounded.
+
+Recently, we have reported that the split--half reliability of individual differences in the n--2 task repetition cost is low, by assessing performance on three paradigms typically used in assessing the n--2 task repetition cost \citep{Kowalczykinpress}.
+This finding is consistent with the notion that the n--2 task repetition cost is not a stable measure of inhibition at the individual difference level, but it is also expected if the n--2 task repetition cost arises due to a mixture of factors (i.e., inhibition plus episodic interference).
+As episodic retrieval was not controlled in the paradigms used by \cite{Kowalczykinpress}---as is typical in this line of research---one possibility is that the low reliability was caused by the contamination episodic interference brings to the measure.
+Current work in our lab is assessing whether reliability of the n--2 task repetition cost improves when episodic retrieval is controlled.
+
+\subsection{Theoretical Implications}
+There are also theoretical implications of these findings.
+There is growing evidence that episodic retrieval plays a role in explaining several task switching effects \citep[e.g.,][for a model of task switching based on episodic retrieval]{Altmann2008}.
+For example, \cite{Altmann2011} provided empirical and theoretical evidence that episodic retrieval can explain the n--1 response-repetition effect in task switching, the observation that task repetition RTs are facilitated when the required response repeats from trial n--1 to the current trial, yet n--1 response repetitions produce a cost for task switches.
+\cite{Horoufchin2011a} \citep[see also][]{Horoufchin2011} also provided evidence that episodic retrieval can explain the reduction of the task switch cost at longer RCIs \citep[e.g.,][]{Meiran2000a}; the standard explanation for this finding pertains to the decay of task representations in memory slowing task repetition RTs.
+However, \cite{Horoufchin2011a} provided compelling evidence that this pattern of data can be better explained with reference to an episodic retrieval account: trial-wise variation of the RCI affects the \emph{temporal distinctiveness} of task traces in episodic memory, thus influencing their retrieval probability \citep{Brown2007, Grange2015, Grange2016}.
+The current work extends this evidence of the role of episodic retrieval influencing task switching effects.
+As such, theoretical accounts of inhibitory control during task switching will have to take into account the role of episodic retrieval.
+
+As the n--2 task repetition cost has been thought to measure a pure inhibitory mechanism, previous research which has shown a modulation of the n--2 task repetition cost due to some experimental manipulation has been interpreted in terms of the manipulation having an effect on inhibition.
+For example, \cite{Schuch2003} found that the n--2 task repetition cost is absent if the task at n--1 did not require a response (i.e., a no-go trial).
+This evidence was used to suggest that inhibition of competing tasks occurs at the response-selection level.
+Other work has found effects of the cue-type \citep{Arbuthnott2005, Grange2009, Grange2010, Houghton2009}, response--related processes \citep{Philipp2007, Schneider2008}, stimulus-related processes \citep{Sdoia2008}, RCI effects \citep{Gade2005}, and practice effects \citep{Grange2015a, Scheil2016}, among others \citep{Koch2010}.
+As such, it would be prudent to re-visit these findings and assess to what extent the experimental manipulations were influencing episodic retrieval rather than inhibition.
+
+For example, the current work has implications for our previous line of research focussing on the effects of cue--transparency on the n--2 task repetition cost \citep{Grange2009, Grange2010, Grange2015a, Houghton2009}.
+Our previous work has shown consistently that reducing the transparency of the cue--task relationship increases the n--2 task repetition cost.
+However, Experiment 2 of the current study provided evidence that the cue--task transparency manipulation was influencing episodic retrieval effects, not inhibition (i.e., cue--task transparency only influenced n--2 response switch trials).
+Thus, it is possible that our previous findings are attributable to episodic retrieval effects, rather than inhibition.
+Further work is needed to establish to what extent cue--task transparency influences episodic retrieval rather than inhibition.
+
+\subsubsection{Analagous Effects in Declarative Working Memory}
+During the final preparation of this paper, we became aware of a paper investigating an analogous effect to the n--2 task repetition cost within a working memory framework.
+\cite{Gadeinpress} presented participants with three lists of items (e.g., numbers: List A = ``6, 5, 1'', List B = ``2, 7, 4'', list C = ``7, 4, 8'') that had to be retained in working memory; participants had to then switch between these lists, and perform operations on an item contained within the list (e.g., mental arithmetic, Experiments 5--8).
+The researchers found evidence for an n--2 \emph{list} repetition cost---analogous to the n--2 task repetition cost--- suggesting that switching between memory sets requires the inhibition of recently-activated memory sets, but only when there was a high degree of competition between memory sets.
+
+\cite{Gadeinpress} assessed whether this n--2 list repetition cost could be explained by episodic interference.
+Specifically, on n--2 list repetitions, it is possible that participants retrieve from episodic memory a trace of performance parameters (e.g., the item that was acted upon, the operation required, and the response executed).
+This retrieval could prime performance when parameters on the current trial match elements of this trace (e.g., the same item requires action), and could lead to interference when the elements mismatch, much like our current study.
+Controlling for this episodic retrieval in their paradigm, \cite{Gadeinpress} reported no significant variance of the n--2 list repetition cost attributable to inhibition.
+
+This finding led \cite{Gadeinpress} to investigate whether the n--2 \emph{task} repetition cost in eight of their lab's published and unpublished experiments could be attributable to episodic interference by controlling for stimulus (and hence, response) repetitions across an ABA sequence.
+They found that there was no n--2 task repetition cost when controlling for episodic retrieval, suggesting episodic retrieval significantly contributes to this measure.
+However, it is important to note that of the eight experiments re-analysed by Gade and colleagues, only two showed significant n--2 task repetition costs before controlling for episodic retrieval.
+Thus it is unclear how to interpret the absence of an n--2 task repetition cost when controlling for episodic retrieval in the six experiments where the cost was not present initially.
+
+However, the findings of \cite{Gadeinpress} certainly compliment the current findings.
+In our study, there were significant n--2 task repetition costs in all three experiments, and we consistently show that this effect is modulated by episodic retrieval.
+Thus, together, our results provide converging evidence that questions the common interpretation of the n--2 task repetition cost that it is attributable exclusively to inhibition.
+
+\subsection{Any Role for Inhibition?}
+It is important to assess whether there is any role for inhibition once controlling for episodic retrieval.
+That is, are there consistent n--2 task repetition costs for n--2 response repetitions?
+To assess this, we performed a mini meta-analysis of the n--2 task repetition cost for response repetitions using the ESCI software \citep{Cumming2012} using a mixed-effects model\footnote{We used a mixed-effects model to be conservative, despite the similarity of the paradigms across all three experiments.
+However, heterogeneity of data between experiments and conditions was low ($Q$ = 7.10, $df$ = 4, $p$ = .13, $I^{2}$ = 43.67\%); thus, a fixed-effects model would produce quantitatively similar results.}.
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width = \textwidth]{Images/meta_analysis.pdf}
+\caption{Forest plot of the meta-analysis of n--2 task repetition cost for response repetitions across all experiments.
+The boxes represent the mean n--2 task repetition cost for each condition, together with their 95\% confidence intervals.
+The size of each box is proportional to that condition's weight in the meta-analysis.
+The meta-analysis estimate of the n--2 repetition cost is shown at the bottom.
+Forest plot created using the \texttt{forestplot} R package \citep{Gordon2016}.}
+\label{fig:meta_analysis}
+\end{center}
+\end{figure*}
+
+The result of this meta analysis is shown in Figure \ref{fig:meta_analysis}; the meta-analysis estimate of the n--2 task repetition cost for response repetitions is 28ms, 95\% confidence interval = [11--46ms].
+Thus, the evidence across all of our data suggests that there is a small n--2 task repetition cost when controlling for episodic retrieval.
+As this cost cannot be contaminated by episodic interference from n--2, it is plausible that this estimate is attributable to inhibition.
+Our data therefore have not provided evidence that episodic retrieval can explain the n--2 task repetition cost entirely, but rather that it reduces the cost considerably.
+
+\subsection{Conclusion}
+In conclusion, our results demonstrate clear effects of episodic interference in generating n--2 task repetition costs, which must be controlled if researchers wish to use this cost as a measure of cognitive inhibition.
+
+\newpage
+%%%--------------------------------------------------------------------------------------------
+\appendix
+\section{Details of Stopping Rules}
+In this section we outline the stopping rules for all three experiments.
+
+\subsection{Experiment 1}
+Our sample size for Experiment 1 was determined via optional stopping, utilising Sequential Bayes Factors \citep{Schoenbrodtinpress} to determine our stopping rule for participant recruitment.
+We were interested in establishing the presence or absence of an interaction between Task Sequence (ABA vs.
+CBA) and Response Repetition (repetition vs.
+switch).
+For the purposes of our stopping rule, this can be expressed as a default within-subjects Bayesian \emph{t}-test \citep{Rouder2009} comparing n--2 task repetition costs for response repetitions and response switches.
+We conducted a Bayesian \emph{t}-test on the data collected until the criterion for our a priori stopping rule was met.
+Specifically, our stopping rule required at least 20 participants; we continued data collection until $BF_{10}$ > 6 (constituting support for the alternative hypothesis) or $BF_{10}$ < 1/6 (constituting support for the null).
+\cite{Schoenbrodtinpress} demonstrated that a stopping rule of $BF_{10}$ > 6 (or $BF_{10}$ < 1/6) provided the best balance between type 1 and type 2 error, and was their recommended value for studies utilising Sequential Bayes Factors.
+
+\subsection{Experiment 2}
+\subsubsection{Overview of Bayesian analysis of factorial designs}
+Experiment 2 again utilised Sequential Bayesian Analysis, but unlike Experiment 1's Bayesian t-test, Experiment 2 utilised Bayesian analysis of factorial designs, outlined by \cite{Rouderinpress} and \cite{Morey2015}.
+Bayesian analysis of factorial designs generally works by constructing permutations of model comparisons, where the models differ in their inclusion of main effect terms and their interaction.
+For example, one model might model the data as a main effect of Factor A and a main effect of Factor B, whereas a second model might model the data as a main effect of Factors A and B, as well as their interaction.
+A Bayes factor is obtained for each model, and the relative evidence for a model comparison is the ratio of their Bayes factors.
+The result is itself a Bayes factor, which can be used to provide evidence for the degree of support for one model compared to another.
+
+Bayesian analysis for multi-factorial designs can produce hundreds if not thousands of model comparisons \citep[see][]{Rouderinpress}; for example, a 4-factor design has 32,767 model comparisons.
+Experiment 2 has three factors, so to reduce the number of model comparisons being made we used the n--2 repetition cost as our dependent variable (which removes one factor---Task Sequence---from the design).
+Thus, the Bayesian factorial analysis had two manipulated factors: Cue-Type and Response Repetition.
+Participants were entered as a random effect.
+The Bayes factor for all models was a comparison against a denominator of the n--2 repetition cost predicted by the random effect of participants.
+
+\subsubsection{Stopping rule}
+The main model of interest is the model with all main effects and the interaction (i.e., n--2 repetition cost predicted from Cue-Type, Response Repetition, and Cue-Type * Response Repetition interaction).
+Our stopping rule involved taking the ratio of the Bayes factor for this ``full'' model with the Bayes factor of the next-best model, if the full model had the highest Bayes factor (i.e., if the full model was the best fit, we wished to quantify how much better it is than its nearest competitor).
+If the full model did not have the highest Bayes factor, we took the ratio of the Bayes factor for the full model with the model with the highest Bayes factor (i.e., if the full model was not the best fit, we wished to quantify how much worse it is than the best model).
+
+Like Experiment 1, our stopping rule required at least 20 participants, and we used a $BF_{10}$ > 6 or $BF_{10}$ < 1/6 as our criterion for stopping data collection.
+
+\subsection{Experiment 3}
+The stopping rule for Experiment 3 was identical to Experiment 2; the factors for this Experiment were Stimulus Condition and Response Repetition; n--2 repetition cost again served as the dependent variable.
+
+%%%--------------------------------------------------------------------------------------------
+\appendix
+\section{Supplemental Bayesian Analysis for Experiment 1}
+
+\subsection{Visualisation of Sequential Bayesian Analysis} 
+The progression of the Bayes Factor for the interaction of Task Sequence and Response Repetition---updated as participants were recruited (see Appendix A for the general procedure)---is shown in Figure \ref{fig:bayesFactor}.
+We stopped data collection after 76 participants, as at this point the criteria for our stopping rule had been reached.
+We could have stopped after 75 participants, but the last two participants were tested in successive sessions, so the Bayes factor was not checked until after the final participant.
 
@@
 \includegraphics[width = \textwidth]{Images/bayesFactor.pdf}
-\caption{Progression of the Sequential Bayes Factor [expressed as log($BF_{10}$)] as sample size increased. The criteria for a priori stopping rules are shown as dotted horizontal lines.}
+\caption{Progression of the Sequential Bayes Factor [expressed as log($BF_{10}$)] as sample size increased in Experiment 1.
+The criteria for a priori stopping rules are shown as dotted horizontal lines.}
 \label{fig:bayesFactor}
@@
 
-\subsubsection{Robustness Check on Bayesian Priors}
-We used a default prior distribution on the effect size for the alternative hypothesis in the Bayes factor analysis, which was assumed to be distributed as a Cauchy distribution with scale parameter $r$ = 0.707.
-To examine how robust our findings were to the choice of prior, we conducted a robustness check by re-calculating the Bayes factor across a wide range of priors by varying scale parameter $r$: As $r$ increases, the prior distribution becomes wider, reflecting a prior for larger effects; $r$s closer to zero make the distribution narrower, reflecting a prior for smaller effects.
+\subsection{Robustness Check on Bayesian Priors}
+We used a default prior distribution on the effect size for the alternative hypothesis in the Bayes factor analysis of the critical interaction, which was assumed to be distributed as a Cauchy distribution with scale parameter $r$ = 0.707.
+To examine how robust our findings were to the choice of prior, we conducted a robustness check by re-calculating the Bayes factor across a wide range of priors by varying scale parameter $r$: As $r$ increases, the prior distribution becomes wider, reflecting a prior for larger effects; $r$ values closer to zero make the distribution narrower, reflecting a prior for smaller effects.
 The robustness check is plotted in Figure \ref{fig:robustPrior}.
-This figure shows our conclusions (and our stopping rule) are robust to the prior used: Evidence favours the alternative hypothesis across all prior widths.
+This figure shows our conclusions (and our stopping rule) are robust to the prior used: Evidence favours the alternative hypothesis across all plausible prior widths.
 
@@
 \includegraphics[width = \textwidth]{Images/robustPrior.pdf}
-\caption{Robustness check of Bayes factor across a wide range of priors.}
+\caption{Robustness check of Bayes factor across a wide range of priors for Experiment 1.}
 \label{fig:robustPrior}
@@
 
-\subsubsection{Robustness of Recruitment Order on the Sequential Bayes Factor}
+\subsection{Robustness of Recruitment Order on the Sequential Bayes Factor}
 The progression of the Bayes Factor as sample size increased (Figure \ref{fig:bayesFactor}) appeared to provide slight evidence in favour of the null between sample sizes of 30 and 40, although the criterion for stopping was not reached.
@@
 \includegraphics[width =  \textwidth]{Images/recruitmentOrder.pdf}
-\caption{Simulated progression of the Sequential Bayes Factors for a random set of 50 different recruitment orders for the current data set. See text for details.}
+\caption{Simulated progression of the Sequential Bayes Factors for a random set of 50 different recruitment orders for the current data set in Experiment 1.}
 \label{fig:recruitmentOrder}
@@
 
-\subsubsection{Bayesian Parameter Estimation}
-We wished to supplement our Bayes factor analysis with Bayesian parameter estimation of the mean and effect size of the difference in n--2 task repetition cost between response repetitions and response switches.
+\subsection{Bayesian Parameter Estimation}
+Due to the theoretical importance of our main result, we wished to supplement our Bayes factor analysis with Bayesian parameter estimation of the mean and effect size of the difference in n--2 task repetition cost between n--2 response repetitions and response switches.
 As such, we used the (default) methods outlined by \cite{Kruschke2013}.
@@
 \includegraphics[width = \textwidth]{Images/bayesParameter.pdf}
-\caption{Bayesian posterior distributions for the parameters of mean difference and effect size of difference for n--2 task repetition cost [response repetition] minus n--2 task repetition cost [response switch].
-HDI = Highest Density Interval.
-See text for details.}
+\caption{Bayesian posterior distributions for the parameters of mean difference and effect size of difference for n--2 task repetition cost [response repetition] minus n--2 task repetition cost [response switch] from Experiment 1.
+HDI = Highest Density Interval.}
 \label{fig:bayesParameter}
@@
 The black horizontal bar represents the 95\% Highest Density Interval (HDI); in contrast to frequentist confidence intervals, we can interpret this interval as the range of parameter values we are 95\% certain the true underlying parameter lies within.
-The mean difference in n--2 task repetition costs for response repetitions and response switches is estimated to be -37ms; the HDI does not cross zero, so we can be confident that there is a difference between response repetitions and switches.
+The mean difference in n--2 task repetition costs for n--2 response repetitions and response switches is estimated to be -37ms; the HDI does not cross zero, so we can be confident that there is a difference between response repetitions and switches.
 Note, though, that the effect size of this difference is in the small range.
-For hypothesis testing (i.e., assessing whether episodic retrieval does impact the n--2 repetition cost or not), this is less relevant, but it is important to note if we wish to explore \emph{how much} episodic retrieval might affect n--2 repetition costs.
-
-\subsection{Accuracy}
-Accuracy analysis showed no significant effect of task sequence [$F$(1, 75) = 3.36, $p$=.07, $\eta_G^2$ = .006]; the Bayes factor for this main effect was $BF_{10}$ = 0.618, which provides only anecdotal support for the null.
-The main effect of response repetition was significant [$F$(1, 75) = 12.17, $p$<.001, $\eta_G^2$ = .019], suggestive of better accuracy for response repetitions (96.28\%) than for response switches (95.41\%).
-The Bayes factor was $BF_{10}$ = 29.66, which provides strong support for the alternative.
-The interaction was not significant [$F$(1, 75) = 1.32, $p$=.25, $\eta_G^2$ = .003]; the Bayes factor was $BF_{10}$ = 0.238, which provides moderate support for the null hypothesis.
-
-%----------------------
-\section{Discussion}
-
-The present study sought to re-examine the evidence for any potential effect of episodic retrieval on n--2 task repetition costs in task switching by replicating key aspects of Mayr's (2002) study.
-In contrast to that study, we found clear evidence of episodic retrieval influencing n--2 task repetition costs in task switching; specifically, n--2 task repetition costs were smaller when the response repeated over an ABA sequence compared to when the response switched.
-This is in line with an episodic retrieval account which produces facilitation to responding when trial parameters match over an ABA sequence (i.e., for n--2 response repetitions).
-This facilitation to performance can reduce to some extent the n--2 task repetition cost, suggesting episodic retrieval can reduce the negative effects of inhibition when trial parameters match.
-
-This finding has important implications for theories of task switching.
-There is growing evidence that episodic retrieval plays a role in explaining several task switching effects.
-For example, \cite{Altmann2011} provided empirical and theoretical evidence that episodic retrieval can explain the response-repetition effect in task switching, the observation that task repetition RTs are facilitated when the required response repeats from trial n--1 to the current trial, yet response repetitions produce a cost for task switches.
-\cite{Horoufchin2011a} \citep[see also][]{Horoufchin2011} also provided evidence that episodic retrieval can explain some task switching effects.
-It is typically found that the switch cost is reduced at longer RCIs \cite[e.g.,][]{Meiran2000a}; the standard explanation for this finding pertains to the decay of task representations in memory reducing task repetition RTs.
-However, \cite{Horoufchin2011a} provided compelling evidence that this pattern of data can be better explained with reference to episodic retrieval account: trialwise variation of the RCI affects the \emph{temporal distinctiveness} of task traces in episodic memory, thus influencing their retrieval probability \citep{Brown2007,Grange2015}.
-The current work extends this evidence of the role of episodic retrieval influencing task switching effects.
-As such, theoretical accounts of cognitive control during task switching will have to take into account the role of episodic retrieval.
-
-For clarification, note that we have not provided evidence that episodic retrieval can explain the n--2 task repetition cost entirely, but rather that it reduces the cost.
-Indeed, the n--2 task repetition cost was still statistically significant even when the trial parameters matched across n--2 task repetitions (i.e., n--2 response repetitions).
-Therefore, our findings do not provide evidence against the inhibitory explanation of these costs.
-Rather, we have shown that these costs can be reduced with successful episodic retrieval.
-As such, researchers should be cognisant of the potential contribution of episodic retrieval mismatches inflating estimates of n--2 task repetition costs when wishing to use this effect for measuring inhibition.
-
-Our results differ to those reported by \cite{Mayr2002}.
-We suggest that our modifications to Mayr's original design improved the sensitivity of the paradigm to be able to detect potential episodic retrieval effects on n--2 task repetitions.
-The modifications were made to enhance the magnitude of n--2 task repetition costs, so that modulation of this cost with response repetitions could be more easily detected.
-Specifically, removing the possibility of immediate task repetitions likely enhanced the n--2 task repetition cost as it has been shown that allowing immediate repetitions reduces this cost \citep{Philipp2006}.
-We also used the shortest RCI used by Mayr (150ms), as it is a consistent finding that this increases the n--2 repetition cost \cite{Gade2005, Grange2009, Mayr2000, Mayr2002}.
-Any one of these modifications could explain the difference in results between this study and that of Mayr (2002).
-Future research should aim to examine the potential role for episodic retrieval influencing n--2 task repetition costs by providing further replications and conceptual extensions to this study \citep{OpenScienceCollaboration2015}.
-
-%%%--------------------------------------------------------------------------------------------
 
